% !Mode:: "TeX:UTF-8"

%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[UTF8,a4paper,12pt, twoside]{ctexart}
% \documentclass[10pt,a4paper,twoside]{article} % 10pt font size, A4 paper and two-sided margins

\usepackage[top=2.54cm,bottom=2.54cm,left=3cm,right=2cm,columnsep=30pt]{geometry} % Document margins and spacings

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

\usepackage{palatino} % Use the Palatino font

\usepackage{microtype} % Improves spacing

\usepackage{multicol} % Required for splitting text into multiple columns

\usepackage[bf,center][big]{titlesec} % Required for modifying section titles - bold, sans-serif, centered

\usepackage{fancyhdr} % Required for modifying headers and footers

\usepackage{enumitem}

\usepackage{xcolor}

\usepackage{xifthen}% provides \isempty test

\usepackage{tcolorbox}

\usepackage{ulem}

\newcommand{\cbox}[2][black!5]{%
\colorbox{#1}{\parbox{\dimexpr\linewidth-\fboxsep}{\textcolor{black}{\strut #2\strut}}}\vspace{3mm}%
}
\newcommand\mystr{Hello World!}

\newcommand{\setList}[1]{\section{List #1}}

\setcounter{secnumdepth}{0}

\fancyhead[L]{\textbf{\rightmark}} % Top left header
\fancyhead[R]{\textbf{\leftmark}} % Top right header
\renewcommand{\headrulewidth}{1pt} % Rule under the header
\fancyfoot[C]{\textbf{Barron 1200}}
\fancyfoot[RO]{\textbf{\thepage}} % Bottom center footer
\fancyfoot[LE]{\textbf{\thepage}} % Bottom center footer
\renewcommand{\footrulewidth}{1pt} % Rule under the footer
\pagestyle{fancy} % Use the custom headers and footers throughout the document
\newcommand{\entry}[5]{
\ifthenelse{\isempty{#4}}%
{\nopagebreak\noindent\markboth{#1}{#1}\cbox{\textbf{#1} \textit{#2} #3}\\*\\*}
{\nopagebreak\noindent\markboth{#1}{#1}\cbox{\textbf{#1} \textit{#2} #3}\ \\*\cbox[black!2]{\textbf{英:} {#4} \\*\textbf{例:} {#5}}\\*\\*}
} % Defines the command to print each word on the page, \markboth{}{} prints the first word on the page in the top left header and the last word in the top right





%----------------------------------------------------------------------------------------

\begin{document}

\markboth{}{}
\tableofcontents
\markboth{}{}
\clearpage

\setList{1-3}

\begin{multicols}{2}
\entry{abash}{V.}{使难堪}{embarrass.}{He was not at all abashed by her open admiration.}
\entry{abate}{V.}{减弱, 减少}{subside; decrease, lessen.}{Rather than leaving immediately, they waited for the storm to abate. abatement, N.}
\entry{abbreviate}{V.}{减短, 缩写}{shorten.}{Because we were running out of time, the lecturer had to abbreviate her speech.}
\entry{aberrant}{N.}{不正常的}{abnormal or deviant.}{Given the aberrant nature of the data, we doubted the validity of the entire experiment. also N.}
\entry{abjure}{V.}{发誓放弃}{renounce upon oath.}{He abjured his allegiance to the king. abjuration, N.}
\entry{abolish}{V.}{废除}{cancel; put an end to.}{The president of the college refused to abolish the physical education requirement. abolition, N.}
\entry{aboriginal}{ADJ. N.}{原来的, 土著的}{being the first of its kind in a region; primitive; native.}{Her studies of the primitive art forms of the aboriginal Indians were widely reported in the scientific journals. aborigines, N.}
\entry{abridge}{V.}{删节, 节选}{condense or shorten.}{Because the publishers felt the public wanted a shorter version of War and Peace, they proceeded to abridge the novel.}
\entry{abrogate}{ADJ.}{废除}{abolish.}{He intended to abrogate the decree issued by his predecessor.}
\entry{abash}{V.}{使难堪}{embarrass.}{He was not at all abashed by her open admiration.}
\entry{absorb}{V.}{吸收, 合并}{assimilate or incorporate; suck or drink up; wholly engage.}{During the nineteenth century, America absorbed hordes of immigrants, turning them into productive citizens. Can Huggies diapers absorb more liquid than Pampers can? This question does not absorb me; instead, it bores me. absorption, N.}
\entry{abstract}{ADJ.}{抽象的}{theoretical; not concrete; nonrepresentational.}{To him, hunger was an abstract concept; he had never missed a meal.}
\entry{abstruse}{ADJ.}{难以理解的, 复杂的}{obscure; profound; difficult to understand.}{She carries around abstruse works of philosophy, not because she understands them but because she wants her friends to think she does.}
\entry{abundant}{ADJ.}{丰富, 富足}{plentiful; possessing riches or resources.}{At his immigration interview, Ivan listed his abundant reasons for coming to America: the hope of religious freedom, the prospect of employment, the promise of a more abundant life.}
\entry{abusive}{ADJ.}{粗俗的侮辱, 对身体有害的}{coarsely insulting; physically harmful.}{An abusive parent damages a child both mentally and physically.}
\entry{accede}{V.}{同意}{agree.}{If I accede to this demand for blackmail, I am afraid that I will be the victim of future demands.}
\entry{accelerate}{V.}{加速}{move faster.}{In our science class, we learn how falling bodies accelerate.}
\entry{accentuate}{V.}{强调, 重音}{emphasize; stress.}{If you accentuate the positive and eliminate the negative, you may wind up with an overoptimistic view of the world.}
\entry{accessible}{ADJ.}{可得到的}{easy to approach; obtainable.}{We asked our guide whether the ruins were accessible on foot.}
\entry{abate}{V.}{减弱, 减少}{subside; decrease, lessen.}{Rather than leaving immediately, they waited for the storm to abate. abatement, N.}
\entry{accommodate}{V.}{招待, 食宿, 适应}{oblige or help someone; adjust or bring into harmony; adapt.}{Mitch always did everything possible to accommodate his elderly relatives, from driving them to medical appointments to helping them with paperwork. (secondary meaning)}
\entry{accord}{N.}{一致}{agreement.}{She was in complete accord with the verdict.}
\entry{accretion}{N.}{增长}{growth; increase.}{The accretion of wealth marked the family's rise in power.}
\entry{acknowledge}{V.}{认可, 承认}{recognize; admit.}{Although I acknowledge that the Beatles' tunes sound pretty dated today, I still prefer them to the "gangsta rap" songs my brothers play.}
\entry{acquiesce}{V.}{默许}{assent; agree without protesting.}{Although she appeared to acquiesce to her employer's suggestions, I could tell she had reservations about the changes he wanted made. acquiescence, N.; acquiescent,ADJ.}
\entry{acquire}{V.}{获取}{obtain; get.}{Frederick Douglass was determined to acquire an education despite his master's efforts to prevent his doing so.}
\entry{acrid}{ADJ.}{尖锐; 尖酸}{sharp; bitterly pungent.}{The acrid odor of burnt gunpowder filled the room after the pistol had been fired.}
\entry{actuate}{V.}{推动, 促使}{motivate.}{I fail to understand what actuated you to reply to this letter so nastily.}
\entry{adapt}{V.}{改变}{alter; modify.}{Some species of animals have become extinct because they could not adapt to a changing environment.}
\entry{abbreviate}{V.}{减短, 缩写}{shorten.}{Because we were running out of time, the lecturer had to abbreviate her speech.}
\entry{adept}{ADJ.}{擅长于}{expert at.}{She was adept at the fine art of irritating people. also N.}
\entry{adorn}{V.}{装饰}{decorate.}{Wall paintings and carved statues adorned the temple. adornment, N.}
\entry{adverse}{ADJ.}{讨厌, 敌意}{unfavorable; hostile.}{The recession had a highly adverse effect on Father's investment portfolio: he lost so much money that he could no longer afford the butler and the upstairs maid. adversity, N.}
\entry{advocate}{V.}{辩护}{urge; plead for.}{The abolitionists advocated freedom for the slaves. also N.}
\entry{aesthetic}{ADJ.}{审美的}{artistic; dealing with or capable of appreciation of the beautiful.}{The beauty of Tiffany's stained glass appealed to Esther's aesthetic sense. aesthete, N.}
\entry{affirmation}{N.}{正面肯定, 确认}{positive assertion; confirmation; solemn pledge by one who refuses to take an oath.}{Despite Tom's affirmations of innocence, Aunt Polly still suspected he had eaten the pie.}
\entry{aftermath}{N.}{后果, 结果}{consequences; outcome; upshot.}{People around the world wondered what the aftermath of China's violent suppression of the student protests would be.}
\entry{agenda}{N.}{议程}{items of business at a meeting.}{We had so much difficulty agreeing upon an agenda that there was very little time for the meeting.}
\entry{aggregate}{V.}{收集, 聚集}{gather; accumulate.}{Before the Wall Street scandals, dealers in so-called junk bonds managed to aggregate great wealth in short periods of time. aggregation, N.}
\entry{aberrant}{N.}{不正常的}{abnormal or deviant.}{Given the aberrant nature of the data, we doubted the validity of the entire experiment. also N.}
\entry{allege}{V.}{断言}{state without proof.}{Although it is alleged that she has worked for the enemy, she denies the allegation and, legally, we can take no action against her without proof. allegation, N.}
\entry{alleviate}{V.}{解脱, 释放, 释然}{relieve.}{This should alleviate the pain; if it does not, we shall have to use stronger drugs.}
\entry{allocate}{V.}{分配, 制定}{assign.}{Even though the Red Cross had allocated a large sum for the relief of the sufferers of the disaster, many people perished.}
\entry{allusion}{N.}{暗指, 暗示}{indirect reference.}{When Amanda said to the ticket scalper, "One hundred bucks? What do you want, a pound of flesh?," she was making an allusion to Shakespeare's Merchant of Venice.}
\entry{altruistic}{ADJ.}{无私的, 关心他人的}{unselfishly generous; concerned for others.}{In providing tutorial assistance and college scholarships for hundreds of economically disadvantaged youths, Eugene Lang performed a truly altruistic deed. altruism, N.}
\entry{amass}{V.}{收集}{collect.}{The miser's aim is to amass and hoard as much gold as possible.}
\entry{ambiguous}{ADJ.}{模棱两可}{unclear or doubtful in meaning.}{His ambiguous instructions misled us; we did not know which road to take. ambiguity, N.}
\entry{ambivalence}{N.}{矛盾的观点或情绪}{the state of having contradictory or conflicting emotional attitudes.}{Torn between loving her parents one minute and hating them the next, she was confused by the ambivalence of her feelings. ambivalent,ADJ.}
\entry{amble}{N.}{漫步, 缓行}{moving at an easy pace.}{When she first mounted the horse, she was afraid to urge the animal to go faster than a gentle amble. alsoV.}
\entry{abjure}{V.}{发誓放弃}{renounce upon oath.}{He abjured his allegiance to the king. abjuration, N.}
\entry{amiss}{ADJ.}{错误}{wrong; faulty.}{Seeing her frown, he wondered if anything were amiss. also ADV.}
\entry{amorphous}{ADJ.}{无形的, 不成形的}{formless; lacking shape or definition.}{As soon as we have decided on our itinerary, we shall send you a copy; right now, our plans are still amorphous.}
\entry{ample}{ADJ.}{丰富的, 富足的}{abundant.}{Bond had ample opportunity to escape. Why did he let us catch him?}
\entry{amplify}{V.}{放大}{broaden or clarify by expanding; intensify; make stronger.}{Charlie Brown tried to amplify his remarks, but he was drowned out by jeers from the audience. Lucy was smarter: she used a loudspeaker to amplify her voice.}
\entry{analogous}{ADJ.}{类似的}{comparable.}{She called our attention to the things that had been done in an analogous situation and recommended that we do the same.}
\entry{anarchist}{N.}{无政府主义者}{person who seeks to overturn the established government; advocate of abolishing authority.}{Denying she was an anarchist, Katya maintained she wished only to make changes in our government, not to destroy it entirely. anarchy, N.}
\entry{ancillary}{ADJ.}{辅助的}{serving as an aid or accessory; auxiliary.}{In an ancillary capacity, Doctor Watson was helpful; however, Holmes could not trust the good doctor to solve a perplexing case on his own. also N.}
\entry{anecdote}{N.}{奇闻轶事}{short account of an amusing or interesting event.}{Rather than make concrete proposals for welfare reform, President Reagan told anecdotes about poor people who became wealthy despite their impoverished backgrounds.}
\entry{angular}{ADJ.}{有尖角的, 瘦骨嶙峋的}{sharp-cornered; stiff in manner.}{Mr. Spock's features, though angular, were curiously attractive, in a Vulcan way.}
\entry{abolish}{V.}{废除}{cancel; put an end to.}{The president of the college refused to abolish the physical education requirement. abolition, N.}
\entry{annals}{N.}{记录, 历史}{records; history.}{In the annals of this period, we find no mention of democratic movements.}
\entry{annul}{v.}{避免}{make void.}{The parents of the eloped couple tried to annul the marriage.}
\entry{anomaly}{N.}{不正常}{irregularity.}{A bird that cannot fly is an anomaly.}
\entry{anonymous}{ADJ.}{匿名的}{having no name.}{She tried to ascertain the identity of the writer of the anonymous letter.}
\entry{antecede}{V.}{先于}{precede.}{The invention of the radiotelegraph anteceded the development of television by a quarter of a century.}
\entry{antidote}{N.}{解药}{medicine to counteract a poison or disease.}{When Marge's child accidentally swallowed some cleaning fluid, the local poison control hotline instructed Marge how to administer the antidote.}
\entry{antipathy}{N.}{反对, 厌恶}{aversion; dislike.}{Tom's extreme antipathy for disputes keeps him from getting into arguments with his temperamental wife. Noise in any form is antipathetic to him. Among his other antipathies are honking cars, boom boxes, and heavy metal rock.}
\entry{antiquated}{ADJ.}{过时的, 陈旧的}{old-fashioned; obsolete.}{Philip had grown so accustomed to editing his papers on word processors that he thought typewriters were too antiquated for him to use.}
\entry{apathy}{N.}{漠不关心}{lack of caring; indifference.}{A firm believer in democratic government, she could not understand the apathy of people who never bothered to vote. apathetic,ADJ.}
\entry{aboriginal}{ADJ. N.}{原来的, 土著的}{being the first of its kind in a region; primitive; native.}{Her studies of the primitive art forms of the aboriginal Indians were widely reported in the scientific journals. aborigines, N.}
\entry{apogee}{N.}{顶点}{highest point.}{When the moon in its orbit is farthest away from the earth, it is at its apogee.}
\entry{apologist}{N.}{辩护者}{one who writes in defense of a cause or institution.}{Rather than act as an apologist for the current regime in Beijing and defend its brutal actions, the young diplomat decided to defect to the West.}
\entry{appease}{V.}{平静, 安抚}{pacify or soothe; relieve.}{Tom and Jody tried to appease the crying baby by offering him one toy after another, but he would not calm down until they appeased his hunger by giving him a bottle.}
\entry{application}{N.}{勤奋的付出}{diligent attention.}{Pleased with how well Tom had whitewashed the fence, Aunt Polly praised him for his application to the task. apply, V. (secondary meaning)}
\entry{apposite}{ADJ.}{合适的}{appropriate; fitting.}{He was always able to find the apposite phrase, the correct expression for every occasion.}
\entry{appraise}{V.}{估价}{estimate value of.}{It is difficult to appraise the value of old paintings; it is easier to call them priceless. appraisal, N.}
\entry{appreciate}{V.}{感激; 增值; 赏识}{be thankful for; increase in worth; be thoroughly conscious of.}{Little Orphan Annie truly appreciated the stocks Daddy Warbucks gave her, which appreciated in value considerably over the years.}
\entry{apprehend}{V.}{逮捕; 惧怕; 领会}{arrest (a criminal); dread; perceive.}{The police will apprehend the culprit and convict him before long.}
\entry{approbation}{N.}{同意, 批准}{approval.}{She looked for some sign of approbation from her parents, hoping her good grades would please them.}
\entry{abridge}{V.}{删节, 节选}{condense or shorten.}{Because the publishers felt the public wanted a shorter version of War and Peace, they proceeded to abridge the novel.}
\entry{aptitude}{N.}{能力, 才能}{fitness; talent.}{The counselor gave him an aptitude test before advising him about the career he should follow.}
\entry{arable}{ADJ.}{可耕种的}{fit for growing crops.}{The first settlers wrote home glowing reports of the New World, praising its vast acres of arable land ready for the plow.}
\entry{arbitrary}{ADJ.}{反复无常; 残暴; 随机的}{capricious; randomly chosen; tyrannical.}{Tom's arbitrary dismissal angered him; his boss had no reason to fire him. He threw an arbitrary assortment of clothes into his suitcase and headed off, not caring where he went.}
\entry{arcane}{ADJ.}{秘密; 谜}{secret; mysterious; known only to the initiated.}{Secret brotherhoods surround themselves with arcane rituals and trappings to mystify outsiders. So do doctors. Consider the arcane terminology they use and the impression they try to give that what is arcane to us is obvious to them.}
\entry{archaic}{ADJ.}{过时的}{antiquated.}{"Methinks," "thee," and "thou" are archaic words that are no longer part of our normal vocabulary.}
\entry{archives}{N.}{档案; 档案馆}{public records; place where public records are kept.}{These documents should be part of the archives so that historians may be able to evaluate them in the future.}
\entry{ardent}{ADJ.}{激烈的; 热心肠的; 有激情的}{intense; passionate; zealous.}{Katya's ardor was contagious; soon all her fellow demonstrators were busily making posters and handing out flyers, inspired by her ardent enthusiasm for the cause. ardor, N.}
\entry{arid}{ADJ.}{荒芜的}{dry; barren.}{The cactus has adapted to survive in an arid environment.}
\entry{arousal}{N.}{觉醒; 激励}{awakening; provocation (of a response).}{On arousal, Papa was always grumpy as a bear. The children tiptoed around the house, fearing they would arouse his anger by waking him up.}
\entry{abrogate}{ADJ.}{废除}{abolish.}{He intended to abrogate the decree issued by his predecessor.}
\entry{arrest}{V.}{阻止; 引起注意; 吸引}{stop or slow down; catch someone's attention.}{Slipping, the trapeze artist plunged from the heights until a safety net luckily arrested his fall. This near-disaster arrested the crowd's attention.}
\entry{arrogance}{N.}{傲慢, 骄傲}{pride; haughtiness.}{Convinced that Emma thought she was better than anyone else in the class, Ed rebuked her for her arrogance.}
\entry{artifact}{N.}{人造物品}{object made by human beings, either handmade or mass-produced.}{Archaeologists debated the significance of the artifacts discovered in the ruins of Asia Minor but came to no conclusion about the culture they represented.}
\entry{ascendancy}{N.}{统治, 控制}{controlling influence; domination.}{Leaders of religious cults maintain ascendancy over their followers by methods that can verge on brainwashing.}
\entry{ascertain}{V.}{确认, 确证}{find out for certain.}{Please ascertain her present address.}
\entry{ascribe}{V.}{归因于; 指派}{refer; attribute; assign.}{I can ascribe no motive for her acts.}
\entry{aspire}{V.}{热望; 热心于}{seek to attain; long for.}{Because he aspired to a career in professional sports, Philip enrolled in a graduate program in sports management. aspiration, N.}
\entry{assert}{V.}{断言}{declare or state with confidence; put oneself forward boldly.}{Malcolm asserted that if Reese quit acting like a wimp and asserted himself a bit more, he'd improve his chances of getting a date. assertion, N.}
\entry{assuage}{V.}{减轻（痛苦）; 满足（饥渴）; 安慰}{ease or lessen (pain); satisfy (hunger); soothe (anger).}{Jilted by Jane, Dick tried to assuage his heartache by indulging in ice cream. One gallon later, he had assuaged his appetite but not his grief.}
\entry{assumption}{N.}{假定, 设想; 采取}{something taken for granted; taking over or taking possession of.}{The young princess made the foolish assumption that the regent would not object to her assumption of power. assume,V.}
\end{multicols}
\clearpage
\setList{4-6}

\begin{multicols}{2}
\entry{assurance}{N.}{担保, 保证; 确定; 自信}{promise or pledge; certainty; self-confidence.}{When Guthrie gave Guinness his assurance that rehearsals were going well, he spoke with such assurance that Guinness felt relieved. assure,V.}
\entry{astronomical}{ADJ.}{巨大, 广阔}{enormously large or extensive.}{The government seems willing to spend astronomical sums on weapons development.}
\entry{astute}{ADJ.}{聪明; 敏锐}{wise; shrewd; keen.}{The painter was an astute observer, noticing every tiny detail of her model's appearance and knowing exactly how important each one was.}
\entry{asymmetric}{ADJ.}{不对称}{not identical on both sides of a dividing central line.}{Because one eyebrow was set markedly higher than the other, William's face had a particularly asymmetric appearance.}
\entry{atrocity}{N.}{暴行}{brutal deed.}{In time of war, many atrocities are committed by invading armies.}
\entry{atrophy}{N.}{萎缩, 变得没用}{wasting away.}{Polio victims need physiotherapy to prevent the atrophy of affected limbs. alsoV.}
\entry{attain}{V.}{获得; 完成}{achieve or accomplish; gain.}{The scarecrow sought to attain one goal: he wished to obtain a brain.}
\entry{attentive}{ADJ.}{专心的, 专注的; 全神贯注}{alert and watchful; considerate; thoughtful.}{Spellbound, the attentive audience watched the final game of the tennis match, never taking their eyes from the ball. A cold wind sprang up; Stan's attentive daughter slipped a sweater over his shoulders without distracting his attention from the game.}
\entry{attest}{V.}{证明}{testify, bear witness.}{Having served as a member of the Grand Jury, I can attest that our system of indicting individuals is in need of improvement.}
\entry{attribute}{N.}{属性}{essential quality.}{His outstanding attribute was his kindness.}
\entry{atypical}{ADJ.}{非正常的, 不正常}{not normal.}{The child psychiatrist reassured Mrs. Keaton that playing doctor was not atypical behavior for a child of young Alex's age. "Yes," she replied, "but not charging for house calls!"}
\entry{audit}{N.}{核算, 稽核}{examination of accounts.}{When the bank examiners arrived to hold their annual audit, they discovered the embezzlements of the chief cashier. alsoV.}
\entry{auditory}{ADJ.}{听觉的}{pertaining to the sense of hearing.}{Audrey suffered from auditory hallucinations: she thought Elvis was speaking to her from the Great Beyond.}
\entry{augment}{V.}{增长}{increase; add to.}{Armies augment their forces by calling up reinforcements; teachers augment their salaries by taking odd jobs.}
\entry{augury}{N.}{占卜; 预言}{omen; prophecy.}{He interpreted the departure of the birds as an augury of evil. augur,V.}
\entry{august}{ADJ.}{威严的; 令人印象深刻的}{impressive; majestic.}{Visiting the palace at Versailles, she was impressed by the august surroundings in which she found herself.}
\entry{austere}{ADJ.}{严厉的; 朴素的}{forbiddingly stern; severely simple and unornamented.}{The headmaster's austere demeanor tended to scare off the more timid students, who never visited his study willingly. The room reflected the man, austere and bare, like a monk's cell, with no touches of luxury to moderate its austerity.}
\entry{authenticate}{V.}{鉴别}{prove genuine.}{An expert was needed to authenticate the original Van Gogh painting, distinguishing it from its imitation.}
\entry{authoritative}{ADJ.}{权威; 独裁}{having the weight of authority; peremptory and dictatorial.}{Impressed by the young researcher's well-documented presentation, we accepted her analysis of the experiment as authoritative.}
\entry{autonomous}{ADJ.}{自治}{self-governing.}{Although the University of California at Berkeley is just one part of the state university system, in many ways Cal Berkeley is autonomous, for it runs several programs that are not subject to outside control. autonomy, N.}
\entry{avenge}{V.}{复仇}{take vengeance for something (or on behalf of someone).}{Hamlet vowed he would avenge his father's murder and punish Claudius for his horrible crime.}
\entry{averse}{ADJ.}{反对的}{reluctant; disinclined.}{The reporter was averse to revealing the sources of his information.}
\entry{avert}{V.}{转移; 防止}{prevent; turn away.}{She averted her eyes from the dead cat on the highway.}
\entry{awe}{N.}{敬畏}{solemn wonder.}{The tourists gazed with awe at the tremendous expanse of the Grand Canyon.}
\entry{badger}{V.}{激怒, 纠缠}{pester; annoy.}{She was forced to change her telephone number because she was badgered by obscene phone calls.}
\entry{baffle}{V.}{挫败}{frustrate; perplex.}{The new code baffled the enemy agents.}
\entry{balk}{V.}{反对; 阻止}{foil or thwart; stop short; refuse to go on.}{When the warden learned that several inmates were planning to escape, he took steps to balk their attempt. However, he balked at punishing them by shackling them to the walls of their cells.}
\entry{barren}{ADJ.}{荒芜的, 贫瘠的}{desolate; fruitless and unproductive; lacking.}{Looking out at the trackless, barren desert, Indiana Jones feared that his search for the missing expedition would prove barren.}
\entry{barterer}{N.}{交易商}{trader.}{The barterer exchanged trinkets for the natives' furs. It seemed smarter to barter than to pay cash.}
\entry{bask}{V.}{享受（温暖）; 愉快, 舒适}{luxuriate; take pleasure in warmth.}{Basking on the beach, she relaxed so completely that she fell asleep.}
\entry{beam}{N.}{光束; 铁梁, 木梁; 一束电波}{ray of light; long piece of metal or wood; course of a radio signal.}{V. smile radiantly. If a beam of light falls on you, it illuminates you; if a beam of iron falls on you, it elimi-nates you. (No one feels like beaming when crushed by an iron beam.)}
\entry{beguile}{V.}{欺骗, 骗住; 消磨时间}{mislead or delude; pass time.}{With flattery and big talk of easy money, the con men beguiled Kyle into betting his allowance on the shell game. Broke, he beguiled himself during the long hours by playing solitaire.}
\entry{beleaguer}{V.}{攻击; 使烦恼}{besiege or attack; harassed.}{The babysitter was surrounded by a crowd of unmanageable brats who relentlessly beleaguered her.}
\entry{belie}{V.}{掩饰, 造成假象; 矛盾}{contradict; give a false impression.}{His coarse, hard-bitten exterior belied his inner sensitivity.}
\entry{belittle}{V.}{蔑视, 使渺小}{disparage or depreciate; put down.}{Parents should not belittle their children's early attempts at drawing, but should encourage their efforts. Barry was a put-down artist: he was a genius at belittling people and making them feel small.}
\entry{bemused}{ADJ.}{困惑的, 发呆的}{confused; lost in thought; preoccupied.}{Jill studied the garbled instructions with a bemused look on her face.}
\entry{beneficial}{ADJ.}{有用的}{helpful; useful.}{Tiny Tim's cheerful good nature had a beneficial influence on Scrooge's onceuncharitable disposition.}
\entry{bequeath}{V.}{遗赠, （代代）相传}{leave to someone by a will; hand down.}{Though Maud had intended to bequeath the family home to her nephew, she died before changing her will. bequest, N.}
\entry{beset}{V.}{困扰}{harass or trouble; hem in.}{Many vexing problems beset the American public school system. Sleeping Beauty's castle was beset on all sides by dense thickets that hid it from view.}
\entry{besiege}{V.}{围攻}{surround with armed forces; harass (with requests).}{When the bandits besieged the village, the villagers holed up in the town hall and prepared to withstand a long siege. Members of the new administration were besieged with job applications from people who had worked on the campaign.}
\entry{bestow}{V.}{给予}{give.}{He wished to bestow great honors upon the hero.}
\entry{betoken}{V.}{预示; 表示}{signify; indicate.}{The well-equipped docks, tall piles of cargo containers, and numerous vessels being loaded all betoken Oakland's importance as a port.}
\entry{betray}{V.}{出卖; 背叛}{be unfaithful; reveal (unconsciously or unwillingly).}{The spy betrayed his country by selling military secrets to the enemy. When he was taken in for questioning, the tightness of his lips betrayed his fear of being caught.}
\entry{biased}{ADJ.}{偏见的, 偏差}{slanted; prejudiced.}{Because the judge played golf regularly with the district attorney's father, we feared he might be biased in the prosecution's favor. bias, N.}
\entry{biennial}{ADJ.}{两年一度}{every two years.}{Seeing no need to meet more frequently, the group held biennial meetings instead of annual ones. Plants that bear flowers biennially are known as biennials.}
\entry{bizarre}{ADJ.}{怪异的}{fantastic; violently contrasting.}{The plot of the novel was too bizarre to be believed.}
\entry{bleak}{ADJ.}{冷淡; 凄凉}{cold or cheerless; unlikely to be favorable.}{The frigid, inhospitable Aleutian Islands are bleak military outposts. It's no wonder that soldiers assigned there have a bleak attitude toward their posting.}
\entry{blighted}{ADJ.}{完蛋了的; 生病了的}{suffering from a disease; destroyed.}{The extent of the blighted areas could be seen only when viewed from the air.}
\entry{bluff}{ADJ.}{直率的}{rough but good-natured.}{Jack had a bluff andhearty manner that belied his actual sensitivity; he never let people know how thin-skinned he really was.}
\entry{bode}{V.}{预兆}{foreshadow; portend.}{The gloomy skies and the sulphurous odors from the mineral springs seemed to bode evil to those who settled in the area.}
\entry{bolster}{V.}{支持, 增援}{support; reinforce.}{The debaters amassed file boxes full of evidence to bolstertheir arguments.}
\entry{bombastic}{ADJ.}{夸张的}{pompous; using inflated language.}{Puffed up with conceit, the orator spoke in such a bombastic manner that we longed to deflate him. bombast, N.}
\entry{booming}{ADJ.}{快速增长的, 欣欣向荣; 深刻的}{deep and resonant; flourishing, thriving.}{"Who needs a microphone?" cried the mayor in his booming voice. Cheerfully he boomed out that, thanks to him, the city's economy was booming. boom,V.}
\entry{boundless}{ADJ.}{无限的}{unlimited; vast.}{Mike's energy was boundless: the greater the challenge, the more vigorously he tackled the job.}
\entry{bountiful}{ADJ.}{富足的; 慷慨的}{abundant; graciously generous.}{Thanks to the good harvest, we had a bountiful supply of food and we could be as bountiful as we liked in distributing food to the needy.}
\entry{boycott}{V.}{抵制}{refrain from buying or using.}{To put pressure on grape growers to stop using pesticides that harmed the farm workers' health, Cesar Chavez called for consumers to boycott grapes.}
\entry{braggart}{N.}{自夸, 吹嘘}{boaster.}{Modest by nature, she was no braggart, preferring to let her accomplishments speak for themselves.}
\entry{breadth}{N.}{宽度}{width; extent.}{We were impressed by the breadth of her knowledge.}
\entry{brevity}{N.}{简短, 短暂}{conciseness.}{Brevity is essential when you send a telegram or cablegram; you are charged for every word.}
\entry{brittle}{ADJ.}{易碎的; 困难的}{easily broken; difficult.}{My employer's self-control was as brittle as an egg-shell. Her brittle personality made it difficult for me to get along with her.}
\entry{browse}{V.}{吃草; 浏览}{graze; skim or glance at casually.}{"How now, brown cow, browsing in the green, green grass." I remember lines of verse that I came across while browsing through the poetry section of the local bookstore.}
\entry{brusque}{ADJ.}{唐图; 直率; 粗暴无礼}{blunt; abrupt.}{Was Bruce too brusque when he brushed off Bob's request with a curt "Not now!"?}
\entry{bumptious}{ADJ.}{盲目自大}{self-assertive.}{His classmates called him a show-off because of his bumptious airs.}
\entry{buoyant}{ADJ.}{可漂浮的, 乐观的}{able to float; cheerful and optimistic.}{When the boat capsized, her buoyant life jacket kept Jody afloat. Scrambling back on board, she was still in a buoyant mood, certain that despite the delay she'd win the race.}
\entry{bureaucracy}{N.}{官僚机构}{over-regulated administrative system marked by red tape.}{The Internal Revenue Service is the ultimate bureaucracy. taxpayers wasted so much paper filling out IRS forms that the IRS bureaucrats printed up a new set of rules requiring taxpayers to comply with the Paperwork Reduction Act.}
\entry{bustle}{V.}{喧嚣, 繁忙, 熙熙攘攘}{move about energetically; teem.}{David and the children bustled about the house getting in each other's way as they tried to pack for the camping trip. The whole house bustled with activity.}
\entry{buttress}{V.}{支持}{support; prop up.}{The attorney came up with several far-fetched arguments in a vain attempt to buttress his weak case. also N.}
\entry{cacophonous}{ADJ.}{不和谐}{discordant; inharmonious.}{Do the students in the orchestra enjoy the cacophonous sounds they make when they're tuning up? I don't know how they can stand the racket. cacophony, N.}
\entry{cajole}{V.}{哄骗, 勾引}{coax; wheedle.}{Diane tried to cajole her father into letting her drive the family car. cajolery, N.}
\entry{calculated}{ADJ.}{预先计划好的, 算好的; 合适的}{deliberately planned; likely.}{Lexy's choice of clothes to wear to the debate tournament was carefully calculated. Her conventional suit was one calculated to appeal to the conservative judges.}
\entry{camouflage}{V.}{伪装}{disguise; conceal.}{In order to rescue Han Solo, Princess Leia camouflaged herself in the helmet and cloak of a space bandit.}
\entry{candor}{N.}{开诚布公; 坦率}{frankness; open honesty.}{Jack can carry candor too far: when he told Jill his honest opinion of her, she nearly slapped his face. candid,ADJ.}
\entry{cant}{N.}{伪善; 黑话}{insincere expressions of piety; jargon of thieves.}{Shocked by news of the minister's extramarital love affairs, the worshippers dismissed his talk about the sacredness of marriage as mere cant. Cant is a form of hypocrisy: those who can, pray; those who cant, pretend.}
\entry{capacious}{ADJ.}{宽敞的}{spacious.}{In the capacious rotunda of the railroad terminal, thousands of travelers lingered while waiting for their train.}
\entry{capacity}{N.}{能力; 角色}{mental or physical ability; role; ability to accommodate.}{Mike had the capacity to handle several jobs at once. In his capacity as president of SelecTronics he marketed an electronic dictionary with a capacity of 2, words.}
\entry{capitulate}{V.}{投降}{surrender.}{The enemy was warned to capitulate or face annihilation.}
\entry{capricious}{ADJ.}{反复无常的}{unpredictable; fickle.}{The storm was capricious: it changed course constantly. Jill was capricious, too: she changed boyfriends almost as often as she changed clothes.}
\entry{caption}{N.}{标题}{title; chapter heading; text under illustration.}{The captions that accompany The Far Side cartoons are almost as funny as the pictures. alsoV.}
\entry{captivate}{V.}{迷住; 迷惑}{charm or enthrall.}{Bart and Lisa were captivated by their new nanny's winning manner.}
\entry{cardinal}{ADJ.}{主要的}{chief.}{If you want to increase your word power, the cardinal rule of vocabulary-building is to read.}
\entry{careen}{V.}{倾斜}{lurch; sway from side to side.}{The taxicab careened wildly as it rounded the corner.}
\entry{carnivorous}{ADJ.}{食肉的}{meat-eating.}{The lion's a carnivorous beast. A hunk of meat makes up his feast. A cow is not a carnivore. She likes the taste of grain, not gore.}
\entry{carping}{ADJ.}{挑剔的, 吹毛求疵}{finding fault.}{A carping critic is a nit-picker: he loves to point out flaws. If you don't like this definition, feel free to carp.}
\entry{cascade}{N.}{小瀑布}{small waterfall.}{We were too tired to appreciate the beauty of the many cascades because we had to detour around them to avoid being drenched by the water cascading down.}
\entry{castigate}{V.}{严厉批评; 惩罚}{criticize severely; punish.}{When the teacher threatened that she would castigate the mischievous boys if they didn't behave, they shaped up in a hurry.}
\entry{casualty}{N.}{严重的事故; 伤亡}{serious or fatal accident.}{The number of automotive casualties on this holiday weekend was high.}
\entry{catastrophe}{N.}{灾难}{calamity; disaster.}{The 196 San Francisco earthquake was a catastrophe that destroyed most of the city. A similar earthquake striking today could have even more catastrophic results.}
\entry{categorical}{ADJ.}{无条件; 直截了当}{without exceptions; unqualified; absolute.}{Though the captain claimed he was never, never sick at sea, he finally had to qualify his categorical denial: he was "hardly ever" sick at sea.}
\entry{cater to}{V.}{迎合}{supply something desired (whether good or bad).}{The chef was happy to cater to the tastes of his highly sophisticated clientele. Critics condemned the movie industry for catering to the public's ever-increasing appetite for violence.}
\entry{catharsis}{N.}{导泻, 通便; 疏泄}{purging or cleansing of any passage of the body.}{Aristotle maintained that tragedy created a catharsis by purging the soul of base concepts.}
\entry{catholic}{ADJ.}{一般的, 普遍的; 天主教}{broadly sympathetic; liberal.}{He was extremely catholic in his taste and read everything he could find in the library.}
\entry{causal}{ADJ.}{因果关系的}{implying a cause-and-effect relationship.}{The psychologist maintained there was a causal relationship between the nature of one's early childhood experiences and one's adult personality. causality, N.}
\entry{caustic}{ADJ.}{腐蚀; 挖苦}{burning; sarcastically biting.}{The critic's caustic remarks angered the hapless actors who were the subjects of his sarcasm.}
\entry{cavil}{V.}{挑剔}{make frivolous objections.}{It's fine when you make sensible criticisms, but it really bugs me when you cavil about unimportant details. also N.}
\entry{celebrated}{ADJ.}{名人}{famous; well-known.}{Thanks to their race to break Roger Maris's home-run record, Sammy Sosa and Mark McGwire are two of America's most celebrated baseball players. celebrity, N.}
\entry{censure}{V.}{责怪; 批评}{blame; criticize.}{The senator was censured for behavior inappropriate to a member of Congress. also N.}
\entry{ceremonious}{ADJ.}{隆重的}{marked by formality.}{Ordinary dress would be inappropriate at so ceremonious an affair.}
\entry{certitude}{N.}{确实}{certainty.}{Though there was no certitude of his getting the job, Lou thought he had a good chance of doing so.}
\entry{champion}{V.}{拥护}{support militantly.}{Martin Luther King, Jr., won the Nobel Peace Prize because he championed the oppressed in their struggle for equality.}
\entry{chaotic}{ADJ.}{混乱}{in utter disorder.}{He tried to bring order into the chaotic state of affairs. chaos, N.}
\end{multicols}
\clearpage
\setList{7-9}

\begin{multicols}{2}
\entry{chary}{ADJ.}{谨慎; 吝啬}{cautious; sparing or restrained about giving.}{A prudent, thrifty, New Englander, DeWitt was as chary of investing money in junk bonds as he was chary of paying people unnecessary compliments.}
\entry{chasten}{V.}{磨练}{discipline; punish in order to correct.}{Whom God loves, God chastens.}
\entry{check}{V.}{控制; 阻止}{stop motion; curb or restrain.}{Thrusting out her arm, Grandma checked Bobby's lunge at his sister. "Young man," she said, "you'd better check your temper." (secondary meaning)}
\entry{chisel}{N.}{凿子}{wedgelike tool for cutting.}{With his hammer and chisel, the sculptor chipped away at the block of marble.}
\entry{chivalrous}{ADJ.}{勇敢; 诚实}{courteous; faithful; brave.}{Chivalrous behavior involves noble words and good deeds.}
\entry{choleric}{ADJ.}{易发怒的; 脾气坏}{hot-tempered.}{His flushed, angry face indicated a choleric nature.}
\entry{chronic}{ADJ.}{慢性的}{long established as a disease.}{The doctors were finally able to attribute his chronic headaches and nausea to traces of formaldehyde gas in his apartment.}
\entry{circuitous}{ADJ.}{迂回的}{roundabout.}{To avoid the traffic congestion on the main highways, she took a circuitous route. circuit, N.}
\entry{cite}{V.}{引用; 掌握}{quote; command.}{She could cite passages in the Bible from memory. citation, N.}
\entry{civil}{ADJ.}{民事的; 国民的}{having to do with citizens or the state; courteous and polite.}{Although Internal Revenue Service agents are civil servants, they are not always civil to suspected tax cheats.}
\entry{cleave}{V.}{劈开; 黏着; 忠于}{split or sever; cling to; remain faithful to.}{With her heavy cleaver, Julia Child can cleave a whole roast duck in two. Soaked through, the soldier tugged at the uniform that cleaved annoyingly to his body. He would cleave to his post, come rain or shine.}
\entry{cliché}{N.}{陈词滥调}{phrase dulled in meaning by repetition.}{High school compositions are often marred by such clichés as "strong as an ox."}
\entry{coalesce}{V.}{接合}{combine; fuse.}{The brooks coalesce into one large river. When minor political parties coalesce, their coalescence may create a major coalition.}
\entry{codify}{V.}{编纂}{arrange (laws, rules) as a code; classify.}{We need to take the varying rules and regulations of the different health agencies and codify them into a national health code.}
\entry{coercion}{N.}{威逼, 强迫}{use of force to get someone to obey.}{The inquisitors used both physical and psychological coercion to force Joan of Arc to deny that her visions were sent by God. coerce,V.}
\entry{cogitate}{V.}{考虑}{think over.}{Cogitate on this problem; the solution will come.}
\entry{cognitive}{ADJ.}{认知的}{having to do with knowing or perceiving; related to the mental processes.}{Though Jack was emotionally immature, his cognitive development was admirable; he was very advanced intellectually.}
\entry{cohesion}{N.}{内聚力; 黏度}{tendency to keep together.}{A firm believer in the maxim "Divide and conquer," the evil emperor, by means of lies and trickery, sought to disrupt the cohesion of the federation of free nations.}
\entry{coincidence}{N.}{巧合}{two or more things occurring at the same time by chance.}{Was it just a coincidence that John and she had chanced to meet at the market for three days running, or was he deliberately trying to seek her out? coincidental,ADJ.}
\entry{collaborate}{V.}{协作, 合作}{work together.}{Two writers collaborated in preparing this book.}
\entry{colloquial}{ADJ.}{口语的}{pertaining to conversational or common speech.}{Some of the new, less formal reading passages on SAT I have a colloquial tone that is intended to make them more appealing to students.}
\entry{colossal}{ADJ.}{巨大}{huge.}{Radio City Music Hall has a colossal stage.}
\entry{combustible}{ADJ.}{易燃的}{easily burned.}{After the recent outbreak of fires in private homes, the fire commissioner ordered that all combustible materials be kept in safe containers, also N.}
\entry{commemorate}{V.}{纪念}{honor the memory of.}{The statue of the Minute Man commemorates the valiant soldiers who fought in the Revolutionary War.}
\entry{communal}{ADJ.}{公共的}{held in common; of a group of people.}{When they were divorced, they had trouble dividing their communal property.}
\entry{compact}{N.}{合约, 合同}{agreement; contract.}{The signers of the Mayflower Compact were establishing a form of government.}
\entry{compelling}{ADJ.}{强制的}{overpowering; irresistible in effect.}{The prosecutor presented a well-reasoned case, but the defense attorney's compelling arguments for leniency won over the jury.}
\entry{compile}{V.}{聚集, 积累, 汇集}{assemble; gather; accumulate.}{We planned to compile a list of the words most frequently used on SAT I examinations.}
\entry{complacency}{N.}{自满; 装模作样}{self-satisfaction; smugness.}{Full of complacency about his latest victories, he looked smugly at the row of trophies on his mantelpiece. complacent,ADJ.}
\entry{complementary}{ADJ.}{补足的, 完善的}{serving to complete something.}{John and Lisa's skills are complementary. he's good at following a daily routine, while she's great at improvising and handling emergencies. Together they make a great team.}
\entry{compliance}{N.}{顺从}{readiness to yield; conformity in fulfilling requirements.}{Bullheaded Bill was not noted for easy compliance with the demands of others. As an architect, however, Bill recognized that his design for the new school had to be in compliance with the local building code.}
\entry{component}{N.}{成分}{element; ingredient.}{I wish all the components of my stereo system were working at the same time.}
\entry{composure}{N.}{镇定, 沉着}{mental calmness.}{Even the latest work crisis failed to shake her composure.}
\entry{comprehensive}{ADJ.}{全面的}{thorough; inclusive.}{This book provides a comprehensive review of verbal and math skills for the SAT.}
\entry{comprise}{V.}{包括}{include; consist of.}{If the District of Columbia were to be granted statehood, the United States of America would comprise fifty-one states, not just fifty.}
\entry{concede}{V.}{勉强, 让步, 屈从}{admit; yield.}{Despite all the evidence Monica had assembled, Mark refused to concede that she was right.}
\entry{concession}{N.}{让步}{an act of yielding.}{Before they could reach an agreement, both sides had to make certain concessions.}
\entry{conciliatory}{ADJ.}{抚慰, 调和}{reconciling; soothing.}{She was still angry despite his conciliatory words. conciliate,V.}
\entry{concise}{ADJ.}{简练}{brief and compact.}{When you define a new word, be concise: the shorter the definition, the easier it is to remember.}
\entry{conclusive}{ADJ.}{决定性的, 确实的}{}{}
\entry{concord}{N.}{和谐}{}{}
\entry{concur}{V.}{同意}{}{}
\entry{condemn}{V.}{谴责; 判刑}{}{}
\entry{condense}{V.}{浓缩, 精简}{}{}
\entry{condone}{V.}{宽恕, 容忍}{}{}
\entry{confine}{V.}{禁闭, 限制}{}{}
\entry{confluence}{N.}{汇合, 交汇处}{}{}
\entry{confound}{V.}{使困惑, 使混淆}{}{}
\entry{confrontation}{N.}{面对; 对质, 对抗}{}{}
\entry{congenital}{ADJ.}{天生的}{}{}
\entry{conjecture}{N. V.}{推测, 猜测}{}{}
\entry{conjure}{V.}{召唤, 变戏法, 想象}{}{}
\entry{consecrate}{V.}{献给}{}{}
\entry{consensus}{N.}{一致同意}{}{}
\entry{consistency}{N.}{一致性, 连贯, 密度}{}{}
\entry{conspicuous}{ADJ.}{明显的, 显著的}{}{}
\entry{constituent}{N.}{选民, 选举人}{}{}
\entry{constraint}{N.}{强制, 约束}{}{}
\entry{contaminate}{V.}{污染}{}{}
\entry{contend}{V.}{斗争, 竞争; 声称}{}{}
\entry{continence}{N.}{自制, 节欲}{}{}
\entry{contortion}{N.}{扭歪, 弯曲}{}{}
\entry{contract}{V.}{收缩; 订约, 感染}{}{}
\entry{contrite}{V.}{深感懊悔的}{}{}
\entry{controvert}{V.}{辩论; 反驳}{oppose with arguments; attempt to refute; contradict.}{The witness's testimony was so clear and her reputation for honesty so well-established that the defense attorney decided it was wiser to make no attempt to controvertwhat she said.}
\entry{convene}{V.}{召集, 集合}{assemble.}{Because much needed legislation had to be enacted, the governor ordered the legislature to convene in special session by January 15.}
\entry{converge}{V.}{聚合; 接近}{approach; tend to meet; come together.}{African-American men from all over the United States converged on Washington to take part in the historic Million Men march.}
\entry{converse}{N.}{相反的}{opposite.}{The inevitable converse of peace is not war but annihilation.}
\entry{conviction}{N.}{定罪; 深信}{judgment that someone is guilty of a crime; strongly held belief.}{Even her conviction for murder did not shake Peter's conviction that Harriet was innocent of the crime.}
\entry{copious}{ADJ.}{丰富的, 大量的}{plentiful.}{She had copious reasons for rejecting the proposal.}
\entry{correlation}{N.}{相互的关系}{mutual relationship.}{He sought to determine the correlation that existed between ability in algebra and ability to interpret reading exercises. correlate, V., N.}
\entry{corroborate}{V.}{确认; 支持}{confirm; support.}{Though Huck was quite willing to corroborate Tom's story, Aunt Polly knew better than to believe either of them.}
\entry{corrode}{V.}{腐蚀}{destroy by chemical action.}{The girders supporting the bridge corroded so gradually that no one suspected any danger until the bridge suddenly collapsed. corrosion, N.}
\entry{cosmic}{ADJ.}{宇宙的; 巨大的}{pertaining to the universe; vast.}{Cosmic rays derive their name from the fact that they bombard the earth's atmosphere from outer space. COSMOS, N.}
\entry{countenance}{V.}{忍受; 接受}{approve; tolerate.}{He refused to countenance such rude behavior on their part.}
\entry{counterpart}{N.}{补充物, 相似物}{}{}
\entry{covert}{ADJ.}{秘密的, 隐藏的}{}{}
\entry{cower}{V.}{畏缩}{}{}
\entry{crass}{ADJ.}{粗糙的}{}{}
\entry{craven}{ADJ.}{怯懦的}{}{}
\entry{credulity}{N.}{轻信; 易受骗}{}{}
\entry{creed}{N.}{信条}{}{}
\entry{criterion}{N.}{标准}{}{}
\entry{crop}{V.}{剪修}{}{}
\entry{cryptic}{ADJ.}{神秘的, 隐藏的, 秘密的}{}{}
\entry{culminate}{V.}{达至顶点}{}{}
\entry{culpable}{ADJ.}{该责备的}{}{}
\entry{cumulative}{ADJ.}{累积}{growing by addition.}{Vocabulary building is a cumulative process: as you go through your flash cards, you will add new words to your vocabulary, one by one.}
\entry{cupidity}{N.}{贪婪}{greed.}{The defeated people could not satisfy the cupidity of the conquerors, who demanded excessive tribute.}
\entry{cursory}{ADJ.}{草率; 匆忙}{casual; hastily done.}{Because a cursory examination of the ruins indicates the possibility of arson, we believe the insurance agency should undertake a more extensive investigation of the fire's cause.}
\entry{curtail}{V.}{减短; 降低}{shorten; reduce.}{When Herb asked Diane for a date, she said she was really sorry she couldn't go out with him, but her dad had ordered her to curtail her social life.}
\entry{cynical}{ADJ.}{愤世嫉俗}{skeptical or distrustful of human motives.}{Cynical from birth, Sidney was suspicious whenever anyone gave him a gift "with no strings attached." cynic, N.}
\entry{dank}{ADJ.}{湿的; 湿透的}{damp.}{The walls of the dungeon were dank and slimy.}
\entry{dapper}{ADJ.}{整齐的, 优雅的}{neat and trim.}{In "The Odd Couple" TV show, Tony Randall played Felix Unger, an excessively dapper soul who could not stand to have a hair out of place.}
\entry{dauntless}{ADJ.}{胆大的}{bold.}{Despite the dangerous nature of the undertaking, the dauntless soldier volunteered for the assignment.}
\entry{deadpan}{ADJ.}{没有表情的; 呆板的}{wooden; impersonal.}{We wanted to see how long he could maintain his deadpan expression.}
\entry{dearth}{N.}{稀缺; 缺乏}{scarcity.}{The dearth of skilled labor compelled the employers to open trade schools.}
\entry{debase}{V.}{贬低, 降低}{reduce in quality or value; lower in esteem; degrade.}{In The King and l, Anna refuses to kneel down and prostrate herself before the king, for she feels that to do so would debase her position, and she will not submit to such debasement.}
\entry{debilitate}{V.}{使虚弱, 衰弱}{weaken; enfeeble.}{Michael's severe bout of the flu debilitated him so much that he was too tired to go to work for a week.}
\entry{debris}{N.}{碎片; 残骸}{rubble.}{A full year after the earthquake in Mexico City, they were still carting away the debris.}
\end{multicols}
\clearpage
\setList{10-12}

\begin{multicols}{2}
\entry{debunk}{V.}{揭穿; 奚落}{expose as false, exaggerated, worthless, etc; ridicule.}{Pointing out that he consistently had voted against strengthening anti-pollution legislation, reporters debunked the candidate's claim that he was a fervent environmentalist.}
\entry{decadence}{N.}{颓废; 腐坏}{decay.}{The moral decadence of the people was reflected in the lewd literature of the period.}
\entry{decelerate}{V.}{减慢}{slow down.}{Seeing the emergency blinkers in the road ahead, he decelerated quickly.}
\entry{decorum}{N.}{礼貌; 温文尔雅}{propriety; orderliness and good taste in manners.}{Even the best-mannered students have trouble behaving with decorum on the last day of school. decorous,ADJ.}
\entry{decry}{V.}{强烈反对}{express strong disapproval of; disparage.}{The founder of the Children's Defense Fund, Marian Wright Edelman, strongly decries the lack of financial and moral support for children in America today.}
\entry{deducible}{ADJ.}{可推导的, 可推论的}{derived by reasoning.}{If we accept your premise, your conclusions are easily deducible.}
\entry{default}{N.}{不作为, 无动于衷}{failure to act.}{When the visiting team failed to show up for the big game, they lost the game by default. When Jack failed to make the payments on his Jaguar, the dealership took back the car because he had defaulted on his debt.}
\entry{defer}{V.}{推迟, 延期}{delay till later; exempt temporarily.}{In wartime, some young men immediately volunteer to serve; others}
\entry{deference}{N.}{尊重的, 尊重他人的}{courteous regard for another's wish.}{In deference to the minister's request, please do not take photographs during the wedding service.}
\entry{definitive}{ADJ.}{完全的; 最终的}{final; complete.}{Carl Sandburg's Abraham Lincoln may be regarded as the definitive work on the life of the Great Emancipator.}
\entry{deflect}{V.}{反射, 偏转}{turn aside.}{His life was saved when his cigarette case deflected the bullet.}
\entry{defuse}{V.}{拆弹; 化解（危机）}{remove the fuse of a bomb; reduce or eliminate a threat.}{Police negotiators are trained to defuse dangerous situations by avoiding confrontational language and behavior.}
\entry{degenerate}{V.}{恶化}{become worse; deteriorate.}{As the fight dragged on, the champion's style degenerated until he could barely keep on his feet.}
\entry{degradation}{N.}{降级; 降格; 退化}{humiliation; debasement; degeneration.}{Some secretaries object to fetching the boss a cup of coffee because they resent the degradation of being made to do such lowly tasks. degrade,V.}
\entry{dehydrate}{V.}{脱水}{remove water from; dry out.}{Running under a hot sun quickly dehydrates the body; joggers soon learn to carry water bottles and to drink from them frequently.}
\entry{delete}{V.}{删除}{erase; strike out.}{Less is more: if you delete this paragraph, your whole essay will have greater appeal.}
\entry{deleterious}{ADJ.}{有害的}{harmful.}{If you believe that smoking is deleterious to your health (and the Surgeon General certainly does), then quit!}
\entry{deliberate}{V.}{深思熟虑的; 商讨}{consider; ponder.}{Offered the new job, she asked for time to deliberate before she told them her decision,}
\entry{delineate}{V.}{描绘; 描述}{portray; depict; sketch.}{Using only a few descriptive phrases, Austen delineates the character of Mr. Collins so well that we can predict his every move. delineation, N.}
\entry{delusion}{N.}{错觉}{false belief; hallucination.}{Don suffers from delusions of grandeur: he thinks he's a world-famous author when he's published just one paperback book.}
\entry{demise}{N.}{死}{death.}{Upon the demise of the dictator, a bitter dispute about succession to power developed.}
\entry{denotation}{N.}{指示; 根据名字区别}{meaning; distinguishing by name.}{A dictionary will always give us the denotation of a word; frequently, it will also give us the connotations. denote,V.}
\entry{denounce}{V.}{咒骂; 批评}{condemn; criticize.}{The reform candidate denounced the corrupt city officers for having betrayed the public's trust. denunciation, N.}
\entry{depict}{V.}{描述}{portray.}{In this sensational exposé, the author depicts Beatle John Lennon as a drug-crazed neurotic. Do you question the accuracy of this depiction of Lennon?}
\entry{deplete}{V.}{耗尽; 减少}{reduce; exhaust.}{We must wait until we deplete our present inventory before we order replacements.}
\entry{deplore}{V.}{悔恨}{regret; disapprove of.}{Although I deplore the vulgarity of your language, I defend your right to express yourself freely.}
\entry{depose}{V.}{革职}{dethrone; remove from office.}{The army attempted to depose the king and set up a military government.}
\entry{depravity}{N.}{堕落, 腐坏}{extreme corruption; wickedness.}{The depravity of Caligula's behavior came to sicken even those who had willingly participated in his earlier, comparatively innocent orgies.}
\entry{deprecate}{V.}{抗议; 蔑视}{express disapproval of; protest against; belittle.}{A firm believer in old-fashioned courtesy, Miss Post deprecated the modern tendency to address new acquaintances by their first names. deprecatory,ADJ.}
\entry{depreciate}{V.}{折旧}{lessen in value.}{If you neglect this property, it will depreciate.}
\entry{deride}{V.}{打趣; 取消}{ridicule; make fun of.}{The critics derided his pretentious dialogue and refused to consider his play seriously. derision, N.}
\entry{desiccate}{V.}{弄干}{dry up.}{A tour of this smokehouse will give you an idea of how the pioneers used to desiccate food in order to preserve it.}
\entry{despise}{V.}{鄙视}{ look on with scorn; regard as worthless or distasteful.}{Mr. Bond, I despise spies; I look down on them as mean, despicable, honorless men, whom I would wipe from the face of the earth with as little concern as I would scrape dog droppings from the bottom of my shoe.}
\entry{despoil}{V.}{掠夺}{plunder.}{If you do not yield, I am afraid the enemy will despoil the countryside.}
\entry{despondent}{ADJ.}{忧郁的; 沮丧的}{depressed; gloomy.}{To the dismay of his parents, William became seriously despondent after he broke up with Jan; they despaired of finding a cure for his gloom. despondency, N.}
\entry{determination}{N.}{决定; 测量, 计算; 解决}{resolve; measurement or calculation; decision.}{Nothing could shake his determination that his children would get the best education that money could buy. Thanks to my pocket calculator, my determination of the answer to the problem took only seconds of my time.}
\entry{detrimental}{ADJ.}{有害的}{harmful; damaging.}{The candidate's acceptance of major financial contributions from a wellknown racist ultimately proved detrimental to his campaign, for he lost the backing of many of his early grassroots supporters. detriment, N.}
\entry{devious}{ADJ.}{拐弯抹角的; 偏僻的}{roundabout; erratic; not straightforward.}{The Joker's plan was so devious that it was only with great difficulty we could follow its shifts and dodges.}
\entry{devoid}{ADJ.}{缺乏的}{lacking.}{You may think her mind is a total void, but she's actually not devoid of intelligence. She just sounds like an airhead.}
\entry{diagnosis}{N.}{诊断}{art of identifying a disease; analysis of a condition.}{In medical school Margaret developed her skill at diagnosis, learning how to read volumes from a rapid pulse or a hacking cough. diagnose, V.; diagnostic,ADJ.}
\entry{differentiate}{V.}{区另, 鉴别}{}{}
\entry{diffidence}{N.}{无自信; 羞怯; 内向}{}{}
\entry{diffuse}{ADJ.}{（文章等）冗长的; 弥漫的, 四散的}{}{}
\entry{digression}{N.}{离题, 偏离}{}{}
\entry{dilatory}{ADJ.}{迟误的, 拖延的}{}{}
\entry{dilemma}{N.}{进退两难的窘境, 困境}{}{}
\entry{diligence}{N.}{勤勉, 勤奋}{}{}
\entry{diminution}{N.}{缩减, 降低}{}{}
\entry{disaffected}{ADJ.}{不忠的, 不满的}{}{}
\entry{disband}{V.}{解散, 遣散}{}{}
\entry{discerning}{ADJ.}{聪明的; 有洞察力的}{}{}
\entry{disclaim}{V.}{放弃; 否认}{}{}
\entry{disclose}{V.}{使显露; 揭露}{}{}
\entry{discomposure}{N.}{心乱; 不安}{agitation; loss of poise.}{Perpetually poised, Agent 7 never exhibited a moment's discomposure.}
\entry{discord}{N.}{冲突的; 不和谐的}{conflict; lack of harmony.}{Watching Tweedledum battle Tweedledee, Alice wondered what had caused this pointless discord.}
\entry{discount}{V.}{漠视; 解散}{disregard; dismiss.}{Be prepared to discount what he has to say about his ex-wife.}
\entry{discredit}{V.}{不信任; 丢脸}{defame; destroy confidence in; disbelieve.}{The campaign was highly negative in tone; each candidate tried to discredit the other.}
\entry{discrete}{ADJ.}{分离; 没有关系的}{separate; unconnected.}{The universe is composed of discrete bodies.}
\entry{discriminating}{ADJ.}{有识别能力的; 有偏见的}{able to see differences; prejudiced.}{A superb interpreter of Picasso, she was sufficiently discriminating to judge the most complex works of modern art. (secondary meaning) discrimination, N.}
\entry{disdain}{V.}{蔑视}{view with scorn or contempt.}{In the film Funny Face, the bookish heroine disdained fashion models for their lack of intellectual interests. also N.}
\entry{disgruntle}{V.}{使郁闷}{make discontented.}{The passengers were disgruntled by the numerous delays.}
\entry{disinclination}{N.}{不情愿, 厌恶}{unwillingness.}{Some mornings I feel a great disinclination to get out of bed}
\entry{disinterested}{ADJ.}{公允的}{unprejudiced.}{Given the judge's political ambitions and the lawyers' financial interest in the case, the only disinterested person in the courtroom may have been the court reporter.}
\entry{dismay}{V.}{使沮丧; 使害怕}{discourage; frighten.}{The huge amount of work she had left to do dismayed her. also N.}
\entry{dismiss}{V.}{拒绝; 排除}{put away from consideration; reject.}{Believing in John's love for her, she dismissed the notion that he might be unfaithful. (secondary meaning)}
\entry{disparage}{V.}{忽略, 轻视}{belittle.}{A doting mother, Emma was more likely to praise her son's crude attempts at art than to disparage them.}
\entry{disparate}{ADJ.}{大相径庭的; 没关系的}{basically different; unrelated.}{Unfortunately, Tony and Tina have disparate notions of marriage: Tony sees it as a carefree extended love affair, while Tina sees it as a solemn commitment to build a family and a home.}
\entry{disperse}{V.}{散开}{scatter.}{The police fired tear gas into the crowd to disperse the protesters. dispersion, N.}
\entry{dissent}{V.}{反对}{disagree.}{In the recent Supreme Court decision, Justice O'Connor dissented from the majority opinion. also N.}
\entry{distant}{ADJ.}{冷漠的; 远离的}{reserved or aloof; cold in manner.}{His distant greeting made me feel unwelcome from the start. (secondary meaning)}
\entry{distend}{V.}{扩大; 扩张}{expand; swell out.}{I can tell when he is under stress by the way the veins distend on his forehead.}
\entry{distinction}{N.}{出名; 出格}{honor; contrast; discrimination.}{A holder of the Medal of Honor, George served with great distinction in World War II. He made a distinction, however, between World War II and Vietnam, which he considered an immoral conflict.}
\entry{distort}{V.}{扭曲, 歪曲}{twist out of shape.}{It is difficult to believe the newspaper accounts of the riots because of the way some reporters distort and exaggerate the actual events. distortion, N.}
\entry{diverge}{V.}{多样的; 各异的}{vary; go in different directions from the same point.}{The spokes of the wheel diverge from the hub.}
\entry{diversity}{N.}{多样性}{variety; dissimilitude.}{The diversity of colleges in this country indicates that many levels of ability are being cared for.}
\entry{doctrine}{N.}{教育; 学说}{teachings, in general; particular principle (religious, legal, etc.}{ taught. He was so committed to the doctrines of his faith that he was unable to evaluate them impartially.}
\entry{document}{V.}{书面证明}{provide written evidence.}{She kept all the receipts from her business trip in order to document her expenses for the firm. also N.}
\entry{dogmatic}{ADJ.}{独断的, 教条的, 固执的}{opinionated; arbitrary; doctrinal.}{We tried to discourage Doug from being so dogmatic, but never could convince him that his opinions might be wrong.}
\entry{dubious}{ADJ.}{可疑的}{questionable; filled with doubt.}{Many critics of SAT I contend the test is of dubious worth. Jay claimed he could get a perfect 16 on SAT I, but Ellen was dubious: she knew he hadn't cracked a book in three years.}
\entry{dutiful}{ADJ.}{恭敬的; 尊重的}{respectful; obedient.}{When Mother told Billy to kiss Great-Aunt Hattie, the boy obediently gave the old woman a dutiful peck on her cheek.}
\entry{dwarf}{V.}{使看上去矮小}{cause to seem small.}{The giant redwoods and high cliffs dwarfed the elegant Ahwahnee Hotel, making it appear a modest lodge rather than an imposing hostelry.}
\entry{dynamic}{ADJ.}{充满活力的}{energetic; vigorously active.}{The dynamic aerobics instructor kept her students on the run; she was a little dynamo.}
\entry{ebullient}{ADJ.}{热情的, 激动的}{showing excitement; overflowing with enthusiasm.}{Amy's ebullient nature could not be repressed; she' was always bubbling over with excitement. ebullience, N.}
\entry{eccentric}{ADJ.}{古怪的, 奇怪的}{irregular; odd; whimsical; bizarre.}{The comet veered dangerously close to the earth in its eccentric orbit. People came up with some eccentric ideas for dealing with the emergency: someone even suggested tieing a knot in the comet's tail!}
\entry{eclectic}{ADJ.}{折衷的}{composed of elements drawn from disparate sources.}{His style of interior decoration was eclectic: bits and pieces of furnishings from widely divergent periods, strikingly juxtaposed to create a unique decor. eclecticism, N.}
\entry{eclipse}{V.}{超越; 衰落; 失色}{darken; extinguish; surpass.}{The new stock market high eclipsed the previous record set in 1995.}
\entry{edify}{V.}{教导; 启迪, 陶冶}{instruct; correct morally.}{Although his purpose was to edify and not to entertain his audience, many of his listeners were amused rather than enlightened.}
\entry{efface}{V.}{抹掉}{rub out.}{The coin had been handled so many times that its date had been effaced.}
\entry{effervescence}{N.}{泡腾, 沸腾; 兴奋, 活泼}{inner excitement or exuberance; bubbling from fermentation or carbonation.}{Nothing depressed Sue for long; her natural effervescence soon reasserted itself. Soda that loses its effervescence goes flat. effervescent, ADJ. effervesce,V.}
\entry{effete}{ADJ.}{软弱的, 懦弱的, 女人气的}{}{}
\entry{efficacy}{N.}{功效}{power to produce desired effect.}{The efficacy of this drug depends on the regularity of the dosage. efficacious,ADJ.}
\entry{egotistical}{ADJ.}{极度自我中心; 自以为是, 逞能}{excessively self-centered; self-important; conceited.}{Typical egotistical remark: "But enough of this chit-chat about you and your little problems. Let's talk about what's really important: Me!"}
\entry{elated}{ADJ.}{过分高兴的; 兴高采烈}{overjoyed; in high spirits.}{Grinning from ear to ear, Bonnie Blair was clearly elated by her fifth Olympic gold medal. elation, N.}
\entry{elegy}{N.}{挽歌, 悲歌}{poem or song expressing lamentation.}{On the death of Edward King, Milton composed the elegy "Lycidas." elegiacal,ADJ.}
\entry{elicit}{V.}{得出}{draw out by discussion.}{The detectives tried to elicit where he had hidden his loot.}
\entry{elliptical}{ADJ.}{椭圆的; 有意模棱两可的}{oval; ambiguous, either purposely or because key words have been left out.}{An elliptical billiard ball wobbles because it is not perfectly round; an elliptical remark baffles because it is not perfectly clear.}
\entry{eloquence}{N.}{雄辩; 修辞}{expressiveness; persuasive speech.}{The crowds were stirred by Martin Luther King's eloquence. eloquent,ADJ.}
\entry{elucidate}{V.}{解释; 启迪}{explain; enlighten.}{He was called upon to elucidate the disputed points in his article.}
\entry{elusive}{ADJ.}{难懂的, 难捉摸的; 令人困惑的}{evasive; baffling; hard to grasp.}{Trying to pin down exactly when the contractors would be finished remodeling the house, Nancy was frustrated by their elusive replies. elude,V.}
\entry{emanate}{V.}{散发, 发出}{issue forth.}{A strong odor of sulphur emanated from the spring.}
\end{multicols}
\clearpage
\setList{13-15}

\begin{multicols}{2}
\entry{embark}{V.}{开始旅程, 开始, 登机, 上船, 上车}{commence; go on board a boat or airplane; begin a journey.}{In devoting herself to the study of gorillas, Dian Fossey embarked on a course of action that was to cost her her life.}
\entry{embed}{V.}{封装, 嵌入, 插入}{enclose; place in something.}{Tales of actual historical figures like King Alfred have become embedded in legends.}
\entry{embellish}{V.}{装饰}{adorn; ornament.}{The costume designer embellished the leading lady's ball gown with yards and yards of ribbon and lace.}
\entry{embody}{V.}{具体化; 包含, 收录}{personify; make concrete; incorporate.}{Cheering on his rival Mark McGwire's efforts to break Roger Maris's home run record, Sammy Sosa embodied the spirit of true sportsmanship.}
\entry{embrace}{V.}{拥抱; 接受, 包含}{hug; adopt or espouse; accept readily; encircle; include.}{Clasping Maid Marian in his arms, Robin Hood embraced her lovingly. In joining the outlaws in Sherwood Forest, she had openly embraced their cause.}
\entry{embryonic}{ADJ.}{胚胎的; 未开发的, 原始的}{undeveloped; rudimentary.}{The evil of class and race hatred must be eliminated while it is still in an embryonic state; otherwise, it may grow to dangerous proportions. emend V. correct; correct by a critic. The critic emended the book by selecting the passages which he thought most appropriate to the text.}
\entry{emend}{V.}{校订, 修改}{}{}
\entry{empathy}{N.}{移情作用, 心入}{ability to identify with another's feelings, ideas, etc.}{What made Ann such a fine counselor was her empathy, her ability to put herself in her client's place and feel his emotions as if they were her own. empathize,V.}
\entry{emulate}{V.}{仿效; 抗衡}{imitate; rival.}{In a brief essay, describe a person you admire, someone whose virtues you would like to emulate.}
\entry{encompass}{V.}{包围}{surround.}{Although we were encompassed by enemy forces, we were cheerful for we were well stocked and could withstand a siege until our allies joined us.}
\entry{endorse}{V.}{认可, 默许; 支持}{approve; support.}{Everyone waited to see which one of the rival candidates for the city council the mayor would endorse. (secondary meaning) endorsement, N.}
\entry{enduring}{ADJ.}{持久的; 不朽的}{lasting; surviving.}{Keats believed in the enduring power of great art, which would outlast its creators' brief lives.}
\entry{energize}{V.}{鼓舞}{invigorate; make forceful and active.}{Rather than exhausting Maggie, dancing energized her.}
\entry{enfranchise}{V.}{赋予公民权（投票权）}{to admit to the rights of citizenship (especially the right to vote).}{Although Blacks were enfranchised shortly after the Civil War, women did not receive the right to vote until 192.}
\entry{engage}{V.}{吸引; 雇佣; 答应; 结合; 订婚}{attract; hire; pledge oneself; confront.}{"Your case has engaged my interest, my lord," said Holmes. "You may engage my services."}
\entry{engender}{V.}{产生, 导致}{cause; produce.}{To receive praise for real accomplishments engenders self-confidence in a child.}
\entry{enormity}{N.}{巨大的, 严重的, 极恶劣}{hugeness (in a bad sense).}{He did not realize the enormity of his crime until he saw what suffering he had caused.}
\entry{entail}{V.}{要求, 需要; 牵涉到}{require; necessitate; involve.}{Building a collegelevel vocabulary will entail some work on your part.}
\entry{entice}{V.}{吸引; 引诱}{lure; attract; tempt.}{She always tried to entice her baby brother into mischief.}
\entry{entitlement}{N.}{权利}{right to claim something; right to benefits.}{While Bill was entitled to use a company car while he worked for the firm, the company's lawyers questioned his entitlement to the vehicle once he'd quit his job.}
\entry{entrance}{V.}{使其着迷; 使其神志恍惚}{put under a spell; carry away with emotion.}{Shafts of sunlight on a wall could entrance her and leave her spellbound.}
\entry{entreat}{V.}{恳求}{plead; ask earnestly.}{She entreated her father to let her stay out till midnight.}
\entry{enumerate}{V.}{枚举}{list; mention one by one.}{Huck hung his head in shame as Miss Watson enumerated his many flaws.}
\entry{ephemeral}{ADJ.}{朝生暮死, 短暂, 短命}{short-lived; fleeting.}{The mayfly is an ephemeral creature: its adult life lasts little more than a day.}
\entry{epoch}{N.}{时代}{period of time.}{The glacial epoch lasted for thousands of years.}
\entry{equable}{ADJ.}{平静的, 均衡的, 稳定的}{tranquil; steady; uniform.}{After the hot summers and cold winters of New England, he found the climate of the West Indies equable and pleasant.}
\entry{equitable}{ADJ.}{公平的, 公允的}{fair; impartial.}{I am seeking an equitable solution to this dispute, one that will be fair and acceptable to both sides.}
\entry{equivocal}{ADJ.}{蓄意误导; 含混, 模棱两可}{ambiguous; intentionally misleading.}{Rejecting the candidate's equivocal comments on tax reform, the reporters pressed him to state clearly where he stood on the issue. equivocate,V.}
\entry{erode}{V.}{侵蚀}{eat away.}{The limestone was eroded by the dripping water until only a thin shell remained. erosion, N.}
\entry{erroneous}{ADJ.}{错误}{mistaken; wrong.}{I thought my answer was correct, but it was erroneous.}
\entry{esoteric}{ADJ.}{难以理解的, 深奥的}{hard to understand; known only to the chosen few.}{The New Yorker short stories often include esoteric allusions to obscure people and events: the implication is, if you are in the in-crowd, you'll get the reference; if you come from Cleveland, you won't.}
\entry{esteem}{V.}{尊重; 估价}{respect; value.}{Jill esteemed Jack's taste in music, but she deplored his taste in clothes.}
\entry{ethnic}{ADJ.}{种族的}{relating to races.}{Intolerance between ethnic groups is deplorable and usually is based on lack of information.}
\entry{euphemism}{N.}{委婉的表达}{mild expression in place of an unpleasant one.}{The expression "he passed away" is a euphemism for "he died."}
\entry{euphoria}{N.}{非常愉快; 病态的愉快, 愉悦症}{feeling of great happiness and well-being (sometimes exaggerated).}{Delighted with her SAT scores, sure that the university would accept her, Allison was filled with euphoria. euphoric,ADJ.}
\entry{evanescent}{ADJ.}{消散的; 凋零的}{fleeting; vanishing.}{Brandon's satisfaction in his new job was evanescent, for he immediately began to notice its many drawbacks. evanescence, N.}
\entry{evocative}{ADJ.}{唤起的}{tending to call up (emotions, memories).}{Scent can be remarkably evocative: the aroma of pipe tobacco evokes the memory of my father; a whiff of talcum powder calls up images of my daughter as a child.}
\entry{exacerbate}{V.}{恶化, 加剧}{worsen; embitter.}{The latest bombing exacerbated England's already existing bitterness against the IRA, causing the prime minister to break off the peace talks abruptly.}
\entry{exalt}{V.}{晋升; 赞扬}{raise in rank or dignity; praise.}{The actor Alec Guinness was exalted to the rank of knighthood by the queen.}
\entry{exceptionable}{ADJ.}{不可的, 可反对的}{objectionable.}{Do you find the punk rock band Green Day a highly exceptionable, thoroughly distasteful group, or do you think they are exceptionally talented performers?}
\entry{excise}{V.}{去除}{cut away; cut out.}{When you excise the dead and dying limbs of a tree, you not only improve its appearance but also enhance its chances of bearing fruit. excision. N.}
\entry{exclaim}{V.}{呼喊, 大叫}{cry out suddenly.}{"Watson! Behind you!" Holmes exclaimed, seeing the assassin hurl himself on his friend.}
\entry{execute}{V.}{执行, 完成}{put into effect; carry out.}{The choreographer wanted to see how well she could execute a pirouette. (secondary meaning) execution, N.}
\entry{exemplary}{ADJ.}{出色的; 典范的; （杀鸡儆猴的）例子}{serving as a model; outstanding.}{At commencement the dean praised Ellen for her exemplary behavior as class president.}
\entry{exemplify}{V.}{作为典型; 具体化}{serve as an example of; embody.}{For a generation of balletgoers, Rudolf Nureyev exemplified the ideal of masculine grace.}
\entry{exempt}{ADJ.}{被免除的}{not subject to a duty, obligation.}{Because of his flat feet, Foster was exempt from serving in the armed forces. alsoV.}
\entry{exhaustive}{ADJ.}{彻底的, 完全的}{thorough; comprehensive.}{We have made an exhaustive study of all published SAT tests and are happy to share our research with you.}
\entry{exonerate}{V.}{开脱, 免罪}{acquit; exculpate.}{The defense team feverishly sought fresh evidence that might exonerate their client.}
\entry{exotic}{ADJ.}{陌生的, 外来的, 奇异的, 异国情调}{not native; strange.}{Because of his exotic headdress, he was followed in the streets by small children who laughed at his strange appearance.}
\entry{expansive}{ADJ.}{扩张的; 爽快的; 广阔的}{outgoing and sociable; broad and extensive; able to increase in size.}{Mr. Fezziwig was in an expansive humor, cheerfully urging his guests to join in the Christmas feast. Looking down on his expansive paunch, he sighed: if his belly expanded any further, he'd need an expansive waistline for his pants.}
\entry{expedite}{V.}{加速, 催促}{hasten.}{Because we are on a tight schedule, we hope you will be able to expedite the delivery of our order. The more expeditious your response is, the happier we'll be.}
\entry{expertise}{N.}{专业知识, 技能}{specialized knowledge; expert skill.}{Although she was knowledgeable in a number of fields, she was hired for her particular expertise in computer programming.}
\entry{explicate}{V.}{解释, 澄清}{explain; interpret; clarify.}{Harry Levin explicated James Joyce's often bewildering novels with such clarity that even Finnegan's Wake seemed comprehensible to his students.}
\entry{exploit}{N.}{壮举}{deed or action, particularly a brave deed.}{Raoul Wallenberg was noted for his exploits in rescuing Jews from Hitler's forces.}
\entry{exposure}{N.}{曝光, 揭露; 暴露（于疾病、恶劣的环境等）的状态}{risk, particularly of being exposed to disease or to the elements; unmasking; act of laying something open.}{Exposure to sun and wind had dried out her hair and weathered her face. She looked so changed that she no longer feared exposure as the notorious Irene Adler, onetime antagonist of Sherlock Holmes.}
\entry{extent}{N.}{范围; 程度}{degree; magnitude; scope.}{What is the extentof the patient's injuries? If they are not too extensive, we can treat him on an outpatient basis.}
\entry{extraneous}{ADJ.}{肤浅的, 不重要的}{not essential; superfluous.}{No wonder Ted can't think straight! His mind is so cluttered up with extraneous trivia, he can't concentrate on the essentials.}
\entry{extricate}{V.}{解脱, 放出, 释放}{free; disentangle.}{Icebreakers were needed to extricate the trapped whales from the icy floes that closed them in.}
\entry{extrovert}{N.}{性格外向的人}{person interested mostly in external objects and actions.}{A good salesman is usually an extrovert, who likes to mingle with people.}
\entry{extrude}{V.}{挤压, 逼}{force or push out.}{Much pressure is required to extrude these plastics.}
\entry{fabricate}{V.}{制造; 编造（谎言）}{build; lie.}{If we fabricate the buildings in this project out of standardized sections, we can reduce construction costs considerably. Because of Jack's tendency to fabricate, Jill had trouble believing a word he said.}
\entry{facet}{N.}{（宝石的）琢面; 方面}{small plane surface (of a gem); a side.}{The stonecutter decided to improve the rough diamond by providing it with several facets.}
\entry{facilitate}{V.}{促进; 帮助; 使变容易}{help bring about; make less difficult.}{Rest and proper nourishment should facilitate the patient's recovery.}
\entry{faculty}{N.}{才能, 教职员工}{mental or bodily powers; teaching staff.}{As he grew old, Professor Twiggly feared he might lose his faculties and become unfit to teach. However, he had tenure: whether or not he was in full possession of his faculties, the school couldn't kick him off the faculty.}
\entry{fallow}{ADJ.}{休耕地; 潜伏的; 不活跃的}{plowed but not sowed; uncultivated.}{Farmers have learned that it is advisable to permit land to lie fallow every few years.}
\entry{fanaticism}{N.}{狂热的, 盲目的}{excessive zeal; extreme devotion to a belief or cause.}{When Islamic fundamentalists demanded the death of Salman Rushdie because his novel questioned their faith, world opinion condemned them for their fanaticism.}
\entry{fathom}{V.}{领会; 调查, 测量}{comprehend; investigate.}{I find his motives impossible to fathom; in fact, I'm totally clueless about what goes on in his mind.}
\entry{feasible}{ADJ.}{可行的}{practical.}{Is it feasible to build a new stadium for the Yankees on New York's West Side? Without additional funding, the project is clearly unrealistic.}
\entry{fell}{ADJ.}{凶猛的, 致命的}{cruel; deadly.}{The newspapers told of the tragic spread of the fell disease.}
\entry{ferment}{N.}{激怒; 挑起骚动、暴乱}{agitation; commotion.}{With the breakup of the Soviet Union, much of Eastern Europe was in a state of ferment.}
\entry{fervor}{N.}{热情; 激情}{glowing ardor; intensity of feeling.}{At the protest rally, the students cheered the strikers and booed the dean with equal fervor.}
\entry{fester}{V.}{使溃烂, 化脓}{rankle; produce irritation or resentment.}{Joe's insult festered in Anne's mind for days, and made her too angry to speak to him.}
\entry{festive}{ADJ.}{欢乐; 庆祝}{joyous; celebratory.}{Their wedding in the park was a festive occasion.}
\entry{fictitious}{ADJ.}{想象的}{imaginary.}{Although this book purports to be a biography of George Washington, many of the incidents are fictitious.}
\entry{figment}{N.}{发明; 臆造的事务}{invention; imaginary thing.}{That incident never took place; it is a figment of your imagination.}
\entry{finesse}{N.}{精密的技巧}{delicate skill.}{The finesse and adroitness with which the surgeon wielded her scalpel impressed all the observers in the operating room.}
\entry{fitful}{ADJ.}{断断续续; 间歇}{spasmodic; intermittent.}{After several fitful attempts, he decided to postpone the start of the project until he felt more energetic.}
\entry{flag}{V.}{萎缩; 衰退}{droop; grow feeble.}{When the opposing hockey team scored its third goal only minutes into the first quarter, the home team's spirits flagged. flagging,ADJ.}
\entry{flaunt}{V.}{招摇; 炫耀}{display ostentatiously.}{Mae West saw nothing wrong with showing off her considerable physical charms, saying, "Honey, if you've got it, flaunt it!"}
\entry{flinch}{V.}{畏首畏尾, 退缩; 犹豫}{hesitate, shrink.}{He did not flinch in the face of danger but fought back bravely.}
\entry{flora}{N.}{植物志}{plants of a region or era.}{Because she was a botanist, she spent most of her time studying the flora of the desert.}
\entry{florid}{ADJ.}{华丽的; 红润的}{ruddy; reddish; flowery.}{If you go to Florida and get a sunburn, your complexion will look florid.}
\entry{flourish}{V.}{生长; 繁荣; 装饰}{grow well; prosper; decorate with ornaments.}{The orange trees flourished in the sun.}
\entry{fluctuate}{V.}{波动的; 起伏的, 摇摆不定的}{waver; shift.}{The water pressure in our shower fluctuates wildly; you start rinsing yourself off with a trickle, and, two minutes later, a blast of water nearly knocks you down.}
\entry{fluency}{N.}{（语言）流利}{smoothness of speech.}{He spoke French with fluency and ease.}
\entry{fluke}{N.}{意外; 小概率事件}{unlikely occurrence; stroke of fortune.}{When Dou- glas defeated Tyson for the heavyweight championship, some sportscasters dismissed his victory as a fluke.}
\entry{foment}{V.}{鼓动, 煽动}{stir up; instigate.}{Cheryl's archenemy Heather spread some nasty rumors that fomented trouble in the club. Do you think Cheryl's foe meant to foment such discord?}
\entry{foolhardy}{ADJ.}{愚勇的; 傻大胆儿}{rash.}{Don't be foolhardy. Get the advice of experienced people before undertaking this venture.}
\entry{forbearance}{N.}{耐心}{patience.}{We must use forbearance in dealing with him because he is still weak from his illness.}
\entry{forebears}{N.}{前人; 祖先}{ancestors.}{Reverence for one's forebears (sometimes referred to as ancestor worship) plays an important part in many Oriental cultures.}
\entry{foreshadow}{V.}{预言; 预测}{give an indication beforehand; portend; prefigure.}{In retrospect, political analysts realized that Yeltsin's defiance of the attempted coup foreshadowed his emergence as the dominant figure of the new Russian republic.}
\entry{foresight}{N.}{洞察力}{ability to foresee future happenings; prudence.}{A wise investor, she had the foresight to buy land just before the current real estate boom.}
\entry{forestall}{V.}{预防}{prevent by taking action in advance.}{By setting up a prenuptial agreement, the prospective bride and groom hoped to forestall any potential arguments about money in the event of a divorce.}
\entry{forgo}{V.}{放弃}{give up; do without.}{Determined to lose weight for the summer, Ida decided to forgo dessert until she could fit into a size eight again.}
\entry{formidable}{ADJ.}{威胁的, 险恶的}{menacing; threatening.}{We must not treat the battle lightly for we are facing a formidable foe.}
\entry{forsake}{V.}{放弃}{desert; abandon; renounce.}{No one expected Foster to forsake his wife and children and run off with another woman.}
\entry{forthright}{ADJ.}{坦率的; 豪爽的}{outspoken; straightforward; frank.}{Never afraid to call a spade a spade, she was perhaps too forthrightto be a successful party politician.}
\entry{foster}{V.}{养育, 培养; 鼓励}{rear; encourage.}{According to the legend, Romulus and Remus were fostered by a she-wolf who raised the abandoned infants with her own cubs. alsoADJ.}
\entry{frail}{ADJ.}{弱的}{weak.}{The delicate child seemed too frail to lift the heavy carton. frailty, N.}
\entry{friction}{N.}{摩擦}{clash in opinion; rubbing against.}{At this time when harmony is essential, we cannot afford to have any friction in our group.}
\end{multicols}
\clearpage
\setList{16-18}

\begin{multicols}{2}
\entry{fruition}{N.}{享用; 成就; 实现}{bearing of fruit; fulfillment; realization.}{This building marks the fruition of all our aspirations and years of hard work.}
\entry{frustrate}{V.}{阻碍; 挫败}{thwart; defeat.}{We must frustrate this dictator's plan to seize control of the government.}
\entry{fundamental}{V.}{基本的, 基础的}{basic; primary; essential.}{The committee discussed all sorts of side issues without ever getting down to addressing the fundamental problem.}
\entry{furtive}{ADJ.}{隐秘的; 偷偷摸摸, 鬼祟}{stealthy; sneaky.}{Noticing the furtive glance the customer gave the diamond bracelet on the counter, the jeweler wondered whether he had a potential shoplifter on his hands.}
\entry{futile}{ADJ.}{没出息; 无望, 没效果的}{useless; hopeless; ineffectual.}{It is futile for me to try to get any work done around here while the telephone is ringing every thirty seconds. futility, N.}
\entry{galaxy}{N.}{星系; 一群显赫的人; 一系列重要的人或物}{large, isolated system of stars, such as the Milky Way; any collection of brilliant personalities.}{Science fiction stories speculate about the possible existence of life in other galaxies. The deaths of such famous actors as John Candy and George Burns tells us that the galaxy of Hollywood superstars is rapidly disappearing.}
\entry{gale}{N.}{大风; 一阵感情的爆发}{windstorm; gust of wind; emotional outburst (laughter, tears).}{The Weather Channel warned viewers about a rising gale, with winds of up to sixty miles per hour.}
\entry{garbled}{ADJ.}{混淆}{mixed up; jumbled; distorted.}{A favorite party game involves passing a whispered message from one person to another until, by the time it reaches the last player, the message is totally garbled.}
\entry{garrulous}{ADJ.}{贫嘴}{loquacious; wordy; talkative.}{My Uncle Henry can out-talk any three people I know. He is the most garrulous person in Cayuga County. garrulity, N.}
\entry{generality}{N.}{一般性}{vague statement.}{This report is filled with generalities; be more specific in your statements.}
\entry{generate}{V.}{产生; 创造}{cause; produce; create.}{In his first days in office, President Clinton managed to generate a new mood of optimism; we just hoped he could generate some new jobs.}
\entry{germinal}{ADJ.}{未成熟的, 幼芽的}{pertaining to a germ; creative.}{Such an idea is germinal, I am certain that it will influence thinkers and philosophers for many generations.}
\entry{germinate}{V.}{发芽}{cause to sprout; sprout.}{After the seeds germinate and develop their permanent leaves, the plants may be removed from the cold frames and transplanted to the garden.}
\entry{gist}{N.}{精华}{essence.}{She was asked to give the gist of the essay in two sentences.}
\entry{glacial}{ADJ.}{冰河的, 冰川的}{like a glacier; extremely cold.}{Never a warm person, when offended John could seem positively glacial.}
\entry{glaring}{ADJ.}{耀眼的}{highly conspicuous; harshly bright.}{Glaring spelling or grammatical errors in your resume will unfavorably impress potential employers.}
\entry{glimmer}{V.}{闪烁}{shine erratically; twinkle.}{In the darkness of the cavern, the glowworms hanging from the cavern roof glimmered like distant stars,}
\entry{grandeur}{N.}{庄严, 伟大, 威严}{impressiveness; stateliness; majesty.}{No matter how often he hiked through the mountains, David never failed to be struck by the grandeur of the Sierra Nevada range.}
\entry{graphic}{ADJ.}{图像的; 图画的}{pertaining to the art of delineating; vividly described.}{I was particularly impressed by the graphic presentation of the storm.}
\entry{gratify}{V.}{取悦}{please.}{Lori's parents were gratified by her successful performance on the SAT.}
\entry{gratuitous}{ADJ.}{无条件的; 无理由的; 免费的}{given freely; unwarranted; uncalled for.}{Quit making gratuitous comments about my driving; no one asked you for your opinion.}
\entry{gravity}{N.}{重力; 严重, 庄严, 严肃}{seriousness.}{We could tell we were in serious trouble from the gravity of the principal's expression. (secondary meaning) grave,ADJ.}
\entry{grimace}{N.}{扭曲的脸; 做鬼脸}{a facial distortion to show feeling such as pain, disgust, etc.}{Even though he remained silent, his grimace indicated his displeasure. alsoV.}
\entry{guile}{N.}{奸诈狡猾; 诡计}{deceit; duplicity; wiliness; cunning.}{lago uses considerable guile to trick Othello into believing that Desdemona has been unfaithful.}
\entry{gullible}{ADJ.}{易受骗的}{easily deceived.}{Overly gullible people have only themselves to blame if they fall for con artists repeatedly. As the saying goes, "Fool me once, shame on you. Fool me twice, shame on me."}
\entry{hackneyed}{ADJ.}{常见的; 不希罕, 陈腐}{commonplace; trite.}{When the reviewer criticized the movie for its hackneyed plot, we agreed; we had seen similar stories hundreds of times before.}
\entry{hallowed}{ADJ.}{神圣化的}{blessed; consecrated.}{Although the dead girl's parents had never been active churchgoers, they insisted that their daughter be buried in hallowed ground.}
\entry{hallucination}{N.}{幻觉, 幻想}{delusion.}{I think you were frightened by a hallucination you created in your own mind.}
\entry{halting}{ADJ.}{犹豫的}{hesitant; faltering.}{Novice extemporaneous speakers often talk in a halting fashion as they grope for the right words.}
\entry{hamper}{V.}{阻挡, 牵制, 妨碍}{obstruct.}{The new mother didn't realize how much the effort of caring for an infant would hamper her ability to keep an immaculate house.}
\entry{harass}{V.}{烦恼}{to annoy by repeated attacks.}{When he could not pay his bills as quickly as he had promised, he was harassed by his creditors.}
\entry{harbor}{V.}{庇护; 隐藏}{provide a refuge for; hide.}{The church harbored illegal aliens who were political refugees.}
\entry{hardy}{ADJ.}{艰苦的; 勇敢的}{sturdy; robust; able to stand inclement weather.}{We asked the gardening expert to recommend particularly hardy plants that could withstand our harsh New England winters.}
\entry{haughtiness}{N.}{傲慢; 不逊}{pride; arrogance.}{When she realized that Darcy believed himself too good to dance with his inferiors, Elizabeth took great offense at his haughtiness.}
\entry{hazardous}{ADJ.}{危险}{angerous.}{Your occupation is too hazardous for insurance companies to consider your application.}
\entry{hazy}{ADJ.}{朦胧的; 模糊的}{slightly obscure.}{In hazy weather, you cannot see the top of this mountain.}
\entry{headstrong}{ADJ.}{硬脖子; 任性; 不屈}{stubborn; willful; unyielding.}{Because she refused to marry the man her parents had chosen for her, everyone scolded Minna and called her a foolish headstrong girl.}
\entry{herbivorous}{ADJ.}{吃粮食的（动物）}{grain-eating.}{Some herbivorous animals have two stomachs for digesting their food.}
\entry{heterogeneous}{ADJ.}{异类, 异种; 不纯}{dissimilar; mixed.}{This year's entering class is a remarkably heterogeneous body: it includes students from forty different states and twenty-six foreign countries, some the children of billionaires, others the offspring of welfare families. heterogenity, N.}
\entry{heyday}{N.}{鼎盛时期}{time of greatest success; prime.}{In their heyday, the San Francisco Forty-Niners won the Super Bowl two years running.}
\entry{hibernal}{ADJ.}{冬天的}{wintry.}{Bears prepare for their long hibernal sleep by overeating.}
\entry{hibernate}{V.}{冬眠}{sleep throughout the winter.}{Bears are one of the many species of animals that hibernate. hibernation, N.}
\entry{hierarchy}{N.}{分级, 排序了的}{arrangement by rank or standing; authoritarian body divided into ranks.}{To be low man on the totem pole is to have an inferior place in the hierarchy.}
\entry{histrionic}{ADJ.}{戏剧性的}{theatrical.}{He was proud of his histrionic ability and wanted to play the role of Hamlet, histrionics, N.}
\entry{hoard}{V.}{储藏}{stockpile; accumulate for future use.}{Whenever there are rumors of a food shortage, many people are tempted to hoard food. also N.}
\entry{hoax}{N.}{伎俩; 小聪明}{trick; practical joke.}{Embarrassed by the hoax, he reddened and left the room. alsoV.}
\entry{homogeneous}{ADJ.}{同类的}{of the same kind.}{Because the student body at Elite Prep was so homogeneous, Sara and James decided to send their daughter to a school that offered greater cultural diversity. homogenize,V.}
\entry{horticultural}{ADJ.}{园艺的}{pertaining to cultivation of gardens.}{When he bought his house, he began to look for flowers and decorative shrubs, and began to read books dealing with horticultural matters.}
\entry{host}{N.}{很多; 主人; 宿主}{great number; person entertaining guests; animal or plant from which a parasite gets its nourishment.}{You must attend to a host of details if you wish to succeed as host of a formal dinner party. Leeches are parasites that cling to their hosts and drink their hosts' blood.}
\entry{hostility}{N.}{不友好, 敌意}{unfriendliness; hatred.}{A child who has been the sole object of his parents' affection often feels hostility toward a new baby in the family, resenting the newcomer who has taken his place.}
\entry{hover}{V.}{逗留; 盘旋; 等待}{hang about; wait nearby.}{The police helicopter hovered above the accident.}
\entry{humane}{ADJ.}{仁慈}{marked by kindness or consideration.}{It is ironic that the Humane Society sometimes must show its compassion toward mistreated animals by killing them to put them out of their misery.}
\entry{humid}{ADJ.}{潮湿的}{damp.}{She could not stand the humid climate and moved to a drier area.}
\entry{humility}{N.}{谦逊}{humbleness of spirit.}{He spoke with a humility and lack of pride that impressed his listeners.}
\entry{husband}{V.}{节约}{use sparingly; conserve; save.}{Marathon runners must husband their energy so that they can keep going for the entire distance.}
\entry{hybrid}{N.}{混合的, 混血的}{mongrel; mixed breed.}{Mendel's formula explains the appearance of hybrids and pure species in breeding. alsoADJ.}
\entry{hyperbole}{N.}{夸张}{exaggeration; overstatement.}{As far as I'm concerned, Apple's claims about the new computer are pure hyperbole: no machine is that good!}
\entry{hypocritical}{ADJ.}{伪善; 欺骗}{pretending to be virtuous; deceiving.}{Believing Eddie to be interested only in his own advancement, Greg resented his hypocritical posing as a friend. hypocrisy, N.}
\entry{hypothetical}{ADJ.}{基于假设的, 设想的, 假想的}{based on assumptions or hypotheses; supposed.}{Suppose you are accepted by Harvard, Stanford, and Brown. Which one would you choose to attend? Remember, this is only a hypothetical situation. hypotheSiS, N.}
\entry{icon}{N.}{偶像, 象征; 图标}{religious image; idol.}{The icons on the walls of the church were painted in the 13th century.}
\entry{iconoclastic}{ADJ.}{打破旧习}{attacking cherished traditions.}{Deeply iconoclastic, Jean Genet deliberately set out to shock conventional theatergoers with his radical plays.}
\entry{ideology}{N.}{意识形态}{system of ideas of a group.}{For people who had grown up believing in the communist ideology, it was hard to adjust to capitalism.}
\entry{idiom}{N.}{习语; 成语}{expression whose meaning as a whole differs from the meanings of its individual words; distinctive style.}{The phrase "to lose one's marbles" is an idiom: if I say that Joe's lost his marbles, I'm not asking you to find some for him. I'm telling you idiomatically that he's crazy.}
\entry{ignite}{V.}{点燃}{kindle; light.}{When Desi crooned, "Baby, light my fire," literal-minded Lucy looked around for some paper to ignite.}
\entry{illicit}{ADJ.}{非法的}{illegal.}{The defense attorney maintained that his client had never performed any illicit action.}
\entry{illuminate}{V.}{照亮; 明朗; 澄清}{brighten; clear up or make understandable; enlighten.}{Just as a lamp can illuminate a dark room, a perceptive comment can illuminate a knotty problem.}
\entry{illusion}{N.}{幻觉}{misleading vision.}{It is easy to create an optical illusion in which lines of equal length appear different.}
\entry{immobility}{N.}{无法移动, 不可移动的}{state of being immovable.}{Modern armies cannot afford the luxury of immobility, as they are vulnerable to attack while standing still.}
\entry{immune}{ADJ.}{免疫; 抵抗}{resistant to; free or exempt from.}{Fortunately, Florence had contracted chicken pox as a child and was immune to it when her baby broke out in spots.}
\entry{immutable}{ADJ.}{不可动摇的, 不能改变的}{unchangeable.}{All things change over time; nothing is immutable.}
\entry{impair}{V.}{伤害}{injure; hurt.}{Drinking alcohol can impair your ability to drive safely; if you're going to drink, don't drive.}
\entry{impartial}{ADJ.}{公平的}{not biased; fair.}{Knowing she could not be impartial about her own child, Jo refused to judge any match in which Billy was competing.}
\entry{impassive}{ADJ.}{冷漠的}{without feeling; imperturbable; stoical.}{Refusing to let the enemy see how deeply shaken he was by his capture, the prisoner kept his face impassive.}
\entry{impede}{V.}{阻止; 拖延}{hinder; block; delay.}{A series of accidents impeded the launching of the space shuttle.}
\entry{impel}{V.}{驱使}{drive or force onward.}{A strong feeling of urgency impelled her; if she failed to finish the project right then, she knew that she would never get it done.}
\entry{impending}{ADJ.}{接近的; 附近的}{nearing; approaching.}{The entire country was saddened by the news of his impending death.}
\entry{imperative}{ADJ.}{及其重要, 及其关键}{absolutely necessary; critically important.}{It is imperative that you be extremely agreeable to GreatAunt Maud when she comes to tea: otherwise she might not leave you that million dollars in her will. also N.}
\entry{imperious}{ADJ.}{专横的}{domineering; haughty.}{Jane rather liked a man to be masterful, but Mr. Rochester seemed so bent on getting his own way that he was actually imperious!}
\entry{impetus}{N.}{动力; 动机}{incentive; stimulus; moving force.}{A new federal highway program would create jobs and give added impetus to our economic recovery.}
\entry{implausible}{ADJ.}{难以置信的; 不像是真的}{unlikely; unbelievable.}{Though her alibi seemed implausible, it in fact turned out to be true.}
\entry{implement}{V.}{贯彻, 实现; 用工具实现}{put into effect; supply with tools.}{The mayor was unwilling to implement the plan until she was sure it had the governor's backing. also N.}
\entry{implication}{N.}{含义; 暗示}{something hinted at or suggested.}{When Miss Watson said she hadn't seen her purse since the last time Jim was in the house, the implication was that she suspected Jim had taken it. imply,V.}
\entry{imply}{V.}{暗示; 表示}{suggest a meaning not expressed; signify.}{When Aunt Millie said, "My! That's a big piece of pie, young man!" was she implying that Bobby was being a glutton in helping himself to such a huge piece?}
\entry{import}{N.}{重要性, 意思}{}{}
\entry{importunate}{ADJ.}{胡搅蛮缠的; 苛刻的}{urging; demanding.}{He tried to hide from his importunate creditors until his allowance arrived.}
\entry{impregnable}{ADJ.}{不受影响的; 无敌的}{invulnerable.}{Until the development of the airplane as a military weapon, the fort was considered impregnable.}
\entry{impropriety}{N.}{不合适, 不恰当}{improperness; unsuitableness.}{Because of the impropriety of the punk rocker's slashed T-shirt and jeans, the management refused to admit him to the hotel's very formal dining room.}
\entry{impudence}{N.}{无礼; 厚颜无耻}{impertinence; insolence.}{Kissed on the cheek by a perfect stranger, Lady Catherine exclaimed, "Of all the nerve! Young man, I should have you horse-whipped for your impudence."}
\entry{inadvertently}{ADV.}{不经意的}{unintentionally; by oversight; carelessly.}{Judy's great fear was that she might inadvertently omit a question on the exam and mismark her whole answer sheet.}
\entry{inarticulate}{ADJ.}{不善于表达的; 口齿不清的}{speechless; producing indistinct speech.}{He became inarticulate with rage and uttered sounds without meaning.}
\entry{incense}{V.}{激怒}{enrage; infuriate.}{Cruelty to defenseless animals incensed Kit: the very idea brought tears of anger to her eyes.}
\entry{incentive}{N.}{刺激, 驱动}{spur; motive.}{Mike's strong desire to outshine his big sister was all the incentive he needed to do well in school.}
\entry{incidence}{N.}{发生; 发生率; 影响的范围、频度; 入射角; 关联, 相结合, 对接}{rate of occurrence; particular occurrence.}{Health professionals expressed great concern over the high incidence of infant mortality in major urban areas.}
\entry{incidental}{ADJ.}{不重要的; 少数的}{not essential; minor.}{The scholarship covered his major expenses at college and some of his incidental expenses as well.}
\entry{incisive}{ADJ.}{尖锐; 深刻, 激烈}{cutting; sharp.}{His incisive remarks made us see the fallacy in our plans.}
\entry{incite}{V.}{煽动, 刺激, 驱使}{arouse to action; goad; motivate; induce to exist.}{In a fiery speech, Mario incited his fellow students to go out on strike to protest the university's anti-affirmative action stand.}
\entry{incline}{N.}{倾斜, 斜面}{slope; slant.}{The architect recommended that the nursing home's ramp be rebuilt because its incline was too steep for wheelchairs.}
\entry{inclusive}{ADJ.}{包揽一切的}{tending to include all.}{The comedian turned down the invitation to join the Players' Club, saying any club that would let him in was too inclusive for him.}
\entry{incompatible}{ADJ.}{不和谐; 不兼容}{inharmonious.}{The married couple argued incessantly and finally decided to separate because they were incompatible. incompatibility, N.}
\entry{inconsequential}{ADJ.}{不合理的, 不重要的}{insignificant; unimportant.}{Brushing off Ali's apologies for having broken the wineglass, Tamara said, "Don't worry about it; it's inconsequential."}
\end{multicols}
\clearpage
\setList{19-21}

\begin{multicols}{2}
\entry{incur}{V.}{招致}{bring upon oneself.}{His parents refused to pay any future debts he might incur.}
\entry{indefatigable}{ADJ.}{疲倦}{tireless.}{Although the effort of taking out the garbage tired Wayne out for the entire morning, when it came to partying, he was indefatigable.}
\entry{indelible}{ADJ.}{去不掉的; 不可磨灭的}{not able to be erased.}{The indelible ink left a permanent mark on my shirt. Young Bill Clinton's meeting with President Kennedy made an indelible impression on the youth.}
\entry{indeterminate}{ADJ.}{不确定}{uncertain; not clearly fixed; indefinite.}{That interest rates shall rise appears certain; when they will do so, however, remains indeterminate.}
\entry{indict}{V.}{控告; 起诉}{charge.}{The district attorney didn't want to indict the suspect until she was sure she had a strong enough case to convince a jury. indictment, N.}
\entry{indifferent}{ADJ.}{普通的, 无关紧要的}{unmoved or unconcerned by; mediocre.}{Because Ann felt no desire to marry, she was indifferent to Carl's constant proposals. Not only was she indifferent to him personally, but she felt that, given his general silliness, he would make an indifferent husband.}
\entry{indifferent}{ADJ.}{普通的, 无关紧要的}{unmoved or unconcerned by; mediocre.}{Because Ann felt no desire to marry, she was indifferent to Carl's constant proposals. Not only was she indifferent to him personally, but she felt that, given his general silliness, he would make an indifferent husband.}
\entry{indigenous}{ADJ.}{本土的, 土生土长的}{native.}{Cigarettes are made of tobacco, a plant indigenous to the New World.}
\entry{indigent}{ADJ.}{穷困的}{poor; destitute.}{Someone who is truly indigent can't even afford to buy a pack of cigarettes. [Don't mix up indigent and indigenous. See previous sentence.]}
\entry{indignity}{N.}{侮辱}{offensive or insulting treatment.}{Although he seemed to accept cheerfully the indignities heaped upon him, he was inwardly very angry.}
\entry{indiscriminate}{ADJ.}{随意的; 不分青红皂白的}{choosing at random; confused.}{She disapproved of her son's indiscriminate television viewing and decided to restrict him to educational programs.}
\entry{indoctrinate}{V.}{教导; 灌输}{instruct in a doctrine or ideology.}{CubanAmericans resisted sending Elian Gonzalez back to Cuba because he would be indoctrinated there with Communist principles.}
\entry{indolent}{ADJ.}{懒惰}{lazy.}{Couch potatoes lead an indolent life lying back on their Lazyboy recliners watching Tv. indo-lence, N.}
\entry{induce}{V.}{劝诱; 导致, 引起}{persuade; bring about.}{After the quarrel, Tina said nothing could induce her to talk to Tony again. inducement, N.}
\entry{indulgent}{ADJ.}{宽容, 纵容, 溺爱}{humoring; yielding; lenient.}{Jay's mom was excessively indulgent she bought him every Nintendo cartridge and video game on the market. She indulged Jay so much, she spoiled him rotten.}
\entry{industrious}{ADJ.}{勤奋的, 努力的}{diligent; hard-working.}{Look busy when the boss walks by your desk; it never hurts to appear industrious. industry, N.}
\entry{ineffable}{ADJ.}{不可言喻的, 无法用语言表达的; 不能说的, 避讳的}{unutterable; cannot be expressed in speech.}{Such ineffable joy must be experienced; it cannot be described.}
\entry{ineffectual}{ADJ.}{无效的, 弱的}{not effective; weak.}{Because the candidate failed to get across his message to the public, his campaign was ineffectual.}
\entry{inequity}{N.}{不公平}{unfairness.}{In demanding equal pay for equal work, women protest the basic inequity of a system that gives greater financial rewards to men.}
\entry{inert}{ADJ.}{惰性的, 不活跃的}{inactive; lacking power to move.}{"Get up, you lazybones," she cried to her husband, who lay in bed inert. inertia, N.}
\entry{inevitable}{ADJ.}{不可避免地}{unavoidable.}{Though death and taxes are both supposedly inevitable, some people avoid paying taxes for years.}
\entry{inexorable}{ADJ.}{无情的; 残酷的}{relentless; unyielding; implacable.}{After listening to the pleas for clemency, the judge was inexorable and gave the convicted man the maximum punishment allowed by law.}
\entry{infallible}{ADJ.}{一贯正确的}{unerring.}{We must remember that none of us is infallible; we all make mistakes.}
\entry{infer}{V.}{推导, 总结}{deduce; conclude.}{From the students' glazed looks, it was easy for me to infer that they were bored out of their minds. inference, N.}
\entry{infiltrate}{V.}{渗透}{pass into or through; penetrate (an organization) sneakily.}{In order to be able to infiltrate enemy lines at night without being seen, the scouts darkened their faces and wore black coveralls. infiltrator, N.}
\entry{informal}{ADJ.}{非正式的; 不拘礼节的}{absence of ceremony; casual.}{The English teacher preferred informal discussions to prepared lectures.}
\entry{infuriate}{V.}{激怒, 热火}{enrage; anger.}{Her big brother's teasing always infuriated Margaret; no matter how hard she tried to keep her temper, he always got her goat.}
\entry{ingenious}{ADJ.}{聪明的}{clever; resourceful.}{Kit admired the ingenious way that her computer keyboard opened up to reveal the built-in CD-ROM below. ingenuity, N.}
\entry{ingenuous}{ADJ.}{心无城府的; 天真的; 幼稚的; 可信的}{naive and trusting; young; unsophisticated.}{The woodsman had not realized how ingenuous Little Red Riding Hood was until he heard that she had gone off for a walk in the woods with the Big Bad Wolf.}
\entry{inherent}{ADJ.}{固有的, 内在的; 与生俱来的}{firmly established by nature or habit.}{Katya's inherent love of justice caused her to champion anyone she considered treated unfairly by society.}
\entry{inhibit}{V.}{限制, 防止; 阻碍}{restrain; retard or prevent.}{Only two things inhibited him from taking a punch at Mike Tyson: Tyson's left hook, and Tyson's right jab. The protective undercoating on my car inhibits the formation of rust.}
\entry{initiate}{V.}{开始, 发源}{begin; originate; receive into a group.}{The college is about to initiate a program in reducing math anxiety among students.}
\entry{injurious}{ADJ.}{有害的}{ harmful.}{Smoking cigarettes can be injurious to your health.}
\entry{innate}{ADJ.}{先天的, 天生的}{inborn.}{Mozart's parents soon recognized young Wolfgang's innate talent for music.}
\entry{innovation}{N.}{发明; 变革}{change; introduction of something new.}{Although Richard liked to keep up with all the latest technological innovations, he didn't always abandon tried and true techniques in favor of something new. innovate,V.}
\entry{inopportune}{ADJ.}{不合时宜的}{untimely; poorly chosen.}{A rock concert is an inopportune setting for a quiet conversation.}
\entry{inordinate}{ADJ.}{紊乱的; 不受限制的}{unrestrained; excessive.}{She had an inordinate fondness for candy, eating two or three boxes in a single day.}
\entry{insatiable}{ADJ.}{不容易伺候的; 贪婪的}{not easily satisfied; unquenchable; greedy.}{David's appetite for oysters was insatiable: he could easily eat four dozen at a single sitting.}
\entry{insensible}{ADJ.}{迟钝的; 硬心肠的}{unconscious; unresponsive.}{Sherry and I are very different; at times when I would be covered with embarrassment, she seems insensible to shame.}
\entry{insightful}{ADJ.}{有洞察力的}{discerning; perceptive.}{Sol thought he was very insightful about human behavior, but he was actually clueless as to why people acted the way they did.}
\entry{instigate}{V.}{驱使; 激励, 鼓动}{urge; start; provoke.}{Rumors of police corruption led the mayor to instigate an investigation into the department's activities.}
\entry{insulated}{ADJ.}{分离; 隔离}{set apart; isolated.}{A well-to-do bachelor, James spent his money freely, insulated from the cares of his friends, who had families to support.}
\entry{insuperable}{ADJ.}{不可战胜的, 不能克服的}{insurmountable; unbeatable.}{Though the odds against their survival seemed insuperable, the Apollo 13 astronauts reached earth safely.}
\entry{intangible}{ADJ.}{难以明了的, 无形的; 暧昧的, 模糊的}{not able to be perceived by touch; vague.}{Though the financial benefits of his Oxford post were meager, Lewis was drawn to it by its intangible rewards: prestige, intellectual freedom, the fellowship of his peers.}
\entry{integrate}{V.}{整合, 合并}{make whole; combine; make into one unit.}{She tried to integrate all their activities into one program.}
\entry{interminable}{ADJ.}{无尽的}{endless.}{Although his speech lasted for only twenty minutes, it seemed interminable to his bored audience.}
\entry{intervene}{V.}{干预; 干涉}{come between.}{When two close friends get into a fight, be careful if you try to intervene; they may join forces to gang up on you.}
\entry{intimacy}{N.}{亲密; 隐私}{closeness, often affectionate; privacy; familiarity.}{In a moment of rare intimacy, the mayor allowed the reporters a glimpse of his personal feelings about his family. intimate,ADJ.}
\entry{intimate}{V.}{私下的, 秘密的, 亲密的; 宣告}{hint; suggest.}{Was Dick intimating that Jane had bad breath when he asked if she'd like a breath mint?}
\entry{intimidate}{V.}{使害怕}{frighten.}{I'll learn karate and then those big bullies won't be able to intimidate me any more.}
\entry{intricate}{ADJ.}{复杂的; 错综的}{complex; knotty; tangled.}{Philip spent many hours designing mazes so intricate that none of his classmates could solve them. intricacy, N.}
\entry{introspective}{ADJ.}{内省的; 反省的}{looking within oneself.}{Though young Francis of Assisi led a wild and worldly life, even then he had introspective moments during which he examined his soul. introvert N. one who is introspective; inclined to think more about oneself. In his poetry, he reveals that he is an introvert by his intense interest in his own problems. alsoV.}
\entry{introvert}{N.}{性格内向的人}{}{}
\entry{intrude}{V.}{强挤入, 侵入; 强加于人}{trespass; enter as an uninvited person.}{She hesitated to intrude on their conversation.}
\entry{intuition}{N.}{直觉}{immediate insight; power of knowing without reasoning.}{Even though Tony denied that anything was wrong, Tina trusted her intuition that something was bothering him. intuitive,ADJ.}
\entry{invalidate}{V.}{摧毁; 使无效; 弱化}{weaken; destroy.}{The relatives who received little or nothing sought to invalidate the will by claiming that the deceased had not been in his right mind when he had signed the document.}
\entry{invasive}{ADJ.}{入侵的}{tending to spread aggressively; intrusive.}{Giving up our war with the invasive blackberry vines that had taken over the back yard, we covered the lawn with concrete. invade,V.}
\entry{invert}{V.}{倒转, 翻转}{turn upside down or inside out.}{When he inverted his body in a handstand, he felt the blood rush to his head. inveterate ADJ. deep-rooted; habitual. An inveterate smoker, Bob cannot seem to break the habit, no matter how hard he tries.}
\entry{invigorate}{V.}{激发; 鼓舞}{energize; stimulate.}{A quick dip in the pool invigorated Meg, and with renewed energy she got back to work.}
\entry{invulnerable}{ADJ.}{无懈可击的}{incapable of injury.}{Achilles was invulnerable except in his heel.}
\entry{irate}{ADJ.}{愤怒的; 生气的}{angry.}{When John's mother found out he had overdrawn his checking account for the third month in a row, she was so irate she could scarcely speak to him.}
\entry{irksome}{ADJ.}{令人厌恶的; 冗长乏味的}{annoying; tedious.}{He found working on the assembly line irksome because of the monotony of the operation he had to perform. irk,V.}
\entry{ironic}{ADJ.}{讽刺性的}{resulting in an unexpected and contrary outcome.}{It is ironic that his success came when he least wanted it.}
\entry{irrational}{ADJ.}{无理的, 缺乏逻辑的; 不理智的}{illogical; lacking reason; insane.}{Many people have such an irrational fear of snakes that they panic at the sight of a harmless garter snake.}
\entry{irreconcilable}{ADJ.}{不相容的; 矛盾的}{incompatible; not able to be resolved.}{Because the separated couple were irreconcilable, the marriage counselor recommended a divorce.}
\entry{irrelevant}{ADJ.}{不相关的, 不照号的}{not applicable; unrelated.}{No matter how irrelevant the patient's mumblings may seem, they give us some indications of what he has on his mind.}
\entry{irrepressible}{ADJ.}{压不住的, 抑制不住的}{unable to be restrained or held back.}{My friend Kitty's curiosity was irrepressible: she poked her nose into everybody's business and just laughed when I warned her that curiosity killed the cat.}
\entry{irresolute}{ADJ.}{犹豫不决的}{uncertain how to act; weak.}{Once you have made your decision, don't waver; a leader should never appear irresolute.}
\entry{irrevocable}{ADJ.}{不能取消的; 不能变更的}{unalterable; irreversible.}{As Sue dropped the "Dear John" letter into the mailbox, she suddenly had second thoughts and wanted to take it back, but she could not: her action was irrevocable.}
\entry{judicious}{ADJ.}{公平的}{sound in judgment; wise.}{At a key moment in his life, he made a judicious investment that was the foundation of his later wealth.}
\entry{kindle}{V.}{点燃, 照亮, 激起}{start a fire; inspire.}{One of the first things Ben learned in the Boy Scouts was how to kindle a fire by rubbing two dry sticks together. Her teacher's praise for her poetry kindled a spark of hope inside Maya.}
\entry{laborious}{ADJ.}{艰苦的, 勤劳的}{demanding much work or care; tedious.}{In putting together his dictionary of the English language, Doctor Johnson undertook a laborious task.}
\entry{laconic}{ADJ.}{简洁的}{brief and to the point.}{Many of the characters portrayed by Clint Eastwood are laconic types: strong men of few words.}
\entry{lament}{V.}{悲伤, 恸哭}{grieve; express sorrow.}{Even advocates of the war lamented the loss of so many lives in combat. lamentation, N.}
\entry{lassitude}{N.}{疲乏}{languor; weariness.}{After a massage and a long soak in the hot tub, I gave in to my growing lassitude and lay down for a nap.}
\entry{latent}{ADJ.}{潜在的}{potential but undeveloped; dormant; hidden.}{Polaroid pictures are popular at parties, because you can see the latent photographic image gradually appear before your eyes.}
\entry{latitude}{N.}{范围}{freedom from narrow limitations.}{I think you have permitted your son too much latitude in this matter.}
\entry{lavish}{ADJ.}{浪费的, 大方的}{liberal; wasteful.}{The actor's lavish gifts pleased her. alsoV.}
\entry{legacy}{N.}{遗赠}{a gift made by a will.}{Part of my legacy from my parents is an album of family photographs.}
\entry{lethal}{ADJ.}{致命的}{deadly.}{It is unwise to leave lethal weapons where children may find them.}
\entry{levitate}{V.}{升空漂浮（魔法）}{float in the air (especially by magical means).}{As the magician passed his hands over the recumbent body of his assistant, she appeared to rise and levitate about three feet above the table.}
\entry{liability}{N.}{责任; 缺点; 债}{drawback; debts.}{Her lack of an extensive vocabulary was a liability that she was eventually able to overcome.}
\entry{limber}{ADJ.}{柔韧的; 可塑的}{flexible.}{Hours of ballet classes kept him limber.}
\entry{linger}{V.}{逗留; 闲逛; 流连}{loiter or dawdle; continue or persist.}{Hoping to see Juliet pass by, Romeo lingered outside the Capulet house for hours. Though Mother made stuffed cabbage on Monday, the smell lingered around the house for days.}
\entry{linguistic}{ADJ.}{语言的}{pertaining to language.}{The modern tourist will encounter very little linguistic difficulty as English has become an almost universal language.}
\entry{listless}{ADJ.}{倦怠的, 冷漠的}{lacking in spirit or energy.}{We had expected him to be full of enthusiasm and were surprised by his listless attitude.}
\entry{loath}{ADJ.}{不情愿的; 勉强}{reluctant; disinclined.}{Romeo and Juliet were both loath for him to go.}
\entry{lofty}{ADJ.}{高高在上的}{very high.}{Though Barbara Jordan's fellow students used to tease her about her lofty ambitions, she rose to hold one of the highest positions in the land.}
\entry{longevity}{N.}{长命不老}{long life.}{When he reached ninety, the old man was proud of his longevity.}
\entry{luminous}{ADJ.}{发光的, 闪耀的}{shining; issuing light.}{The sun is a luminous body.}
\entry{lunar}{ADJ.}{月亮的}{pertaining to the moon.}{Lunar craters can plainly seen with the aid of a small telescope.}
\entry{lunge}{V.}{突进, 刺, 冲}{quick forward dive or reach; thrust.}{The wide receiver lunged forward to grab the football. With his sword, Dartagnan lunged at his adversary.}
\entry{lurid}{ADJ.}{耸人听闻的; 可怕的; 惨白的; 血红的}{wild; sensational; graphic; gruesome.}{Do the lurid cover stories in the Enquirer actually attract people to buy that trashy tabloid?}
\entry{luxuriant}{ADJ.}{丰富的, 富足的; 丰富多彩; 肥沃的}{abundant; rich and splendid; fertile.}{Lady Godiva was completely covered by her luxuriant hair.}
\entry{machinations}{N.}{阴谋, 诡计}{evil schemes or plots.}{Fortunately, Batman saw through the wily machinations of the Riddler and saved Gotham City from destruction by the forces of evil.}
\entry{magnanimous}{ADJ.}{宽宏大量的}{generous; great-hearted.}{Philanthropists by definition are magnanimous; misers, by definition, are not. Cordelia was too magnanimous to resent her father's unkindness to her; instead, she generously forgave him. magnanimity, N.}
\entry{magnate}{N.}{富豪, 要人; 突出的人物, XX大王}{person of prominence or influence.}{Growing up in Pittsburgh, Annie Dillard was surrounded by the mansions of the great steel and coal magnates who set their mark on that city.}
\entry{malevolent}{ADJ.}{坏心肠的}{wishing evil.}{lago is a malevolent villain who takes pleasure in ruining Othello.}
\entry{malicious}{ADJ.}{恶毒的}{hateful; spiteful.}{Jealous of Cinderella's beauty, her malicious stepsisters expressed their spite by forcing her to do menial tasks. malice, N.}
\entry{malleable}{ADJ.}{有延展性的; 可锻的}{capable of being shaped by pounding; impressionable.}{Gold is a malleable metal, easily shaped into bracelets and rings. Fagin hoped Oliver was a malleable lad, easily shaped into a thief.}
\end{multicols}
\clearpage
\setList{22-24}

\begin{multicols}{2}
\entry{mammal}{N.}{哺乳动物}{a vertebrate animal whose female suckles its young.}{Many people regard the whale as a fish and do not realize that it is a mammal.}
\entry{manifest}{ADJ.}{明白的, 显然的; 证明, 表现}{evident; visible; obvious.}{Digby's embarrassment when he met Madonna was manifest: his ears turned bright pink, he kept scuffing one shoe in the dirt, and he couldn't look her in the eye.}
\entry{manipulate}{V.}{操作}{operate with one's hands; control or play upon (people, forces, etc.}{ artfully. Jim Henson understood how to manipulate the Muppets. Madonna understands how to manipulate men (and publicity).}
\entry{mannered}{ADJ.}{做作的, 矫饰的}{affected; not natural.}{Attempting to copy the style of his wealthy neighbors, Gatsby adopted a mannered, artificial way of speech.}
\entry{maritime}{ADJ.}{海事的, 海运的, 海上的}{bordering on the sea; nautical.}{The Maritime Provinces depend on the sea for their wealth.}
\entry{marked}{ADJ.}{值得注意的; 报仇的目标}{noticeable or pronounced; targeted for vengeance.}{He walked with a marked limp, a souvenir of an old I.R.A. attack. As British ambassador, he knew he was a marked man, for he knew the Irish Republican Army wanted him dead.}
\entry{marshal}{V.}{排序; 整理}{put in order.}{At a debate tournament, extemporaneous speakers have only a minute or two to marshal their thoughts before they address their audience.}
\entry{martial}{ADJ.}{好战的; 尚武的}{warlike.}{The sound of martial music inspired the young cadet with dreams of military glory.}
\entry{material}{ADJ.}{物质的; 重要的}{made of physical matter; unspiritual; important.}{Probing the mysteries of this material world has always fascinated physicist George Whitesides. Reporters nicknamed Madonna the Material Girl because, despite her name, she seemed wholly uninterested in spiritual values. Lexy's active participation made a material difference to the success of the fund-raiser.}
\entry{meager}{ADJ.}{瘦的; 贫乏的, 不足的}{scanty; inadequate.}{Still hungry after his meager serving of porridge, Oliver Twist asked for a second helping.}
\entry{meander}{V.}{弯曲; 蜿蜒}{wind or turn in its course.}{Needing to stay close to a source of water, he followed every twist and turn of the stream as it meandered through the countryside.}
\entry{meddlesome}{ADJ.}{爱管闲事的; 好事的; 好插手的}{interfering.}{He felt his marriage was suffering because of his meddlesome mother-in-law.}
\entry{mediate}{V.}{调解; 仲裁}{settle a dispute through the services of an outsider.}{King Solomon was asked to mediate a dispute between two women, each of whom claimed to be the mother of the same child.}
\entry{meditation}{N.}{沉思冥想}{reflection; thought.}{She reached her decision only after much meditation.}
\entry{mentor}{N.}{门特; 顾问; 导师}{teacher.}{During this very trying period, she could not have had a better mentor, for the teacher was sympathetic and understanding.}
\entry{mercenary}{ADJ.}{唯利是图}{interested in money or gain.}{Andy's every act was prompted by mercenary motives: his first question was always "What's in it for me?"}
\entry{mercurial}{ADJ.}{善变的; 无常的}{capricious; changing; fickle.}{Quick as quicksilver to change, he was mercurial in nature and therefore unreliable.}
\entry{merger}{N.}{合并; 吞并}{combination (of two business corporations).}{When the firm's president married the director of financial planning, the office joke was that it wasn't a marriage, it was a merger.}
\entry{metaphor}{N.}{隐喻}{implied comparison.}{"He soared like an eagle" is an example of a simile; "He is an eagle in flight," a metaphor.}
\entry{methodical}{ADJ.}{方法论的; 系统化的}{systematic.}{An accountant must be methodical and maintain order among his financial records.}
\entry{meticulous}{ADJ.}{小心翼翼的}{excessively careful; painstaking; scrupulous.}{Martha Stewart was a meticulous housekeeper, fussing about each and every detail that went into making up her perfect home.}
\entry{metropolis}{N.}{大都会}{large city.}{Every evening the terminal is filled with thousands of commuters going from this metropolis to their homes in the suburbs.}
\entry{migrant}{ADJ.}{移居的; 候鸟的}{changing its habitat; wandering.}{These migrant birds return every spring. also N.}
\entry{militant}{ADJ.}{好战的}{combative; bellicose.}{Although at this time he was advocating a policy of neutrality, one could usually find him adopting a more militant attitude. also N.}
\entry{minuscule}{ADJ.}{极小的}{extremely small.}{Why should I involve myself with a project with so minuscule a chance for success?}
\entry{minute}{ADJ.}{极小的}{extremely small.}{The twins resembled one another closely; only minute differences set them apart.}
\entry{mirth}{N.}{欢笑}{merriment; laughter.}{Sober Malvolio found Sir Toby's mirth improper.}
\entry{misanthrope}{N.}{厌恶人类的人; 憎人者}{one who hates mankind.}{In Gulliver's Travels, Swift portrays an image of humanity as vile, degraded beasts; for this reason, various critics consider him a misanthrope.}
\entry{misapprehension}{N.}{错误; 误解}{error; misunderstanding.}{To avoid misapprehension, I am going to ask all of you to repeat the instructions I have given.}
\entry{misconception}{N.}{误解}{mistaken idea.}{"Sir, you are suffering from a misconception. I do not wish to marry you in the least!"}
\entry{misconstrue}{V.}{曲解}{interpret incorrectly; misjudge.}{She took the passage seriously rather than humorously because she misconstrued the author's ironic tone.}
\entry{miserly}{ADJ.}{吝啬的; 贪婪的; 坏的}{stingy; mean.}{Transformed by his vision on Christmas Eve, mean old Scrooge ceased being miserly and became a generous, kind old man.}
\entry{mishap}{N.}{意外, 灾难}{accident.}{With a little care you could have avoided this mishap.}
\entry{misnomer}{N.}{错误的名字; 写错名字; 用词不当}{wrong name; incorrect designation.}{His tyrannical conduct proved to all that his nickname, King Eric the Just, was a misnomer.}
\entry{misrepresent}{V.}{误传; 有意制造误解}{give a false or incorrect impression, often deliberately; serve unsatisfactorily as a representative.}{In his job application, Milton misrepresented his academic background; he was fired when his employers discovered the truth. The reformers accused Senator Gunbucks of mis-representing his constituents and claimed he took bribes from the NRA.}
\entry{mitigate}{V.}{减轻; 减缓; 中和}{appease; moderate.}{Nothing Jason did could mitigate Medea's anger; she refused to forgive him for betraying her.}
\entry{mobile}{ADJ.}{移动的}{movable; not fixed.}{The mobile blood bank operated by the Red Cross visited our neighborhood today. mobility, N.}
\entry{mock}{V.}{嘲弄, 嘲笑}{ridicule; imitate, often in derision.}{It is unkind to mock anyone; it is stupid to mock anyone significantly bigger than you. mockery, N.}
\entry{mode}{N.}{时尚; 方式; 模式}{prevailing style; manner; way of doing something.}{The rock star had to have her hair done in the latest mode: frizzed, with occasional moussed spikes for variety. Henry plans to adopt a simpler mode of life: he is going to become a mushroom hunter and live off the land.}
\entry{modulate}{V.}{控制; 调制到标准; 调制（信号）}{tone down in intensity; regulate; change from one key to another.}{Always singing at the top of her lungs, the budding Brunhilde never learned to modulate her voice.}
\entry{molecule}{N.}{分子}{the smallest particle (one or more atoms) of a substance, having all the properties of that substance.}{In chemistry, we study how atoms and molecules react to form new substances.}
\entry{mollify}{V.}{平息; 安抚}{soothe.}{The airline customer service representative tried to mollify the angry passenger by offering her a seat in first class.}
\entry{molten}{ADJ.}{融化了的}{melted.}{The city of Pompeii was destroyed by volcanic ash rather than by molten lava flowing from Mount Vesuvius.}
\entry{momentous}{ADJ.}{非常重要的}{very important.}{When Marie and Pierre Curie discovered radium, they had no idea of the momentous impact their discovery would have upon society.}
\entry{monetary}{ADJ.}{金融的}{pertaining to money.}{Jane held the family purse strings: she made all monetary decisions affecting the household.}
\entry{monolithic}{ADJ.}{单片的, 单块的; 一体不动摇的}{solidly uniform; unyielding.}{Knowing the importance of appearing resolute, the patriots sought to present a monolithic front.}
\entry{monumental}{ADJ.}{雄伟的; 厚重的; 结实的; 纪念的}{massive.}{Writing a dictionary is a monumental task.}
\entry{morose}{ADJ.}{郁闷的; 乖僻的}{ill-humored; sullen; melancholy.}{Forced to take early retirement, Bill acted morose for months; then, all of a sudden, he shook off his sullen mood and was his usual cheerful self.}
\entry{mosaic}{N.}{马赛克}{picture made of colorful small inlaid tiles.}{The mayor compared the city to a beautiful mosaic made up of people of every race and religion on earth.}
\entry{motif}{N.}{主旨, 本意; 动机}{theme.}{This simple motif runs throughout the entire score.}
\entry{multifaceted}{ADJ.}{多面的}{having many aspects.}{A multifaceted composer, Roger Davidson has recorded original pieces that range from ragtime tangos to choral masses.}
\entry{multiplicity}{N.}{多样性}{state of being numerous.}{He was appalled by the multiplicity of details he had to complete before setting out on his mission.}
\entry{mundane}{ADJ.}{世俗的; 日常的}{worldly as opposed to spiritual; everyday.}{Uninterested in philosophical or spiritual discussions, Tom talked only of mundane matters such as the daily weather forecast or the latest basketball results.}
\entry{munificent}{ADJ.}{宽宏大量的; 慷慨大方的}{very generous.}{Shamelessly fawning over a particularly generous donor, the dean kept on referring to her as "our munificent benefactor." munificence, N.}
\entry{mutability}{N.}{变化能力}{ability to change in form; fickleness.}{Going from rags to riches, and then back to rags again, the bankrupt financier was a victim of the mutability of fortune.}
\entry{muted}{ADJ.}{静默的; 静音的}{silent; muffled; toned down.}{Thanks to the thick, sound-absorbing walls of the cathedral, only muted traffic noise reached the worshippers within.}
\entry{myriad}{N.}{无数, 非常多}{very large number.}{Myriads of mosquitoes from the swamps invaded our village every twilight. alsoADJ.}
\entry{naiveté}{N.}{天真烂漫的, 简单的}{quality of being unsophisticated; simplicity; artlessness; gullibility.}{Touched by the naivetd of sweet, convent-trained Cosette, Marius pledges himself to protect her innocence. naive,ADJ.}
\entry{narrative}{ADJ.}{解说的}{related to telling a story.}{A born teller of tales, Tillie Olsen used her impressive narrative skills to advantage in her story "I Stand Here Ironing." narrate,V.}
\entry{nascent}{ADJ.}{初生的}{incipient; coming into being.}{If we could identify these revolutionary movements in their nascent state, we would be able to eliminate serious trouble in later years.}
\entry{navigable}{ADJ.}{可以通航的}{wide and deep enough to allow ships to pass through; able to be steered.}{So much sand had built up at the bottom of the canal that the waterway was barely navigable.}
\entry{negate}{V.}{拒绝, 否定, 取消}{cancel out; nullify; deny.}{A sudden surge of adrenalin can negate the effects of fatigue: there's nothing like a good shock to wake you up.}
\entry{negligible}{ADJ.}{可忽略不计的}{so small, trifling, or unimportant that it may be easily disregarded.}{Because the damage to his car had been negligible, Michael decided he wouldn't bother to report the matter to his insurance company.}
\entry{neutral}{ADJ.}{中型的; 自然的; 中庸的, 公允的}{impartial; not supporting one side over another.}{Reluctant to get mixed up in someone else's quarrel, Bobby tried to remain neutral, but eventually he had to take sides.}
\entry{nicety}{N.}{准确, 精密}{precision; minute distinction.}{I cannot distinguish between such niceties of reasoning.}
\entry{nomadic}{ADJ.}{游牧的}{wandering.}{Several nomadic tribes of Indians would hunt in this area each year.}
\entry{nonchalance}{N.}{冷淡}{indifference; lack of concern; composure.}{Cool, calm, and collected under fire, James Bond shows remarkable nonchalance in the face of danger.}
\entry{noncommittal}{ADJ.}{不明朗的, 不表态的; 中庸的, 未决的}{neutral; unpledged; undecided.}{We were annoyed by his noncommittal reply for we had been led to expect definite assurances of his approval.}
\entry{notoriety}{N.}{臭名昭著的}{disrepute; ill fame.}{To the starlet, any publicity was good publicity: if she couldn't have a good reputation, she'd settle for notoriety. notorious,ADJ.}
\entry{novelty}{N.}{新奇}{something new; newness.}{The computer is no longer a novelty at work; every desk in our office has one. novel,ADJ.}
\entry{noxious}{ADJ.}{有害的}{harmful.}{We must trace the source of these noxious gases before they asphyxiate us.}
\entry{nullify}{V.}{使无效}{to make invalid.}{Once the contract was nullified, it no longer had any legal force.}
\entry{nurture}{V.}{养育; 教育}{nourish; educate; foster.}{The Head Start program attempts to nurture pre-kindergarten children so that they will do well when they enter public school. also N.}
\entry{nutrient}{N.}{营养品}{nourishing substance.}{As a budding nutritionist, Kim has learned to design diets that contain foods rich in important basic nutrients.}
\entry{objective}{ADJ.}{不为情所动的; 公平的}{not influenced by emotions; fair.}{Even though he was her son, she tried to be objective about his behavior.}
\entry{obligatory}{ADJ.}{必须的}{binding; required.}{It is obligatory that books borrowed from the library be returned within two weeks.}
\entry{oblivious}{ADJ.}{遗忘的; 出神的}{inattentive or unmindful; wholly absorbed.}{Deep in her book, Nancy was oblivious to the noisy squabbles of her brother and his friends.}
\entry{obscure}{ADJ.}{模糊的, 不明了的, 暗淡的}{dark; vague; unclear.}{Even after I read the poem a fourth time, its meaning was still obscure. obscurity, N.}
\entry{obsessive}{ADJ.}{强迫性的, 入迷的; 出神的}{related to thinking about something constantly; preoccupying.}{Ballet, which had been a hobby, began to dominate his life: his love of dancing became obsessive. obsession, N.}
\entry{obstinate}{ADJ.}{坚定的, 倔强的}{stubborn; hard to control or treat.}{We tried to persuade him to give up smoking, but he was obstinate and refused to change. Blackberry stickers are the most obstinate weeds I know: once established in a yard, they're extremely hard to root out. obstinacy, N.}
\entry{obtrude}{V.}{插手, 强入, 冲出}{push (oneself or one's ideas) forward or intrude; butt in; stick out or extrude.}{Because Fanny was reluctant to obtrude her opinions about child-raising upon her daughter-in-law, she kept a close watch on her tongue. obtrusive,ADJ.}
\entry{obviate}{V.}{消除; 排除; 避免}{make unnecessary; get rid of.}{I hope this contribution will obviate any need for further collections of funds.}
\entry{odious}{ADJ.}{可恨的; 可耻的}{hateful; vile.}{Cinderella's ugly stepsisters had the odious habit of popping their zits in public.}
\entry{offensive}{ADJ.}{攻击的; 冒犯的}{attacking; insulting; distasteful.}{Getting into street brawls is no minor matter for professional boxers, who are required by law to restrict their offensive impulses to the ring.}
\entry{ominous}{ADJ.}{有威胁的; 恶兆的}{threatening.}{Those clouds are ominous; they suggest a severe storm is on the way.}
\entry{omniscient}{ADJ.}{无所不知的}{all-knowing.}{I do not pretend to be omniscient, but I am positive about this fact.}
\entry{onset}{N.}{开始, 发作, 肇端; 攻击}{beginning; attack.}{Caught unprepared by the sudden onset of the storm, we rushed around the house closing windows and bringing the garden furniture into shelter. Caught unprepared by the enemy onset, the troops scrambled to take shelter.}
\entry{opportune}{ADJ.}{世纪恰巧的; 刚好的}{timely; well-chosen.}{Sally. looked at her father struggling to balance his checkbook; clearly this would not be an opportune moment to ask him for a raise in her allowance.}
\entry{optimist}{N.}{乐观者}{person who looks on the good side.}{The pessimist says the glass is half-empty; the optimist says it is half-full.}
\entry{optimum}{ADJ.}{最优的}{most favorable.}{If you wait for the optimum moment to act, you may never begin your project. also N.}
\entry{optional}{ADJ.}{可选的}{not obligatory; left to one's choice.}{Most colleges require applicants to submit SAT I scores; at some colleges, however, submitting SAT I scores is optional.}
\entry{opulence}{N.}{奢华; 巨富; 富裕, 富足}{extreme wealth; luxuriousness; abundance.}{The glitter and opulence of the ballroom took Cinderella's breath away. opulent,ADJ.}
\entry{orient}{V.}{确定方向; 校准}{get one's bearings; adjust.}{Philip spent his first day in Denver orienting himself to the city.}
\entry{orthodox}{ADJ.}{传统的; 保守的}{traditional; conservative in belief.}{Faced with a problem, he preferred to take an orthodox approach rather than shock anyone. orthodoxy, N.}
\entry{outspoken}{ADJ.}{坦率直言的}{candid; blunt.}{The candidate was too outspoken to be a successful politician; he had not yet learned to weigh his words carefully.}
\entry{outstrip}{V.}{超过}{surpass; outdo.}{Jesse Owens easily outstripped his white competitors to win the gold medal at the Olympic Games.}
\entry{overbearing}{ADJ.}{傲慢专横的}{bossy and arrogant; decisively important.}{Certain of her own importance, and of the unimportance of everyone else, Lady Bracknell was intolerably overbearing in her manner. "In choosing a husband," she said, "good birth is of overbearing importance; compared to that, neither wealth nor talent signifies."}
\entry{overwrought}{ADJ.}{歇斯底里的}{extremely agitated; hysterical.}{When Kate heard the news of the sudden tragedy, she became too overwrought to work and had to leave the office early.}
\entry{pacify}{V.}{安抚; 平静}{soothe; make calm or quiet; subdue.}{Dentists criticize the practice of giving fussy children sweets to pacify them.}
\entry{pandemic}{ADJ.}{广泛传播的, 流行的}{widespread; affecting the majority of people.}{They feared the AIDS epidemic would soon reach pandemic proportions.}
\end{multicols}
\clearpage
\setList{25-27}

\begin{multicols}{2}
\entry{paradigm}{N.}{典范; 模式}{model; example; pattern.}{Pavlov's experiment in which he trains a dog to salivate on hearing a bell is a paradigm of the conditioned-response experiment in behavioral psychology. Barron's How to Prepare for College Entrance Examinations was a paradigm for all the SAT-prep books that followed.}
\entry{paradox}{N.}{悖论; 佯谬}{something apparently contradictory in nature; statement that looks false but is actually correct.}{Richard presents a bit of a paradox, for he is a card-carrying member of both the National Rifle Association and the relatively pacifist American Civil Liberties Union.}
\entry{parallelism}{N.}{平行状态; 相似的}{state of being parallel; similarity.}{Although the twins were separated at birth and grew up in different adoptive families, a striking parallelism exists between their lives.}
\entry{paramount}{ADJ.}{极其重要的}{foremost in importance; supreme.}{Proper nutrition and hygiene are of paramount importance in adolescent development and growth.}
\entry{paraphrase}{V.}{解释; 批注; 注释}{restate a passage in one's own words while retaining thought of author.}{In 25 wordsaor less, paraphrase this article. also N.}
\entry{parity}{N.}{相等; 势均力敌; 奇偶}{equality in status or amount; close resemblance.}{Unfortunately, some doubt exists whether women's salaries will ever achieve paritywith men's.}
\entry{parody}{N.}{拙劣的模仿}{humorous imitation; spoof; takeoff; travesty.}{The show Forbidden Broadway presents parodies spoofing the year's new productions playing on Broadway.}
\entry{parsimony}{N.}{过度俭省; 吝啬}{stinginess; excessive frugality.}{Furious because her father wouldn't let her buy out the clothing store, Annie accused him of parsimony.}
\entry{partial}{ADJ.}{不完善的; 偏爱的}{incomplete; having a liking for something.}{In this issue we have published only a partial list of contributors because we lack space to acknowledge everyone. I am extremely partial to chocolate eclairs.}
\entry{partisan}{ADJ.}{一边倒的}{one-sided; prejudiced; committed to a party.}{On certain issues of principle, she refused to take a partisan stand, but let her conscience be her guide. Rather than joining forces to solve our nation's problems, the Democrats and Republicans spend their time on partisan struggles. also N.}
\entry{passive}{ADJ.}{被动的}{not active; acted upon.}{Mahatma Gandhi urged his followers to pursue a program of passive resistance as he felt that it was more effective than violence and acts of terrorism.}
\entry{patent}{ADJ.}{显而易见的; 公开查阅的}{open for the public to read; obvious.}{It was patent to everyone that the witness spoke the truth. also N.}
\entry{paucity}{N.}{少量; 缺乏}{scarcity.}{They closed the restaurant because the paucity of customers made it uneconomical to operate.}
\entry{pedantic}{ADJ.}{书生气的}{showing off learning; bookish.}{Leavening his decisions with humorous, down-to-earth anecdotes, Judge Walker was not at all the pedantic legal scholar. pedant, pedantry, N.}
\entry{pedestrian}{ADJ.}{没有想象力的, 普通的}{ordinary; unimaginative.}{Unintentionally boring, he wrote page after page of pedestrian prose.}
\entry{peerless}{ADJ.}{不可比较的, 不相衡的, 无可匹敌的}{having no equal; incomparable.}{The reigning operatic tenor of his generation, to his admirers Luciano Pavarotti was peerless: no one could compare with him.}
\entry{pensive}{ADJ.}{沉思默想的; 忧心忡忡的}{dreamily thoughtful; thoughtful with a hint of sadness; contemplative.}{The pensive lover gazed at the portrait of his beloved and deeply sighed.}
\entry{penury}{N.}{一贫如洗; 穷困潦倒}{severe poverty; stinginess.}{When his pension fund failed, George feared he would end his days in penury. He became such a penny pincher that he turned into a closefisted, penurious miser.}
\entry{perceptive}{ADJ.}{有洞察力的, 警觉的; 智慧的}{insightful; aware; wise.}{Although Maud was a generally perceptive critic, she had her blind spots: she could never see flaws in the work of her friends.}
\entry{perforate}{V.}{打孔}{pierce; put a hole through.}{Before you can open the aspirin bottle, you must first perforate the plastic safety seal that covers the cap.}
\entry{perfunctory}{ADJ.}{肤浅的, 不投入的; 漠不关心的}{superficial; not thorough; lacking interest, care, or enthusiasm.}{The auditor's perfunctory inspection of the books overlooked many errors. Giving the tabletop only a perfunctory swipe with her dust cloth, Betty promised herself she'd clean it more thoroughly tomorrow.}
\entry{peripheral}{ADJ.}{外围的}{marginal; outer.}{We lived, not in central London, but in one of those peripheral suburbs that spring up on the outskirts of a great city.}
\entry{permeate}{V.}{传播; 流传}{pass through; spread.}{The odor of frying onions permeated the air.}
\entry{pernicious}{ADJ.}{及具毁灭性的}{very destructive.}{Crack cocaine has had a pernicious effect on urban society: it has destroyed families, turned children into drug dealers, and increased the spread of violent crimes.}
\entry{perpetual}{ADJ.}{永久的}{everlasting.}{Ponce de Leon hoped to find the legendary fountain of perpetual youth.}
\entry{perpetuate}{V.}{保护免于灭绝}{make something last; preserve from extinction.}{Some critics attack The Adventures of Huckleberry Finn because they believe Twain's book perpetuates a false image of Blacks in this country.}
\entry{persevere}{V.}{坚持; 不屈不挠; 固执己见（在辩论中}{}{}
\entry{personable}{ADJ.}{有吸引力的}{attractive.}{The man I am seeking to fill this position must be personable since he will be representing us before the public.}
\entry{perspicacious}{ADJ.}{洞察一切的, 渗透的; 机敏的}{having insight; penetrating; astute.}{The brilliant lawyer was known for his perspicacious deductions. perspicacity, N.}
\entry{pertinacious}{ADJ.}{拒不屈服; 反抗}{stubborn; persistent.}{He is bound to succeed because his pertinacious nature will not permit him to quit.}
\entry{pertinent}{ADJ.}{说到点子上的; 中肯的; 有关的}{To the point; relevant.}{Virginia Woolf's words on women's rights are as pertinent today as they were when she wrote them nearly a century ago.}
\entry{pervasive}{ADJ.}{深入人心的; 普遍的}{pervading; spread throughout every part.}{Despite airing them for several hours, Martha could not rid her clothes of the pervasive odor of mothballs that clung to them. pervade,V.}
\entry{phenomena}{N.}{现象}{observable facts; subjects of scientific investigation.}{We kept careful records of the phenomena we noted in the course of these experiments.}
\entry{phoenix}{N.}{凤凰（象征不死和重生、涅磐）}{symbol of immortality or rebirth.}{Like the legendary phoenix rising from its ashes, the city of San Francisco rose again after its destruction during the 196 earthquake.}
\entry{piety}{N.}{虔诚; 孝行}{religious devotion; godliness.}{The nuns in the convent were noted for their piety; they spent their days in worship and prayer. Pious,ADJ.}
\entry{pitfall}{N.}{缺陷}{hidden danger; concealed trap.}{Her parents warned young Sophie against the many pitfalls that lay in wait for her in the dangerous big city.}
\entry{pithy}{ADJ.}{精炼的; 抓住灵魂的}{concise; meaningful; substantial; meaty.}{While other girls might have gone on and on about how uncool Elton was, Liz summed it up in one pithy remark: "He's bogus!"}
\entry{pivotal}{ADJ.}{关键的}{crucial; key; vital.}{The new "smart weapons" technology played a pivotal role in the quick resolution of the war with Iraq.}
\entry{placate}{V.}{安抚}{pacify; conciliate.}{The store manager tried to placate the angry customer, offering to replace the damaged merchandise or to give back her money right away.}
\entry{placid}{ADJ.}{平静的}{peaceful; calm.}{After his vacation in this placid section, he felt soothed and rested.}
\entry{plaudit}{N.}{喝彩}{enthusiastically worded approval; round of applause.}{The theatrical company reprinted the plaudits of the critics in its advertisements. plauditory,ADJ.}
\entry{plausible}{ADJ.}{似是而非的}{having a show of truth but open to doubt; specious.}{Your mother made you stay home from school because she needed you to program the VCR? I'm sorry, you'll have to come up with a more plausible excuse than that.}
\entry{plenitude}{N.}{充分, 富足}{abundance; completeness.}{Looking in the pantry, we admired the plenitude of fruits and pickles we had preserved during the summer.}
\entry{plight}{N.}{情况, 状况; 困境}{condition, state (especially a bad state or condition); predicament.}{Many people feel that the federal government should do more to alleviate the plight of the homeless. Loggers, unmoved by the plight of the spotted owl, plan to continue logging whether or not they ruin the owl's habitat.}
\entry{plummet}{V.}{垂直落下}{fall sharply.}{Stock prices plummeted as Wall Street reacted to the crisis in the economy.}
\entry{polarize}{V.}{极化; 分化; 两极分化}{split into opposite extremes or camps.}{The abortion issue has polarized the country into pro-choice and anti-abortion camps. polarization, N.}
\entry{politic}{ADJ.}{精明的; 明智的; 诡计多端的; 谨慎的}{expedient; prudent; well advised.}{Even though he was disappointed by the size of the bonus he was offered, he did not think it politic to refuse it.}
\entry{polyglot}{ADJ.}{多语言}{speaking several languages.}{New York City is a polyglot community because of the thousands of immigrants who settle there.}
\entry{ponderous}{ADJ.}{沉重的; 笨重的; 呆板的; 冗长的}{weighty; unwieldy.}{His humor lacked the light touch; his jokes were always ponderous.}
\entry{porous}{ADJ.}{筛子似的}{full of pores; like a sieve.}{Dancers like to wear porous clothing because it allows the ready passage of water and air.}
\entry{portend}{V.}{预示}{foretell; presage.}{The king did not know what these omens might portend and asked his soothsayers to interpret them.}
\entry{portent}{N.}{征兆}{sign; omen; forewarning.}{He regarded the black cloud as a portent of evil.}
\entry{posterity}{N.}{子孙; 后裔}{descendants; future generations.}{We hope to leave a better world to posterity.}
\entry{postulate}{N.}{前提; 基于的假定}{essential premise; underlying assumption.}{The basic postulate of democracy, set forth in the Declaration of Independence, is that all men are created equal.}
\entry{potent}{ADJ.}{有效的}{powerful; persuasive; greatly influential.}{Looking at the expiration date on the cough syrup bottle, we wondered whether the medication would still be potent. potency, N.}
\entry{potential}{ADJ.}{潜在的}{expressing possibility; latent.}{This juvenile delinquent is a potential murderer. also N.}
\entry{practicable}{ADJ.}{可行的}{feasible.}{The board of directors decided that the plan was practicable and agreed to undertake the project.}
\entry{pragmatic}{ADJ.}{实际的; 注重实效的}{practical (as opposed to idealistic); concerned with the practical worth or impact of something.}{This coming trip to France should provide me with a pragmatic test of the value of my conversational French class.}
\entry{precarious}{ADJ.}{不确定的; 冒风险}{uncertain; risky.}{Saying the stock would be a precarious investment, the broker advised her client against purchasing it.}
\entry{precedent}{N.}{先例}{something preceding in time that may be used as an authority or guide for future action.}{If I buy you a car for your sixteenth birthday, your brothers will want me to buy them cars when they turn sixteen, too; I can't afford to set such an expensive precedent. The law professor asked Jill to state which famous case served as a precedent for the court's decision in Brown ll.}
\entry{precipitate}{ADJ.}{匆忙的; 突然的; 未成熟的; 草率的}{rash; premature; hasty; sudden.}{Though I was angry enough to resign on the spot, I had enough sense to keep myself from quitting a job in such a precipitate fashion.}
\entry{precise}{ADJ.}{精确的}{exact.}{If you don't give me precise directions and a map, I'll never find your place.}
\entry{preclude}{V.}{消灭; 杜绝}{make impossible; eliminate.}{The fact that the band was already booked to play in Hollywood on New Year's Eve precluded their accepting the New Year's Eve gig in London they were offered.}
\entry{precocious}{ADJ.}{早熟的}{advanced in development.}{Listening to the grown-up way the child discussed serious topics, we couldn't help remarking how precocious she was. precocity, N.}
\entry{precursor}{N.}{领跑者, 先驱}{forerunner.}{Though Gray and Burns share many traits with the Romantic poets who followed them, most critics consider them precursors of the Romantic Movement, not true Romantics.}
\entry{predator}{N.}{捕食者}{creature that seizes and devours another animal; person who robs or exploits others.}{Not just cats, but a wide variety of predators-owls, hawks, weasels, foxescatch mice for dinner. A carnivore is by definition predatory, for he preys on weaker creatures.}
\entry{predicament}{N.}{困境; 危险的境地; 两难}{tricky or dangerous situation; dilemma.}{Tied to the railroad tracks by the villain, Pauline strained against her bonds. How would she escape from this terrible predicament?}
\entry{preeminent}{ADJ.}{出色的; 出类拔萃的}{outstanding; superior.}{The king traveled to Boston because he wanted the preeminent surgeon in the field to perform the operation.}
\entry{prelude}{N.}{序; 先驱; 先导}{introduction; forerunner.}{I am afraid that this border raid is the prelude to more serious attacks.}
\entry{premise}{N.}{假定, 假设; 前提}{assumption; postulate.}{Based on the premise that there's no fool like an old fool, P. T. Barnum hired a ninety-year-old clown for his circus.}
\entry{preposterous}{ADJ.}{荒唐的}{absurd; ridiculous.}{When he tried to downplay his youthful experiments with marijuana by saying he hadn't inhaled, we all thought, "What a preposterous excuse!"}
\entry{presage}{V.}{预示}{foretell.}{The vultures flying overhead presaged the discovery of the corpse in the desert.}
\entry{prescience}{N.}{预示能力}{ability to foretell the future.}{Given the current wave of Japan-bashing, it does not take prescience for me to foresee problems in our future trade relations with Japan.}
\entry{prestige}{N.}{声望; 威信}{impression produced by achievements or reputation.}{Many students want to go to Harvard College not for the education offered but for the prestige of Harvard's name.}
\entry{presumptuous}{ADJ.}{自大; 轻狂; 专横}{overconfident; impertinently bold; taking liberties.}{Matilda thought it was somewhat presumptuous of the young man to have addressed her without first having been introduced. Perhaps manners were freer here in the New World.}
\entry{prevalent}{ADJ.}{普遍的; 流行的}{widespread; generally accepted.}{A radical committed to social change, Reed had no patience with the conservative views prevalent in the America of his day.}
\entry{prey}{N.}{猎物; 受害人, 牺牲品}{target of a hunt; victim.}{In Stalking the Wild Asparagus, Euell Gibbons has as his prey not wild beasts but wild plants. alsoV.}
\entry{primordial}{ADJ.}{原始的; 与时间同在的}{existing at the beginning (of time); rudimentary.}{The Neanderthal Man is one of our primordial ancestors.}
\entry{pristine}{ADJ.}{史前的; 质朴的}{characteristic of earlier times; primitive; unspoiled.}{This area has been preserved in all its pristine wildness.}
\entry{probe}{V.}{探测}{explore with tools.}{The surgeon probed the wound for foreign matter before suturing it. also N.}
\entry{problematic}{ADJ.}{忧郁的; 忧心忡忡的; 心存疑虑的; 有疑问的}{doubtful; unsettled; questionable; perplexing.}{Given the way building costs have exceeded estimates for the job, whether the arena will ever be completed is problematic.}
\entry{proclivity}{N.}{倾向; 自然倾向}{inclination; natural tendency.}{Watching the two-year-old voluntarily put away his toys, I was amazed by his proclivityfor neatness.}
\entry{prodigal}{ADJ.}{浪费的}{wasteful; reckless with money.}{Don't be so prodigal spending my money; when you've earned some money yourself, you can waste it as much as you want! also N.}
\entry{prodigy}{N.}{奇才; 天才}{marvel; highly gifted child.}{Menuhin was a prodigy, performing wonders on his violin when he was barely eight years old.}
\entry{profligate}{ADJ.}{放荡的; 放肆的; 不检点的}{dissipated; wasteful; wildly immoral.}{Although surrounded by wild and profligate companions, she nevertheless managed to retain some sense of decency.}
\entry{profound}{ADJ.}{深刻的}{deep; not superficial; complete.}{Freud's remarkable insights into human behavior caused his fellow scientists to honor him as a profound thinker. profundity, N.}
\entry{progeny}{N.}{后裔}{children; offspring.}{He was proud of his progeny in general, but regarded George as the most promising of all his children.}
\entry{proliferation}{N.}{迅速增长, 倍增; 扩散}{rapid growth; spread; multiplication.}{Times of economic hardship inevitably encourage the proliferation of countless get-rich-quick schemes. proliferate,V.}
\entry{prolific}{ADJ.}{多产的; 丰富的}{abundantly fruitful.}{My editors must assume I'm a prolific writer: they expect me to revise six books this year!}
\entry{prolong}{V.}{拖延}{make longer; draw out; lengthen.}{In their determination to discover ways to prolong human life, doctors fail to take into account that longer lives are not always happier ones.}
\entry{prominent}{ADJ.}{突出的, 显著的; 杰出的; 卓越的}{}{}
\entry{promote}{V.}{提升; 促进}{help to flourish; advance in rank; publicize.}{Founder of the Children's Defense Fund, Marian Wright Edelman ceaselessly promotes the welfare of young people everywhere.}
\entry{prompt}{V.}{提示; 鼓动; 迅速及时的}{cause; provoke; provide a cue for an actor.}{Whatever prompted you to ask for such a big piece of cake when you're on a diet?}
\entry{prone}{ADJ.}{倾向于}{inclined to; prostrate.}{She was prone to sudden fits of anger during which she would lie prone on the floor, screaming and kicking her heels.}
\entry{propagate}{V.}{迅速增长, 传播, 扩散}{multiply; spread.}{Since bacteria propagate more quickly in unsanitary environments, it is important to keep hospital rooms clean.}
\entry{proponent}{N.}{支持者; 建议者}{supporter; backer; opposite of opponent.}{In the Senate, proponents of the universal health care measure lobbied to gain additional support for the controversial legislation.}
\entry{propriety}{N.}{适当}{fitness; correct conduct.}{Miss Manners counsels her readers so that they may behave with due propriety in any social situation and not embarrass themselves.}
\entry{prosperity}{N.}{繁荣; 好运}{good fortune; financial success; physical well-being.}{Promising to stay together "for richer, for poorer," the newlyweds vowed to be true to one another in prosperity and hardship alike.}
\entry{protrude}{V.}{突出}{stick out.}{His fingers protruded from the holes in his gloves. protrusion, N.}
\entry{provincial}{ADJ.}{省级的; 视野不宽的; 简单的}{pertaining to a province; limited in outlook; unsophisticated.}{As provincial governor, Sir Henry administered the Queen's law in his remote corner of Canada. Caught up in local problems, out of touch with London news, he became sadly provincial.}
\end{multicols}
\clearpage
\setList{28-30}

\begin{multicols}{2}
\entry{quagmire}{N.}{沼泽; 湿地}{soft wet boggy land; complex or dangerous situation from which it is difficult to free oneself.}{Up to her knees in mud, Myra wondered how on earth she was going to extricate herself from this quagmire.}
\entry{quail}{V.}{懦弱; 胆怯}{cower; lose heart.}{The Cowardly Lion was afraid that he would quail in the face of danger.}
\entry{qualified}{ADJ.}{有资格的; 有限制的; 被限制的}{limited; restricted.}{Unable to give the candidate full support, the mayor gave him only a qualified endorsement. (secondary meaning)}
\entry{quell}{V.}{扑灭; 镇压; 平息}{extinguish; put down; quiet.}{Miss Minchin's demeanor was so stern and forbidding that she could quell any unrest among her students with one intimidating glance.}
\entry{query}{N.}{问询; 质问}{inquiry; question.}{In her column "Ask Beth," the columnist invites young readers to send her their queries about life and love.}
\entry{quiescent}{ADJ.}{睡眠的; 休息的; 暂停活动的}{at rest; dormant; temporarily inactive.}{After the great eruption, fear of Mount Etna was great; people did not return to cultivate its rich hillside lands until the volcano had been quiescent for a full two years. quiescence, N.}
\entry{quip}{N.}{嘲弄; 讽刺}{taunt.}{You are unpopular because you are too free with your quips and sarcastic comments. alsoV.}
\entry{rabid}{ADJ.}{狂暴的; 激烈的}{like a fanatic; furious.}{He was a rabid follower of the Dodgers and watched them play whenever he could go to the ball park.}
\entry{ramble}{V.}{游荡; 漫无目的游荡}{wander aimlessly (physically or mentally).}{Listening to the teacher ramble, Judy wondered whether he'd ever get to his point.}
\entry{rancor}{N.}{苦难}{bitterness; hatred.}{Thirty years after the war, she could not let go of the past but was still consumed with rancor against the foe.}
\entry{random}{ADJ.}{随机的}{without definite purpose, plan, or aim; haphazard.}{Although the sponsor of the raffle claimed all winners were chosen at random, people had their suspicions when the grand prize went to the sponsor's brother-in-law.}
\entry{ratify}{V.}{批准, 认可}{approve formally; confirm; verify.}{Party leaders doubted that they had enough votes in both houses of Congress to ratify the constitutional amendment.}
\entry{rationale}{N.}{基础科学; 基本原理}{fundamental reason or justification; grounds for an action.}{Her need to have someplace to hang her earring collection was Dora's rationale for piercing fifteen holes in each ear.}
\entry{ravenous}{ADJ.}{饥饿的}{extremely hungry.}{The ravenous dog upset several garbage pails in its search for food.}
\entry{raze}{V.}{彻底摧毁}{destroy completely.}{Spelling is important: to raise a building is to put it up; to raze a building is to tear it down.}
\entry{reactionary}{ADJ.}{反作用的}{recoiling from progress; politically ultraconservative.}{Opposing the use of English in worship services, reactionary forces in the church fought to reinstate the mass in Latin.}
\entry{realm}{N.}{领域}{kingdom; field or sphere.}{In the animal realm, the lion is the king of beasts.}
\entry{rebuke}{V.}{严厉批评; 猛烈的训斥}{scold harshly; criticize severely.}{No matter how sharply Miss Watson rebuked Huck for his misconduct, he never talked back but just stood there like a stump. also N.}
\entry{rebuttal}{N.}{驳斥; 举反证}{refutation; response with contrary evidence.}{The defense lawyer confidently listened to the prosecutor sum up his case, sure that she could answer his arguments in her rebuttal.}
\entry{recant}{V.}{放弃; 宣布放弃}{disclaim or disavow; retract a previous statement; openly confess error.}{Those who can, keep true to their faith; those who can't, recant. Hoping to make Joan of Arc recant her sworn testimony, her English captors tried to convince her that her visions had been sent to her by the Devil.}
\entry{recast}{V.}{重建}{reconstruct (a sentence, story, etc.}{; fashion again. Let me recast this sentence in terms your feeble brain can grasp: in words of one syllable, you are a fool.}
\entry{receptive}{ADJ.}{善于接受的}{quick or willing to receive ideas, suggestions, etc.}{Adventure-loving Huck Finn proved a receptive audience for Tom's tales of buried treasure and piracy.}
\entry{recession}{N.}{撤退}{withdrawal; retreat; time of low economic activity.}{The slow recession of the flood waters created problems for the crews working to restore power to the area. recede,V.}
\entry{recipient}{N.}{接受的东西; 容器}{receiver.}{Although he had been the recipient of many favors, he was not grateful to his benefactor.}
\entry{reconcile}{V.}{抛弃前嫌; 不打不相识; 结为好友; 化解冲突}{correct inconsistencies; become friendly after a quarrel.}{Each month when we try to reconcile our checkbook with the bank statement, we quarrel. However, despite these monthly lovers' quarrels, we always manage to reconcile.}
\entry{recount}{V.}{解说, 告诉; 重新数}{narrate or tell; count over again.}{A born storyteller, my father loved to recount anecdotes about his early years in New York.}
\entry{rectify}{V.}{纠正}{set right; correct.}{You had better send a check to rectify your account before American Express cancels your credit card.}
\entry{rectitude}{N.}{垂直; 正直; 公正}{uprightness; moral virtue; correctness of judgment.}{The Eagle Scout was a model of rectitude.}
\entry{recuperate}{V.}{恢复}{recover.}{The doctors were worried because the patient did not recuperate as rapidly as they had expected.}
\entry{recurrent}{ADJ.}{一遍又一遍发生的; 循环发生的}{occurring again and again.}{Richard's recurrent asthma attacks disturbed us and we consulted a physician.}
\entry{redoubtable}{ADJ.}{可怕的}{formidable; causing fear.}{During the Cold War period, neighboring countries tried not to offend the Russians because they could be redoubtable foes.}
\entry{redundant}{ADJ.}{冗余的; 多余的}{superfluous; repetitious; excessivejy wordy.}{The bottle of wine I brought to Bob's was certainly redundant how was I to know Bob owned a winery? In your essay, you repeat several points unnecessarily; try to be less redundant in the future. redundancy, N.}
\entry{refrain}{V.}{抵制; 抵抗; 远离, 节制}{abstain from; resist.}{Whenever he heard a song with a lively chorus, Sol could never refrain from joining in on the refrain.}
\entry{refute}{V.}{反驳}{disprove.}{The defense called several respectable witnesses who were able to refute the false testimony of the prosecution's sole witness. refutation, N.}
\entry{regeneration}{N.}{再生, 重生; 重建}{}{}
\entry{rehabilitate}{V.}{恢复; 复原}{restore to proper condition.}{We must rehabilitate those whom we send to prison.}
\entry{reimburse}{V.}{偿还}{repay.}{Let me know what you have spent and I will reimburse you.}
\entry{reiterate}{V.}{重申; 重复}{repeat.}{He reiterated the warning to make sure everyone understood it.}
\entry{relegate}{V.}{指派; 下放; 贬}{banish to an inferior position; delegate; assign.}{After Ralph dropped his second tray of drinks that week, the manager swiftly relegated him to a minor post cleaning up behind the bar.}
\entry{relevant}{ADJ.}{有关的; 相对的}{pertinent; referring to the case in hand.}{How relevant Virginia Woolf's essays are to women writers today! It's as if Woolf in the 193s foresaw our current literary struggles. relevancy, N.}
\entry{relinquish}{V.}{不情愿的屈服, 放弃（某物）}{give up something with reluctance; yield.}{Denise never realized how hard it would be for her to relinquish her newborn son to the care of his adoptive parents. Once you get used to fringe benefits like expense account meals and a company car, it's very hard to relinquish them.}
\entry{remediable}{ADJ.}{可挽回的}{reparable.}{Let us be grateful that the damage is remediable.}
\entry{remedial}{ADJ.}{治疗的, 补救的}{curative; corrective.}{Because he was a slow reader, he decided to take a course in remedial reading.}
\entry{remission}{N.}{减轻, 缓解; 宽恕}{temporary moderation of disease symptoms; cancellation of a debt; forgiveness or pardon.}{Though the senator had been treated for cancer, his symptoms were in remission, and he was considered fit enough to handle the strains of a presidential race.}
\entry{remorse}{N.}{懊悔, 自责}{guilt; self-reproach.}{The murderer felt no remorse for his crime.}
\entry{render}{V.}{呈递; 开账单; 给予; 还以, 报以; 放弃, 投降投降或交出; 放弃; 描写以文字形式表现, 描绘; 以图像或绘画表现; 演奏, 诠释; 翻译; 正式宣布; 裁决; 使成为; 熔解, 精炼; 打底}{deliver; provide; represent.}{He rendered aid to the needy and indigent.}
\entry{renounce}{V.}{放弃; 断绝关系}{abandon; disown; repudiate.}{Even though she knew she would be burned at the stake as a witch, Joan of Arc refused to renounce her belief that her voices came from God. renunciation, N.}
\entry{renovate}{V.}{革新; 刷新; 修复}{restore to good condition; renew.}{They claim that they can renovate worn shoes so that they look like new ones.}
\entry{renown}{N.}{名望}{fame.}{For many years an unheralded researcher, Barbara McClintock gained international renown when she won the Nobel Prize in Physiology and Medicine. renowned,ADJ.}
\entry{reparable}{ADJ.}{可修复的}{capable of being repaired.}{Fortunately, the damages we suffered in the accident were reparable and our car looks brand new.}
\entry{reparation}{N.}{修订; 弥补; 补偿}{amends; compensation.}{At the peace conference, the defeated country promised to pay reparations to the victors.}
\entry{repeal}{V.}{废除; 撤除}{revoke; annul.}{What would the effect on our society be if we decriminalized drug use by repealing the laws against the possession and sale of narcotics?}
\entry{repel}{V.}{撤退; 退却}{drive away; disgust.}{At first, the Beast's ferocious appearance repelled Beauty, but she came to love the tender heart hidden behind that beastly exterior.}
\entry{replenish}{V.}{补充}{fill up again.}{Before she could take another backpacking trip, Carla had to replenish her stock of freeze-dried foods.}
\entry{replete}{ADJ.}{充满的; 充足的}{filled to the brim or to the point of being stuffed; abundantly supplied.}{The movie star's memoir was replete with juicy details about the love life of half of Hollywood.}
\entry{replicate}{V.}{复制}{reproduce; duplicate.}{Because he had always wanted a palace, Donald decided to replicate the Tai Mahal in miniature on his estate.}
\entry{reprehensible}{ADJ.}{应斥责的; 应该谴责的}{}{}
\entry{repress}{V.}{压迫; 压制; 压}{restrain; crush; oppress.}{Anne's parents tried to curb her impetuosity without repressing her boundless high spirits.}
\entry{reprimand}{V.}{谴责}{reprove severely; rebuke.}{Every time Ermengarde made a mistake in class, she was afraid that Miss Minchin would reprimand her and tell her father how badly she was doing in school. also N.}
\entry{reprove}{V.}{责备}{censure; rebuke.}{The principal severely reproved the students whenever they talked in the halls.}
\entry{reputable}{ADJ.}{著名的; 令人尊敬的}{respectable.}{If you want to buy antiques, look for a reputable dealer; far too many dealers today pass off fakes as genuine antiques.}
\entry{requisite}{N.}{必须品; 必要的}{necessary requirement.}{Many colleges state that a student must offer three years of a language as a requisite for admission.}
\entry{rescind}{V.}{取消}{cancel.}{Because of the public outcry against the new taxes, the senator proposed a bill to rescind the unpopular financial measure.}
\entry{reserve}{N.}{自我控制; 疏远}{self-control; formal but distant manner.}{Although some girls were attracted by Mark's air of reserve, Judy was put off by it, for she felt his aloofness indicated a lack of openness. reserved,ADJ.}
\entry{resigned}{ADJ.}{认命, 顺从; 听天由命}{accepting one's fate; unresisting; patiently submissive.}{Resigned to his downtrodden existence, Bob Cratchit was too meek to protest Scrooge's bullying. resignation, N.}
\entry{resolution}{N.}{坚定; 决心; 决定}{determination; resolve.}{Nothing could shake his resolution that his children would get the best education that money could buy. resolute,ADJ.}
\entry{restraint}{N.}{抑制; 控制}{moderation or self-control; controlling force; restriction.}{Control yourself. young lady! Show some restraint!}
\entry{retain}{V.}{保持; 使用}{keep; employ.}{Fighting to retain his seat in Congress, Senator Foghorn retained a new manager to head his reelection campaign.}
\entry{retract}{V.}{撤回, 撤退}{withdraw; take back.}{When I saw how Fred and his fraternity brothers had trashed the frat house, I decided to retract my offer to let them use our summer cottage for the weekend. retraction, N.}
\entry{retrieve}{V.}{重新得到; 找回}{recover; find and bring in.}{The dog was intelligent and quickly learned to retrieve the game killed by the hunter.}
\entry{retroactive}{ADJ.}{反动的; （法律）追溯的（由制定之日前的某一天生效）}{of a law that dates back to a period before its enactment.}{Because the law was retroactive to the first of the year, we found she was eligible for the pension.}
\entry{retrograde}{V.}{倒退的}{go backwards; degenerate.}{instead of advancing, our civilization seems to have retrograded in ethics and culture. alsoADJ.}
\entry{revoke}{V.}{撤回; 取消}{cancel; retract.}{Repeat offenders who continue to drive under the influence of alcohol face having their driver's licenses permanently revoked.}
\entry{rigid}{ADJ.}{刚硬的; 不屈的}{stiff and unyielding; strict; hard and unbending.}{By living with a man to whom she was not married, George Eliot broke Victorian society's most rigid rule of respectable behavior.}
\entry{rigorous}{ADJ.}{严峻的; 严格的; 严厉的}{severe; harsh; demanding; exact.}{Disliked by his superiors, the officer candidate in An Officer and a Gentleman endured an extremely rigorous training program.}
\entry{robust}{ADJ.}{健壮的}{vigorous; strong.}{After pumping iron and taking karate for six months, the little old lady was so robust that she could break a plank with her fist.}
\entry{roster}{N.}{列表}{list.}{They print the roster of players in the season's program.}
\entry{rudimentary}{ADJ.}{原始的; 最初的; 原来的}{not developed; elementary; crude.}{Although my grandmother's English vocabulary was limited to a few rudimentary phrases, she always could make herself understood.}
\entry{ruthless}{ADJ.}{无情的}{pitiless; cruel.}{Captain Hook was a dangerous, ruthless villain who would stop at nothing to destroy Peter Pan.}
\entry{sagacious}{ADJ.}{有洞察力的}{perceptive; shrewd; having insight.}{My father was a sagacious judge of character: he could spot a phony a mile away. sagacity, N.}
\entry{sage}{N.}{智者; 圣人}{person celebrated for wisdom.}{Hearing tales of a mysterious Master of All Knowledge who lived in the hills of Tibet, Sandy was possessed with a burning desire to consult the legendary sage. alsoADJ.}
\entry{salient}{ADJ.}{显著的; 突出的; 卓越的}{prominent.}{One of the salient features of that newspaper is its excellent editorial page.}
\entry{salutary}{ADJ.}{有用的; 有益的}{tending to improve; beneficial; wholesome.}{The punishment had a salutary effect on the boy, as he became a model student.}
\entry{salvage}{V.}{补救; 抢救; 打捞; 营救}{rescue from loss.}{All attempts to salvage the wrecked ship failed. also N.}
\entry{sanction}{V.}{批准, 许可}{approve; ratify.}{Nothing will convince me to sanction the engagement of my daughter to such a worthless young man.}
\entry{sanctuary}{N.}{避难所}{refuge; shelter; shrine; holy place.}{The tiny attic was Helen's sanctuary to which she fled when she had to get away from the rest of her family.}
\entry{sanguine}{ADJ.}{高兴的; 有希望的; 乐天的}{cheerful; hopeful.}{Let us not be too sanguine about the outcome; something could go wrong.}
\entry{satire}{N.}{讽刺的}{form of literature in which irony, sarcasm, and ridicule are employed to attack vice and folly.}{Gulliver's Travels, which is regarded by many as a tale for children, is actually a bitter satire attacking man's folly.}
\entry{satirical}{ADJ.}{嘲弄的}{mocking.}{The humor of cartoonist Gary Trudeau often is satirical; through the comments of the Doonesbury characters, Trudeau ridicules political corruption and folly.}
\entry{saturate}{V.}{湿透}{soak thoroughly.}{Saturate your sponge with water until it can't hold any more.}
\entry{savory}{ADJ.}{有味道的; 吸引人的}{tasty; pleasing, attractive, or agreeable.}{Julia Child's recipes enable amateur chefs to create savory delicacies for their guests.}
\entry{scale}{V.}{爬升; 升高}{climb up; ascend.}{In order to locate a book on the top shelf of the stacks, Lee had to scale an exceptionally rickety ladder.}
\entry{scanty}{ADJ.}{缺乏的; 稀疏的}{meager; insufficient.}{Thinking his helping of food was scanty, Oliver Twist asked for more.}
\entry{scenario}{N.}{情节; 剧本大纲; （电影、歌剧）剧本}{plot outline; screenplay; opera libretto.}{Scaramouche startled the other actors in the commedia troupe when he suddenly departed from their customary scenario and began to improvise.}
\entry{schematic}{ADJ.}{示例的; 示意性的}{relating to an outline or diagram; using a system of symbols.}{In working out the solution to this logic puzzle, you may find it helpful to construct a simple schematic diagram outlining the order of events.}
\entry{scrupulous}{ADJ.}{小心翼翼的; 谨慎的}{conscientious; extremely thorough.}{Though Alfred is scrupulous in fulfilling his duties at work, he is less conscientious about his obligations to his family and friends.}
\entry{scurvy}{ADJ.}{下流的; 卑鄙的, 无理的; 坏血病}{despicable; contemptible.}{Peter Pan sneered at Captain Hook and his scurvy crew.}
\entry{seasoned}{ADJ.}{老练的}{experienced.}{Though pleased with her new batch of rookies, the basketball coach wished she had a few more seasoned players on the team.}
\entry{secession}{N.}{撤退; 脱离}{withdrawal.}{The secession of the Southern states provided Lincoln with his first major problem after his inauguration. secede,V.}
\entry{seclusion}{N.}{隔离}{isolation; solitude.}{One moment she loved crowds; the next, she sought seclusion. seclude,V.}
\end{multicols}
\clearpage
\setList{31-33}

\begin{multicols}{2}
\entry{sedate}{ADJ.}{安静的; 稳重的; 低沉的}{composed; grave.}{The parents were worried because they felt their son was too quiet and sedate.}
\entry{sedition}{N.}{抵抗当局; 反抗; 暴动}{resistance to authority; insubordination.}{His words, though not treasonous in themselves, were calculated to arouse thoughts of sedition.}
\entry{sedulous}{ADJ.}{勤奋的; 勤勤恳恳的}{diligent; hardworking.}{After weeks of patient and sedulous labor, we completed our detailed analysis of every published SAT examination.}
\entry{seemly}{ADJ.}{适宜的, 合适的}{proper; appropriate.}{Lady Bracknell did not think it was seemly for Ernest to lack a proper family: no baby abandoned on a doorstep could grow up to be a fit match for her daughter.}
\entry{seep}{V.}{渗出; 渗漏}{ooze; trickle.}{During the rainstorm, water seeped through the crack in the basement wall and damaged the floor boards. seepage, N.}
\entry{sequester}{V.}{隐退; 隔离}{isolate; retire from public life; segregate; seclude.}{Banished from his kingdom, the wizard Prospero sequestered himself on a desert island. To prevent the jurors from hearing news broadcasts about the case, the judge decided to sequester the jury.}
\entry{serenity}{N.}{平静}{calmness; placidity.}{The sound of air raid sirens pierced the serenity of the quiet village of Pearl Harbor. serpentine ADJ. winding; twisting. The car swerved at every curve in the serpentine road.}
\entry{servile}{ADJ.}{奴隶的; 奴性的}{slavish; cringing.}{Constantly fawning on his employer, humble Uriah Heap was a servile creature.}
\entry{sever}{V.}{切断}{cut; separate.}{The released prisoner wanted to begin a new life and sever all connections with his criminal past. Dr. Guillotin invented a machine that could neatly sever an aristocratic head from its equally aristocratic body. Unfortunately, he couldn't collect any severance pay. severance, N.}
\entry{severity}{N.}{严肃; 严格; 激烈}{harshness; intensity; sternness; austerity.}{The severity of Jane's migraine attack was so great that she took to her bed for a week.}
\entry{shear}{V.}{剪; 修剪}{cut or clip (hair, fleece); strip of something.}{You may not care to cut a sheep's hair, but Sarah shears sheep for Little Bo Peep.}
\entry{sheer}{ADJ.}{纯粹的,, 绝对的; 透明的; 峻峭的; 避开, 躲避; 偏航, 避开}{very thin or transparent; very steep; absolute.}{Wearing nothing but an almost sheer robe, Delilah draped herself against the sheer temple wall. Beholding her, Samson was overcome by her sheer beauty. Then she sheared his hair.}
\entry{shimmer}{V.}{微光}{glimmer intermittently.}{The moonlight shimmered on the water as the moon broke through the clouds for a moment. also N.}
\entry{shroud}{V.}{裹尸; 隐藏}{hide from view; wrap for burial.}{Fog shrouded Dracula's castle, hiding the ruined tower beneath sheets of mist.}
\entry{sibling}{N.}{兄弟姐妹}{brother or sister.}{We may not enjoy being siblings, but we cannot forget that we still belong to the same family.}
\entry{simile}{N.}{明喻; 比较}{comparison of one thing with another, using the word like or as.}{"My love is like a red, red rose" is a simile.}
\entry{simplistic}{ADJ.}{过分单纯化的}{oversimplified.}{Though Jack's solution dealt adequately with one aspect of the problem, it was simplistic in failing to consider various complications that might arise.}
\entry{simulate}{V.}{模仿; 冒充}{feign.}{He simulated insanity in order to avoid punishment for his crime.}
\entry{singular}{ADJ.}{奇的; 独一无二的}{unique; extraordinary; odd.}{Though the young man tried to understand Father William's singular behavior, he still found it odd that the old man incessantly stood on his head. singularity, N.}
\entry{sinister}{ADJ.}{邪恶的}{evil.}{We must defeat the sinister forces that seek our downfall.}
\entry{skeptic}{N.}{怀疑论者}{doubter; person who suspends judgment until the evidence supporting a point of view has been examined.}{I am a skeptic about the new health plan; I want some proof that it can work. skepticism, N.}
\entry{slander}{N.}{诽谤}{defamation; utterance of false and malicious statements.}{Considering the negative comments politicians make about each other, it's a wonder that more of them aren't sued for slander. alsoV.}
\entry{slight}{N.}{怠慢; 斥责; 侮辱}{insult to one's dignity; snub.}{Hypersensitive and ready to take offense at any discourtesy, Bertha was always on the lookout for real or imaginary slights. alsoV.}
\entry{sluggish}{ADJ.}{行动迟缓的}{Slow; lazy; lethargic.}{After two nights without sleep, she felt sluggish and incapable of exertion.}
\entry{smirk}{N.}{傻笑}{conceited smile.}{Wipe that smirk off your face! alsoV.}
\entry{sobriety}{N.}{清醒, 冷静; 节制; 严肃}{}{}
\entry{solemnity}{N.}{严肃的; 一本正经的}{seriousness; gravity.}{The minister was concerned that nothing should disturb the solemnity of the marriage service. solemn,ADJ.}
\entry{solicit}{V.}{恳求}{request earnestly; seek.}{Knowing she needed to have a solid majority for the budget to pass, the mayor telephoned all the members of the city council to solicit their votes.}
\entry{solicitous}{ADJ.}{担心的; 关切的; 期望的}{worried; concerned.}{The employer was very solicitous about the health of her employees as replacements were difficult to get.}
\entry{solitude}{N.}{独身}{state of being alone; seclusion.}{Much depends on how much you like your own company. What to one person seems fearful isolation to another is blessed solitude.}
\entry{solvent}{ADJ.}{有偿付能力的}{able to pay all debts.}{By dint of very frugal living, he was finally able to become solvent and avoid bankruptcy proceedings.}
\entry{somber}{ADJ.}{阴森的; 昏暗的; 抑郁的}{gloomy; depressing; dark; drab.}{From the doctor's grim expression, I could tell he had somber news. Dull brown and charcoal gray are pretty somber colors; can't you wear something bright?}
\entry{sophisticated}{ADJ.}{世故的; 复杂的}{worldly-wise and urbane; complex.}{When Sophie makes wisecracks, she thinks she sounds sophisticated, but instead she sounds sophomoric. The new IBM laptop with the butterfly keyboard and the built-in quadspeed FAX modem is a pretty sophisticated machine.}
\entry{sophistry}{N.}{似真实假的}{seemingly plausible but fallacious reasoning.}{Instead of advancing valid arguments, he tried to overwhelm his audience with a flood of sophistries.}
\entry{sophomoric}{ADJ.}{一知半解的; 不成熟的}{immature; half-baked, like a sophomore.}{Even if you're only a freshman, it's no compliment to be told your humor is sophomoric. The humor in Dumb and Dumber is sophomoric at best.}
\entry{sovereign}{ADJ.}{君主的; 至高无上的}{efficacious; supreme or paramount; selfgoverning.}{Professor Pennywhistle claimed his panacea was a sovereign cure for all chronic complaints. In medicine the sovereign task of the doctor is to do no harm. Rebelling against the mother country, the onetime colony now proclaimed itself a sovereign state. also N.}
\entry{sparse}{ADJ.}{稀少的; 稀疏的}{not thick; thinly scattered; scanty.}{No matter how carefully Albert combed his hair to make it look as full as possible, it still looked sparse.}
\entry{spasmodic}{ADJ.}{断断续续的; 间歇的}{fitful; periodic.}{The spasmodic coughing in the auditorium annoyed the performers.}
\entry{spatial}{ADJ.}{空间的}{relating to space.}{NASA is engaged in an ongoing program of spatial exploration. When Jay says he's studying spatial relations, that doesn't mean he has relatives in outer space.}
\entry{spawn}{V.}{孵化; 下蛋}{lay eggs.}{Fish ladders had to be built in the dams to assist the salmon returning to spawn in their native streams. also N.}
\entry{specious}{ADJ.}{似是而非的}{seemingly reasonable but incorrect; misleading (often intentionally).}{To claim that, because houses and birds both have wings, both can fly, is extremely specious reasoning.}
\entry{spectrum}{N.}{光谱}{colored band produced when beam of light passes through a prism.}{The visible portion of the spectrum includes red at one end and violet at the other.}
\entry{spendthrift}{N.}{挥霍的人}{someone who wastes money.}{Easy access to credit encourages people to turn into spendthrifts who shop till they drop.}
\entry{spontaneity}{N.}{自发的; 自然的; 无预谋的}{lack of premeditation; naturalness; freedom from constraint.}{When Anne and Amy met, Amy impulsively hugged her new colleague, but Anne drew back, unprepared for such spontaneity. The cast over-rehearsed the play so much that the eventual performance lacked any spontaneity. spontaneous,ADJ.}
\entry{sporadic}{ADJ.}{零星的}{occurring irregularly.}{Although you can still hear sporadic outbursts of laughter and singing outside, the big Halloween parade has passed; the party's over till next year.}
\entry{spurious}{ADJ.}{伪造的, 欺骗的}{false; counterfeit; forged; illogical.}{The antique dealer hero of Jonathan Gash's mystery novels gives the reader tips on how to tell spurious antiques from the real thing. Natasha's claim to be the lost heir of the Romanoffs was spurious: the only thing Russian about her was the vodka she drank!}
\entry{squander}{V.}{浪费}{waste.}{If you squander your allowance on candy and comic books, you won't have any money left to buy the new box of crayons you want.}
\entry{stagnant}{ADJ.}{静止的; 单调的}{motionless; stale; dull.}{Mosquitoes commonly breed in ponds of stagnant water. Mike's career was stagnant; it wasn't going anywhere, and neither was he! stagnate,V.}
\entry{stamina}{N.}{毅力; 意志力}{strength; staying power.}{I doubt that she has the stamina to run the full distance of the marathon race.}
\entry{static}{ADJ.}{静态的}{unchanging; lacking development.}{Why watch chess on TV? I like watching a game with action, not something static where nothing seems to be going on.}
\entry{statute}{N.}{法令; 条例}{law enacted by the legislature.}{The statute of limitations sets the limits on how long you have to take legal action in specific cases.}
\entry{steadfast}{ADJ.}{坚定的; 不渝的; 忠诚的}{loyal; unswerving.}{Penelope was steadfast in her affections, faithfully waiting for Ulysses to return from his wanderings.}
\entry{steep}{V.}{浸泡, 弄湿; 陡坡; 悬崖}{soak; saturate.}{Be sure to steep the fabric in the dyebath for the full time prescribed.}
\entry{stellar}{ADJ.}{星体的; 恒星的}{pertaining to the stars.}{He was the stellar attraction of the entire performance.}
\entry{stem}{V.}{制止流出}{check the flow.}{The paramedic used a tourniquet to stem the bleeding from the slashed artery.}
\entry{stereotype}{N.}{老套; 一成不变; 铅版}{fixed and unvarying representation; standardized mental picture, often reflecting prejudice.}{Critics object to the character of Jim in The Adventures of Huckleberry Finn because he seems to reflect the stereotype of the happy, ignorant slave.}
\entry{stint}{N.}{供应; 分配; 限量分配}{supply; allotted amount; assigned portion of work.}{He performed his daily stint cheerfully and willingly. alsoV.}
\entry{stipulate}{V.}{规定; 明细化}{make express conditions; specify.}{Before agreeing to reduce American military forces in Europe, the president stipulated that NATO inspection teams be allowed to inspect Soviet bases.}
\entry{stratum}{N.}{地层; 社会阶层}{layer of earth's surface; layer of society.}{Unless we alleviate conditions in the lowest stratum of our society, we may expect grumbling and revolt.}
\entry{strew}{V.}{散开; 随意散开; 散播}{spread randomly; sprinkle; scatter.}{Preceding the bride to the altar, the flower girl will strew rose petals along the aisle.}
\entry{strut}{N.}{大摇大摆; 高视阔步}{pompous walk; swagger.}{Looking at his selfimportant strut as he swaggered about the parade ground, I could tell Colonel Blimp thought highly of himself. alsoV.}
\entry{subjective}{ADJ.}{主观的; 个人的}{occurring or taking place within the subject; unreal.}{Your analysis is highly subjective; you have permitted your emotions and your opinions to color your thinking.}
\entry{subjugate}{V.}{征服}{conquer; bring under control.}{It is not our aim to subjugate our foe; we are interested only in establishing peaceful relations.}
\entry{submissive}{ADJ.}{屈服的; 胆怯的}{yielding; timid.}{When he refused to permit Elizabeth to marry her poet, Mr. Barrett expected her to be properly submissive; instead, she eloped!}
\entry{subordinate}{ADJ.}{低级的; 下级的; 次要的}{occupying a lower rank; inferior; submissive.}{Bishop Proudie's wife expected all the subordinate clergy to behave with great deference to the wife of their superior.}
\entry{subsequent}{ADJ.}{后来的; 接下来的}{following; later.}{In subsequent lessons, we shall take up more difficult problems.}
\entry{subside}{V.}{下沉; 平息; 减退}{settle down; descend; grow quiet.}{The doctor assured us that the fever would eventually subside.}
\entry{substantial}{ADJ.}{坚实的; 充实的}{ample; solid; in essentials.}{The generous scholarship represented a substantial sum of money.}
\entry{substantiate}{V.}{证实; 验证}{establish by evidence; verify; support.}{These endorsements from satisfied customers substantiate our claim that Barron's How to Prepare for the SAT I is the best SAT-prep book on the market.}
\entry{subtlety}{N.}{精明; 稀薄; 微妙}{perceptiveness; ingenuity; delicacy.}{Never obvious, she expressed herself with such subtlety that her remarks went right over the heads of most of her audience. subtle,ADJ.}
\entry{succinct}{ADJ.}{简洁的; 紧身的}{brief; terse; compact.}{Don't bore your audi ence with excess verbiage: be succinct.}
\entry{summit}{N.}{巅峰; 顶点}{utmost height or pinnacle; highest point (of a mountain, etc.}{ The summit of the amateur mountain climber's aspirations was someday to reach the summit of Mount Everest.}
\entry{sumptuous}{ADJ.}{奢侈的; 华丽的}{lavish; rich.}{I cannot recall when I have had such a sumptuous Thanksgiving feast.}
\entry{superficial}{ADJ.}{肤浅的; 浅薄的}{trivial; shallow.}{Since your report gave only a superficial analysis of the problem, I cannot give you more than a passing grade.}
\entry{superimpose}{V.}{添加}{place over something else.}{Your attempt to superimpose another agency in this field will merely increase the bureaucratic nature of our government.}
\entry{supersede}{V.}{取代; 推迟}{cause to be set aside; replace; make obsolete.}{The new bulk mailing postal regulation supersedes the old one. If you continue to follow the old regulation, your bulk mailing will be returned to you.}
\entry{supplicate}{V.}{恳求; 祈祷}{petition humbly; pray to grant a favor.}{We supplicate Your Majesty to grant him amnesty.}
\entry{supposition}{N.}{假定; 假想}{hypothesis; the act of supposing.}{I based my decision to confide in him on the supposition that he would be discreet. suppose,V.}
\entry{suppress}{V.}{镇压; 抑制; 查禁}{stifle; overwhelm; subdue; inhibit.}{Too polite to laugh in anyone's face, Roy did his best to suppress his amusement at Ed's inane remark.}
\entry{surpass}{V.}{超越}{exceed.}{Her SAT I scores surpassed our expectations.}
\entry{susceptible}{ADJ.}{易受影响的; 易感动的; 易患病的}{impressionable; easily influenced; having little resistance, as to a disease; receptive to.}{Said the patent medicine man to his very susceptible customer: "Buy this new miracle drug, and you will no longer be susceptible to the common cold."}
\entry{swagger}{V.}{大摇大摆; 自大}{behave arrogantly or pompously; strut or walk proudly.}{The conquering hero didn't simply stride down the street; he swaggered. also N.}
\entry{symmetry}{N.}{对称; 匀称}{arrangement of parts so that balance is obtained; congruity.}{Something lopsided by definition lacks symmetry.}
\entry{synthesis}{N.}{合成}{combining parts into a whole.}{Now that we have succeeded in isolating this drug, our next problem is to plan its synthesis in the laboratory. synthesize,V.}
\entry{tangible}{ADJ.}{可触摸的; 真实的}{able to be touched; real; palpable.}{Although Tom did not own a house, he had several tangible assets-a car, a television, a PC-that he could sell if he needed cash.}
\entry{tantamount}{ADJ.}{同等的}{equivalent in effect or value.}{Though Rudy claimed his wife was off visiting friends, his shriek of horror when she walked into the room was tantamount to a confession that he believed she was dead.}
\entry{tedious}{ADJ.}{令人厌倦的}{boring; tiring.}{The repetitious nature of work on the assembly line made Martin's job very tedious. tedium, N.}
\entry{temper}{V.}{中和; 回火; 调剂; 锻炼}{moderate; tone down or restrain; toughen (steel).}{Not even her supervisor's grumpiness could temper Nancy's enthusiasm for her new job.}
\entry{temperament}{N.}{气质; 性情}{characteristic frame of mind; disposition; emotional excess.}{Although the twins look alike, they differ markedly in temperament: Todd is calm, but Rod is excitable.}
\entry{temporal}{ADJ.}{暂时的}{not lasting forever; limited by time; secular.}{At onetime in our history, temporal rulers assumed that they had been given their thrones by divine right.}
\entry{tenacious}{ADJ.}{顽强的}{holding fast.}{I had to struggle to break his tenacious hold on my arm.}
\entry{tender}{V.}{提供; 扩充}{offer; extend.}{Although no formal charges had been made against him, in the wake of the recent scandal the mayor felt he should tender his resignation.}
\entry{tentative}{ADJ.}{试验性的, 暂定的; 踌躇的}{}{}
\entry{termination}{N.}{结束}{end.}{Though the time for termination of the project was near, we still had a lot of work to finish before we shut up shop. terminate,V.}
\entry{terrestrial}{ADJ.}{地的; 地球的}{earthly (as opposed to celestial); pertaining to the land.}{In many science fiction films, alien invaders from outer space plan to destroy all terrestrial life.}
\entry{theoretical}{ADJ.}{理论的}{not practical or applied; hypothetical.}{Bob was better at applied engineering and computer programming than he was at theoretical physics and math. While I can still think of some theoretical objections to your plan, you've convinced me of its basic soundness.}
\entry{thermal}{ADJ.}{热的; 热学的}{pertaining to heat.}{The natives discovered that the hot springs made excellent thermal baths and began to develop their community as a health resort. also N.}
\entry{thrive}{V.}{繁荣; 昌盛}{prosper; flourish.}{Despite the impact of the recession on the restaurant trade, Philip's cafe thrived.}
\entry{throng}{N.}{聚集}{crowd.}{Throngs of shoppers jammed the aisles. alsoV.}
\entry{timorous}{ADJ.}{害怕的}{fearful; demonstrating fear.}{His timorous manner betrayed the fear he felt at the moment.}
\end{multicols}
\clearpage
\setList{34-35}

\begin{multicols}{2}
\entry{titanic}{ADJ.}{巨大的}{gigantic.}{Titanic waves beat against the majestic S.S. Titanic, driving it against the concealed iceberg.}
\entry{title}{N.}{名字; 等级; 拥有权}{right or claim to possession; mark of rank; name (of a book, film, etc.}{. Though the penniless Duke of Ragwort no longer held title to the family estate, he still retained his title as head of one of England's oldest families.}
\entry{titular}{ADJ.}{有名无实的}{nominal holding of title without obligations.}{Although he was the titular head of the company, the real decisions were made by his general manager.}
\entry{tonic}{ADJ.}{精神充沛的}{invigorating; refreshing.}{The tart homemade ginger ale had a tonic effect on Kit: she perked right up. also N.}
\entry{torpor}{N.}{迟钝; 麻木; 不活泼}{lethargy; sluggishness; dormancy.}{Throughout the winter, nothing aroused the bear from his torpor: he would not emerge from hibernation until spring. torpid,ADJ.}
\entry{tortuous}{ADJ.}{曲折的, 蜿蜒的}{winding; full of curves.}{Because this road is so tortuous, it is unwise to go faster than twenty miles an hour on it.}
\entry{touchstone}{N.}{试金石; 准绳; 标准; 尺度}{stone used to test the fineness of gold alloys; criterion.}{What touchstone can be used to measure the character of a person?}
\entry{touchy}{ADJ.}{暴躁的; 难以处理的; 易上火的}{sensitive; irascible.}{Do not mention his bald spot; he's very touchy about it.}
\entry{toxic}{ADJ.}{有毒的}{poisonous.}{We must seek an antidote for whatever toxic substance he has eaten. toxicity, N.}
\entry{tractable}{ADJ.}{驯良的; 温顺的; 易处理的}{docile; easily managed.}{Although Susan seemed a tractable young woman, she had a stubborn streak of independence that occasionally led her to defy the powers-that-be when she felt they were in the wrong.}
\entry{tranquility}{N.}{宁静; 平静}{}{}
\entry{transcendent}{ADJ.}{卓越的; 非比寻常的}{surpassing; exceeding ordinary limits; superior.}{For the amateur chef, dining at the four-star restaurant was a transcendent experience: the meal surpassed his wildest dreams.}
\entry{transgression}{N.}{犯罪}{violation of a law; sin.}{Forgive us our transgressions; we know not what we do.}
\entry{transient}{ADJ.}{暂时的}{momentary; temporary; staying for a short time.}{Lexy's joy at finding the perfect Christmas gift for Phil was transient, she still had to find presents for the cousins and Uncle Bob. Located near the airport, this hotel caters to a largely transient trade. transience, N.}
\entry{transition}{N.}{过渡; 转换; 跃迁}{going from one state of action to another.}{During the period of transition from oil heat to gas heat, the furnace will have to be shut off.}
\entry{translucent}{ADJ.}{半透明的}{partly transparent.}{We could not recognize the people in the next room because of the translucent curtains that separated us.}
\entry{transparent}{ADJ.}{透明的; 容易检测的, 明晰的}{easily detected; permitting light to pass through freely.}{John's pride in his son is transparent; no one who sees the two of them together can miss it.}
\entry{transport}{N.}{运输; 狂喜}{strong emotion.}{Margo was a creature of extremes, at one moment in transports of joy over a vivid sunset, at another moment in transports of grief over a dying bird. also V. (secondary meaning)}
\entry{traverse}{V.}{穿过}{go through or across.}{When you traverse this field, be careful of the bull.}
\entry{treatise}{N.}{论文}{article treating a subject systematically and thoroughly.}{He is preparing a treatise on the Elizabethan playwrights for his graduate degree.}
\entry{tremulous}{ADJ.}{震荡的}{trembling; wavering.}{She was tremulous more from excitement than from fear.}
\entry{trespass}{V.}{过失; 侵入}{unlawfully enter the boundaries of some else's property.}{The wicked baron flogged any poacher who trespassed on his private hunting grounds. also N.}
\entry{trigger}{V.}{引起; 触发; 扳机}{set off.}{John is touchy today; say one word wrong and you'll trigger an explosion.}
\entry{trivial}{ADJ.}{不重要的}{unimportant; trifling.}{Too many magazines ignore newsworthy subjects and feature trivial affairs. trivia, N.}
\entry{tundra}{N.}{苔原; 冻土}{rolling, treeless plain in Siberia and arctic North America.}{Despite the cold, many geologists are trying to discover valuable mineral deposits in the tundra.}
\entry{turbulence}{N.}{湍流; 骚乱; 动荡}{state of violent agitation.}{Warned of approaching turbulence in the atmosphere, the pilot told the passengers to fasten their seat belts.}
\entry{turmoil}{N.}{骚动; 混乱}{great commotion and confusion.}{Lydia running off with a soldier! Mother fainting at the news! The Bennet household was in turmoil.}
\entry{tutelage}{N.}{监护}{guardianship; training.}{Under the tutelage of such masters of the instrument, she made rapid progress as a virtuoso.}
\entry{tycoon}{N.}{大亨}{wealthy leader.}{John D. Rockefeller was a prominent tycoon.}
\entry{tyranny}{N.}{暴政; 专制}{oppression; cruel government.}{Frederick Douglass fought against the tyranny of slavery throughout his life.}
\entry{ubiquitous}{ADJ.}{无所不在的}{being everywhere; omnipresent.}{That Christmas "The Little Drummer Boy" seemed ubiquitous; David heard the tune everywhere.}
\entry{ulterior}{ADJ.}{将来的; 隐蔽的}{situated beyond; unstated.}{You must have an ulterior motive for your behavior, since there is no obvious reason for it.}
\entry{ultimate}{ADJ.}{终极的}{final; not susceptible to further analysis.}{Scientists are searching for ultimate truths.}
\entry{unaccountable}{ADJ.}{无责任的; 无法解释的}{inexplicable; unreasonable or mysterious.}{I have taken an unaccountable dislike to my doctor: "I do not love thee, Doctor Fell. The reason why, I cannot tell."}
\entry{unanimity}{N.}{全体同意; 全体一致}{complete agreement.}{We were surprised by the unanimity with which members of both parties accepted our proposals. unanimous,ADJ.}
\entry{unassailable}{ADJ.}{攻不破的}{not subject to question; not open to attack.}{Penelope's virtue was unassailable; while she waited for her husband to come back from the war, no other man had a chance.}
\entry{unassuming}{ADJ.}{谦逊的}{modest.}{He is so unassuming that some people fail to realize how great a man he really is.}
\entry{unconscionable}{ADJ.}{不合理的; 不道德的; 过度的}{unscrupulous; excessive.}{She found the loan shark's demands unconscionable and impossible to meet.}
\entry{underlying}{ADJ.}{根本的; 在下面的; 潜在的}{fundamental; lying below.}{The underlying cause of the student riot was not the strict curfew rule but the moldy cafeteria food. Miss Marple seems a sweet little old lady at first, but there's an iron will underlying that soft and fluffy facade.}
\entry{undermine}{V.}{破坏}{weaken; sap.}{The recent corruption scandals have undermined many people's faith in the city government. The recent torrential rains have washed away much of the cliffside; the deluge threatens to undermine the pillars supporting several houses at the edge of the cliff.}
\entry{underscore}{V.}{强调}{emphasize.}{Addressing the jogging class, Kim underscored the importance to runners of good nutrition.}
\entry{unearth}{V.}{出土; 发掘}{dig up.}{When they unearthed the city, the archeologists found many relics of an ancient civilization.}
\entry{unequivocal}{ADJ.}{明白清楚的}{plain; obvious; unmistakable.}{My answer to your proposal is an unequivocal and absolute "No."}
\entry{unfathomable}{ADJ.}{不可理解的; 不能渗透的}{incomprehensible; impenetrable.}{Unable to get to the bottom of the mystery, Watson declared it was unfathomable.}
\entry{uniformity}{N.}{一致性; 同样}{sameness; monotony.}{At Persons magazine, we strive for uniformity of style; as a result, all our writers wind up sounding exactly alike.}
\entry{uninhibited}{ADJ.}{放荡不羁的; 不受限制的}{unrepressed.}{The congregation was shocked by her uninhibited laughter during the sermon.}
\entry{unintimidating}{ADJ.}{无惧的}{unfrightening.}{Though Phil had expected to feel overawed when he met Steve Young, he found the famous quarterback friendly and unintimidating.}
\entry{unobtrusive}{ADJ.}{不显眼的; 朴素的}{inconspicuous; not blatant.}{Reluctant to attract notice, the governess took a chair in a far corner of the room and tried to be as unobtrusive as possible.}
\entry{unprecedented}{ADJ.}{空前的}{novel; unparalleled.}{For a first novel, Margaret Mitchell's novel Gone with the Wind was an unprecedented success.}
\entry{unprepossessing}{ADJ.}{不吸引人的}{unattractive.}{During adolescence many attractive young people somehow acquire the false notion that their appearance is unprepossessing.}
\entry{unravel}{V.}{拆开; 解决}{disentangle; solve.}{With equal ease Miss Marple unraveled tangled balls of yarn and baffling murder mysteries.}
\entry{unsightly}{ADJ.}{难看的}{ugly.}{Although James was an experienced emergency room nurse, he occasionally became queasy when faced with a particularly unsightly injury.}
\entry{untenable}{ADJ.}{防不住的; 防不胜防的; 站不住的}{indefensible; not able to be maintained.}{Wayne is so contrary that, the more untenable a position is, the harder he'll try to defend it.}
\entry{unwarranted}{ADJ.}{莫名其妙的; 没来由的; 冤枉的}{unjustified; groundless; undeserved.}{Your assumption that I would accept your proposal is unwarranted, sir; I do not want to marry you at all. We could not understand Martin's unwarranted rudeness to his mother's guests.}
\entry{unwitting}{ADJ.}{不知情的}{unintentional; not knowing.}{She was the unwitting tool of the swindlers.}
\entry{usurp}{V.}{篡取}{seize another's power or rank.}{The revolution ended when the victorious rebel general succeeded in his attempt to usurp the throne.}
\entry{vacillate}{V.}{犹豫; 踌躇; 摇摆}{}{}
\entry{valid}{ADJ.}{正当的; 有效的}{logically convincing; sound; legally acceptable.}{You're going to have to come up with a better argument if you want to convince me that your reasoning is valid.}
\entry{validate}{V.}{批准; 确认}{confirm; ratify.}{I will not publish my findings until I validate my results.}
\entry{valor}{N.}{英勇; 勇猛}{bravery.}{He received the Medal of Honor for his valor in battle.}
\entry{vantage}{N.}{优势}{position giving an advantage.}{They fired upon the enemy from behind trees, walls and any other point of vantage they could find.}
\entry{vaporize}{V.}{蒸发}{turn into vapor (steam, gas, fog, etc.}{. "Zap!" went Super Mario's atomic ray gun as he vaporized another deadly foe.}
\entry{velocity}{N.}{速度}{speed.}{The train went by at considerable velocity.}
\entry{venerable}{ADJ.}{庄严的; 值得尊重的}{deserving high respect.}{We do not mean to be disrespectful when we refuse to follow the advice of our venerable leader.}
\entry{venerate}{V.}{崇敬}{revere.}{In Tibet today, the common people still venerate their traditional spiritual leader, the Dalai Lama.}
\entry{vent}{N.}{出口, 出路}{a small opening; outlet.}{The wine did not flow because the air vent in the barrel was clogged.}
\entry{venturesome}{ADJ.}{冒险的}{bold.}{A group of venturesome women were the first to scale Mt. Annapurna.}
\entry{veracity}{N.}{真实; 准确性}{truthfulness.}{Asserting his veracity, young George Washington proclaimed, "Father, I cannot tell a lie!"}
\entry{verge}{N.}{边界}{border; edge.}{Madame Curie knew she was on the verge of discovering the secrets of radioactive elements. alsoV.}
\entry{verity}{N.}{真实; 真理; 真实的陈述}{quality of being true; lasting truth or principle.}{Did you question the verity of Kato Kaelin's testimony about what he heard the night Nicole Brown Simpson was slain? To the skeptic, everything was relative: there were no eternal verities in which one could believe.}
\entry{versatile}{ADJ.}{万能的; 通用的; 多面手的}{having many talents; capable of working in many fields.}{She was a versatile athlete, earning varsity letters in basketball, hockey, and track.}
\entry{vertex}{N.}{顶点}{summit.}{Let us drop a perpendicular line from the vertex of the triangle to the base.}
\entry{vestige}{N.}{遗迹; 痕迹; 残留物}{trace; remains.}{We discovered vestiges of early Indian life in the cave. vestigial,ADJ.}
\entry{viable}{ADJ.}{能养活的; 可行的}{practical or workable; capable of maintaining life.}{That idea won't work. Let me see whether I can come up with a viable alternative.}
\entry{vicarious}{ADJ.}{代理的; 代理人的}{acting as a substitute; done by a deputy.}{Many people get a vicarious thrill at the movies by imagining they are the characters on the screen.}
\entry{vigor}{N.}{活力}{active strength.}{Although he was over seventy years old, Jack had the vigor of a man in his prime. vigorOUS,ADJ.}
\entry{vindicate}{V.}{辩护; 维护}{clear from blame; exonerate; justify or support.}{The lawyer's goal was to vindicate her client and prove him innocent on all charges. The critics' extremely favorable reviews vindicate my opinion that The Madness of King George is a brilliant movie.}
\entry{virtual}{ADJ.}{有效的; 实质的; 虚的}{in essence; for practical purposes.}{She is a virtual financial wizard when it comes to money matters.}
\entry{virtue}{N.}{美德}{goodness, moral excellence; good quality.}{Virtue carried to extremes can turn into vice: humility, for example, can degenerate into servility and spinelessness.}
\entry{virus}{N.}{病毒}{disease communicator.}{The doctors are looking for a specific medicine to control this virus.}
\entry{visionary}{ADJ.}{幻想的}{produced by imagination; fanciful; mystical.}{She was given to visionary schemes that never materialized. also N.}
\entry{vital}{ADJ.}{重要的; 生命的; 生机的}{vibrant and lively; critical; living, breathing.}{The vital, highly energetic first aid instructor stressed that it was vital in examining accident victims to note their vital signs.}
\entry{vivacious}{ADJ.}{生动的}{animated; lively.}{She had always been vivacious and sparkling.}
\entry{volatile}{ADJ.}{挥发的; 飞行的; 可变的; 爆炸的}{changeable; explosive; evaporating rapidly.}{The political climate today is extremely volatile: No one can predict what the electorate will do next. Maria Callas's temper was extremely volatile: The only thing you could predict was that she was sure to blow up. Acetone is an extremely volatile liquid: It evaporates instantly.}
\entry{voluble}{ADJ.}{口齿伶俐的; 爱说话的}{fluent; glib; talkative.}{The excessively voluble speaker suffers from logorrhea: he runs off at the mouth a lot!}
\entry{voluminous}{ADJ.}{庞大的}{bulky; large.}{A caftan is a voluminous garment; most people wearing one look as if they're draped in a small tent.}
\entry{voracious}{ADJ.}{贪婪的; 狼吞虎咽的}{ravenous.}{The wolf is a voracious animal, its hunger never satisfied.}
\entry{vortex}{N.}{漩涡; 漩涡中心; （争斗、讨论的）中心}{whirlwind; whirlpool; center of turbulence; predicament into which one is inexorably plunged.}{Sucked into the vortex of the tornado, Dorothy and Toto were carried from Kansas to Oz.}
\entry{vulnerable}{ADJ.}{易受攻击的}{susceptible to wounds.}{His opponents could not harm Achilles, who was vulnerable only in his heel.}
\entry{waive}{V.}{暂时放弃; 屈从}{give up temporarily; yield.}{I will waive my rights in this matter in order to expedite our reaching a proper decision.}
\entry{warrant}{V.}{授权; 证明; 批准}{justify; authorize.}{Before the judge issues the injunction, you must convince her this action is warranted.}
\entry{wary}{ADJ.}{机警的; 小心的}{very cautious.}{The spies grew wary as they approached the sentry.}
\entry{wax}{V.}{增长}{increase; grow.}{With proper handling, his fortunes waxed and he became rich.}
\entry{weather}{V.}{侵蚀; 风化}{endure the effects of weather or other forces.}{He weathered the changes in his personal life with difficulty, as he had no one in whom to confide.}
\entry{whimsical}{ADJ.}{无常的; 古怪的}{capricious; fanciful.}{In Mrs. Doubtfire, the hero is a playful, whimsical man who takes a notion to dress up as a woman so that he can look after his children, who are in the custody of his ex-wife. whimsy, N.}
\entry{withdrawn}{ADJ.}{内向的; 孤僻的}{introverted; remote.}{Rebuffed by his colleagues, the initially outgoing young researcher became increasingly withdrawn.}
\entry{withhold}{V.}{拒给; 保留}{refuse to give; hold back.}{The tenants decided to withhold a portion of the rent until the landlord kept his promise to renovate the building.}
\entry{withstand}{V.}{抵抗; 经受住}{stand up against; successfully resist.}{If you can withstand all the peer pressure in high school to cut classes and goof off, you should survive college just fine.}
\entry{yield}{V.}{屈服; 放弃}{give in; surrender.}{The wounded knight refused to yield to his foe.}
\entry{zenith}{N.}{顶点}{point directly overhead in the sky; summit.}{When the sun was at its zenith, the glare was not as strong as at sunrise and sunset.}
\end{multicols}

%------------------------------------------------
\end{document}